---
title: "Teaching with NYC Open Data: Publishing Student Civic Research Through Reproducible Workflows"
author: "Christian Martinez"
format:
  revealjs:
    output-file: index.html
     output-dir: docs
editor: visual
---

## Teaching with NYC Open Data

Christian A. Martinez

Brooklyn College, City University of New York (CUNY)

NYC Open Data Week 2026

### [NYC Open Data Student Gallery](https://martinezc1-nyc-open-data-student-gallery.share.connect.posit.cloud/)

### [nycOpenData Package](https://martinezc1.github.io/nycOpenData/)

## Why This Matters

I realized my students were learning to **“juggle upside down.”**

They weren’t struggling with the code—\
they were struggling with the **relevance**.

### The Shift

-   Replace generic datasets with [NYC Open Data](https://opendata.cityofnewyork.us/)
-   Let students study their own neighborhoods, systems, and experiences

### The Result

👉 Learning actually sticks

## Today’s Format

### Lightning Research Talks

Each student will briefly share:

-   Research question\
-   NYC Open Data dataset used\
-   Key analysis or visualization\
-   Main finding\
-   Why it matters

## Student Presenters

These projects were developed as part of a graduate course in reproducible research using real NYC data.

-   Crystal Adote
-   Jonah Dratfield
-   Joyce Escatel Flores
-   Robert Hutto
-   Isley Jean-Pierre
-   Shannon Joyce
-   Emma Valentina Tupone
-   Xinru Wang
-   Laura Werner

------------------------------------------------------------------------

## Crystal Adote

### NYC Leading Causes of Death and Environmental Complaints

## Overview

My project examines the leading causes of death in NYC from 2007–2014, and indoor environmental complaints such as mold, indoor air quality, asbestos, and more from 2010 to the present. I wanted to explore these datasets and see whether there were any relationships between the two.

## Data

-   Leading causes of death: <https://data.cityofnewyork.us/resource/jb7j-dtam.json>
-   Indoor environmental complaints: <https://data.cityofnewyork.us/resource/9jgj-bmct.json>

## Indoor Environmental Complaint Types

```{r}
#| label: fig-tile
#| message: false
#| warning: true
#| fig-cap: "This is a Heatmap that conveys 5 of the leading causes of death over the years"
#| fig-alt: "This is a Heatmap that conveys 5 of the leading causes of death over the years"
#| paged-print: false
library(tidyverse)
library(skimr)
library(ggplot2)
library(knitr)
library(lubridate)
library(arrow)
library(here)

causes_of_death<- read_parquet(
  here("data","raw", "New_York_City_Leading_Causes_of_Death_data.parquet"))

indoor_complaints<- read_parquet(here
                            ("data","raw","Indoor_Environmental_Complaints_data.parquet"))

indoor_complaints<- select(indoor_complaints, -Incident_Address)
indoor_complaints<- select(indoor_complaints, -Incident_Address_Street_Number)
indoor_complaints<- select(indoor_complaints, -Incident_Address_Street_Name)
indoor_complaints<- select(indoor_complaints, -Incident_Address_Zip)
indoor_complaints<- select(indoor_complaints, -Complaint_Status)
indoor_complaints<- select(indoor_complaints, -Latitude)
indoor_complaints<- select(indoor_complaints, -Longitude)
indoor_complaints<- select(indoor_complaints, -`Community Board`)
indoor_complaints<- select(indoor_complaints, -`Council District`)
indoor_complaints<- select(indoor_complaints, -`Census Tract`)
indoor_complaints<- select(indoor_complaints, -BIN)
indoor_complaints<- select(indoor_complaints, -BBL)
indoor_complaints<- select(indoor_complaints, -NTA)
indoor_complaints<- select(indoor_complaints, -Deleted)
indoor_complaints<- select(indoor_complaints, -Complaint_Number)
indoor_complaints<- select(indoor_complaints, -Descriptor_1_311)
indoor_complaints<- select(indoor_complaints, -Incident_Address_Borough)
indoor_complaints$Date_Received<- year(indoor_complaints$Date_Received)
indoor_complaints<- indoor_complaints %>% rename(Year = Date_Received)
indoor_complaints<- indoor_complaints %>% rename(complaint_type = Complaint_Type_311)

causes_of_death<- select(causes_of_death, -`Death Rate`)
causes_of_death<- select(causes_of_death, -`Age Adjusted Death Rate`)
causes_of_death<- select(causes_of_death, -Sex)
causes_of_death<- select(causes_of_death, -`Race Ethnicity`)
causes_of_death<- select(causes_of_death, -Deaths)
causes_of_death<- causes_of_death %>% rename(cause_of_death = `Leading Cause`)

indoor_complaints<- indoor_complaints %>% 
  mutate(complaint_type = recode(
    complaint_type,
    "MOLD"="Mold",
    "Asbestos/Garbage Nuisance"="Garbage Nuisance",
    "LEAD"="Lead",
    "NEW YORK"="NY",
    "ASBESTOS"="Asbestos",
    "IAQ"="Indoor Air Quality"
  ))
indoor_complaints<- indoor_complaints %>% 
  filter(!complaint_type %in% c("NY", "100", "04727995"))
causes_of_death<- causes_of_death %>% 
  filter(!cause_of_death %in% c("Human Immunodeficiency Virus Disease (HIV: B20-B24)", "Intentional Self-Harm (Suicide: X60-X84, Y87.0)",
                                "Essential Hypertension and Renal Diseases (I10, I12)", "Diabetes Mellitus (E10-E14)", "Mental and Behavioral Disorders due to Accidental Poisoning and Other Psychoactive Substance Use (F11-F16, F18-F19, X40-X42, X44)",
                                "Accidents Except Drug Posioning (V01-X39, X43, X45-X59, Y85-Y86)", "All Other Causes", "Certain Conditions originating in the Perinatal Period (P00-P96)", 
                                "Chronic Liver Disease and Cirrhosis (K70, K73)", "Nephritis, Nephrotic Syndrome and Nephrisis (N00-N07, N17-N19, N25-N27)", "Alzheimer's Disease (G30)", 
                                "Assault (Homicide: Y87.1, X85-Y09)", "Congenital Malformations, Deformations, and Chromosomal Abnormalities (Q00-Q99)",
                                "Septicemia (A40-A41)", "Viral Hepatitis (B15-B19)", "Aortic Aneurysm and Dissection (I71)", "Parkinson's Disease (G20)",
                                "Tuberculosis (A16-A19)","Mental and Behavioral Disorders due to Use of Alcohol (F10)", "Insitu or Benign / Uncertain Neoplasms (D00-D48)", "Atherosclerosis (I70)"))


complaints_summary<- indoor_complaints %>% add_count(complaint_type, name = "Number of Complaints")

deaths_summary <- causes_of_death %>%
  group_by(cause_of_death) %>%
  summarise(`Number of Deaths` = n(), .groups = "drop")

death_counts<- causes_of_death %>% count(Year, cause_of_death)

death_causes_and_year<- ggplot(death_counts, aes(x=Year, y=cause_of_death, fill=n))+
  geom_tile()+
  labs(
    title="Leading Causes of Death Across the Years",
    x="Year",
    y="Leading Causes of Death",
    fill="Number of Deaths"
  ) +
  theme_minimal()
death_causes_and_year
```

## Leading Causes of Death

```{r}
#| label: fig-indoor-environmental-graph
#| message: false
#| warning: true
#| fig-cap: "This stacked bar graph conveys the amount of indoor environmental complaints over the years"
#| fig-alt: 'This stacked bar graph conveys the amount of indoor environmental complaints over the years'
#| paged-print: false
complaint_and_year<- ggplot(indoor_complaints, aes(x=Year, fill=complaint_type))+
  geom_bar()+
  labs(
    title="Indoor Environmental Complaint Types across the Years",
    x="Year",
    y="Complaint Type",
    fill="Complaint Type"
  ) +
theme_classic()
complaint_and_year
```


## Data Cleaning and Analysis

-   Took out columns that were not needed
-   Kept only five common, well-known causes of death
-   Paired complaint types with causes of death
-   Merged the two datasets

## Statistical Tests

-   Correlation: r = 0.6122905
    -   Moderately strong
-   Linear regression suggested that indoor complaint types did not show a meaningful relationship with the leading causes of death in NYC.

## Takeaway

-   This topic is important to the general community because it sheds light on indoor environmental hazards that individuals file complaints about.
-   It also raises questions about whether there may be a relationship between indoor environmental hazards and leading causes of death in NYC.

------------------------------------------------------------------------

## Jonah Dratfield

### Social Infrastructure & Well-being

## The Overarching Questions

-   Can publicly available data be used to explore the conditions that best facilitate social connectedness, and thereby, most enhance quality of life?

-   Is there already data that points to "abstract" psychological constructs like well-being, loneliness, etc?

-   If so, is how can this data be acted upon or improved?

## Some (Partial) Answers

-   At present, NYC Open Data does not include the validated measures psychologists typically use to assess metrics like social connectedness and well-being.

-   However, there are various proxies.

-   Permitted events are a proxy for connectedness.

-   Number of SNAP Benefit Recipients is a (very) rough proxy for economic health (which is often associated with well-being).

## Community District/SNAP Chart

```{r}
#| include: false
library(tidyverse)
library(nycOpenData)
library(dplyr)
library(stringr)

Events <- nyc_permit_events_historic(limit = 10000, filters = list())
BoroReport <- nyc_borough_community_report(limit = 10000, filters = list())

knitr::kable(
  head(Events, 25),
  caption = "First 25 rows of Events"
)

knitr::kable(
  head(BoroReport, 25),
  caption = "First 25 rows of BoroReport"
)

eventscleaner <- Events %>%
  mutate(
    cd_id =
      community_board |> 
      str_replace_all("[^0-9]", "") |>  
      as.numeric()                       
  )
BoroReport <- BoroReport %>%
  
  mutate(
    snap_borough = str_extract(community_district, "^[A-Za-z]") |> str_to_upper(),
    snap_cb      = str_extract(community_district, "[0-9]+") |> as.numeric()
  ) %>%
  
  mutate(
    snap_borough_num = case_when(
      snap_borough == "M" ~ 100,  # Manhattan
      snap_borough == "B" ~ 200,  # Bronx
      snap_borough == "K" ~ 300,  # Brooklyn
      snap_borough == "Q" ~ 400,  # Queens
      snap_borough == "S" ~ 500,  # Staten Island
      TRUE ~ NA_real_
    ),
    
    cd_id = snap_borough_num + snap_cb
  )
eventscleaner <- eventscleaner %>%
  
  mutate(
    borough_num = case_when(
      event_borough == "Manhattan"     ~ 100,
      event_borough == "Bronx"         ~ 200,
      event_borough == "Brooklyn"      ~ 300,
      event_borough == "Queens"        ~ 400,
      event_borough == "Staten_Island" ~ 500,
      event_borough == "Staten Island" ~ 500,  
      TRUE ~ NA_real_
    ),
    
   
    cd_id = borough_num + cd_id
  )
events_cd <- eventscleaner %>%
  count(cd_id, name = "n_events")

knitr::kable(
  head(events_cd, 30),
  caption = "Number of Events Per CD"
)

events_cd %>%
  slice_max(n_events, n = 25) %>%
  ggplot(aes(x = reorder(cd_id, n_events), y = n_events)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Number of Events by Community District (Top 25)",
    x = "Community District",
    y = "Number of Events"
  ) +
  theme_minimal()

BoroReport <- BoroReport %>%
  mutate(
    bc_snap_recipients = as.numeric(bc_snap_recipients)
  )

snap_plot_data <- BoroReport %>%
  group_by(cd_id) %>%
  summarise(
    bc_snap_recipients = mean(bc_snap_recipients,na.rm = TRUE),
    .groups = "drop"
  )
```

```{R}
#| label: fig-snap-plot-data
#| echo: false

snap_plot_data %>%
  slice_max(bc_snap_recipients, n = 25) %>%
  ggplot(
    aes(
      x = reorder(cd_id, bc_snap_recipients),
      y = bc_snap_recipients
    )
  ) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "SNAP Recipients by Community District (Top 25)",
    x = "Community District",
    y = "SNAP Recipients"
  ) +
  theme_minimal()

```

```{r}
#| include: false

merged <- BoroReport %>%
  left_join(events_cd, by = "cd_id")

knitr::kable(
  head(merged, 25),
  caption = "First 25 rows of merged"
)

model1 <- lm(bc_snap_recipients ~ n_events, data = merged)
summary(model1)
```

## Results

-   A linear regression was conducted to determine whether number of permitted events predicts number of SNAP recipients.

-   The model was statistically significant, F(1, 723) = 45.34, p \< .001, and explained approximately 6% of the variance in SNAP recipients (R² = .059).

-   The number of events was a significant negative predictor of SNAP recipients, b = −21.30, SE = 3.16, t(723) = −6.73, p \< .001.

## Permitted Events/SNAP Linear Model

```{R}
#| label: fig-permit-events-snap
#| echo: false

ggplot(
  merged,
  aes(
    x = n_events,
    y = bc_snap_recipients
  )
) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, color = "red") +
  labs(
    title = "Permitted Events and SNAP Recipients by Community District",
    x = "Permitted Events",
    y = "SNAP Recipients"
  ) +
  theme_minimal()
```

## Limitations

-   Results are significant and promising ... but ...

-   SNAP is an imperfect measure of holistic well-being (as well as economic). We need more "middle range" data.

-   We need better social gathering info (Reddit, Meetup, Eventbrite, etc.)

-   Community districts are imperfect units. Access is as important as location. Parks, for instance, were excluded from the analysis.

## New Directions

-   Survey data about abstract constructs to corroborate and inform the "practical" data.

-   Use of evidence to intervene in low-barrier ways (and tracking of those interventions).

------------------------------------------------------------------------

## Joyce Escatel-Flores

### NYC Art Meets NYC Appetite

## Goals of the Project

-   Explore whether restaurants near art museums are **more** likely to have higher ratings than restaurants not close to museums.

-   Explore whether restaurants near museums are **less** likely to have no violation citations than restaurants not close to museums.

-   Creating an **interactive map** that pinpoints restaurants that are nearby museums.

## Data Sets Used

-   **DOHMH New York City Restaurant Inspection results** which you can find at https://data.cityofnewyork.us/Health/DOHMH-New-York-City-Restaurant-Inspection-Results/43nn-pn8j/about_data
-   **MUSEUM** which you can find at https://data.cityofnewyork.us/Recreation/MUSEUM/fn6f-htvy/about_data

The third data set is a Kaggle open data set created by **Beridzeg45** called **NYC Restaurants**, which you can find at https://www.kaggle.com/datasets/beridzeg45/nyc-restaurants

## Goal 1: Visualizing the Analysis

We are visualizing the proportion of rating groups (high, medium, low) by if restaurants are near museums (yes,no).

```{r}
#| include: false
library(readr)
library(tidyr)
library(dplyr)
library(tidyverse)
library(stringr)
library(readxl)
library(janitor)
library(ggthemes)
library(rcompanion)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(htmltools)

endpoint<- "https://data.cityofnewyork.us/resource/fn6f-htvy.json"
resp <- httr::GET(endpoint)
museum_data <- jsonlite::fromJSON(httr::content(resp, as = "text"), flatten = TRUE)



endpoint_1<-"https://data.cityofnewyork.us/resource/43nn-pn8j.json"
resp1 <- httr::GET(endpoint_1)
restaurant_data <- jsonlite::fromJSON(httr::content(resp1, as = "text"), flatten = TRUE)


restaurant_rating_data <- read_parquet(here("data", "raw", "restaurant_rating_data.parquet"), as_data_frame = TRUE )
```

```{r}
#| include: false
restaurant_rating_data$lat_new<- shQuote(restaurant_rating_data$Lat)
restaurant_rating_data$lon_new<- shQuote(restaurant_rating_data$Lon)
restaurant_rating_data$location.coordinates<- paste("c", "(", restaurant_rating_data$lon_new, ",", restaurant_rating_data$lat_new, ")", sep = "")

restaurant_rating_data <- restaurant_rating_data[-c(1, 2, 4, 5, 6, 8, 10, 11, 12, 15, 16, 26, 28, 32, 33,37, 38, 42, 45, 46, 47, 48, 50, 51, 57, 58, 61, 62, 63, 66, 68, 69, 74, 75, 79, 82, 85, 86, 89, 90, 93, 94, 95, 96, 97, 98, 99, 100, 103, 104, 105, 110, 111, 113, 117, 118, 119, 120, 128, 131, 133, 134, 138, 140, 144, 147, 151, 152, 153, 160, 165, 168, 174, 175, 176, 178, 179, 182, 183, 184, 186, 190, 192, 193, 195, 197, 198, 203, 204, 206, 208, 209, 212, 216, 218, 220, 223, 224, 225, 231, 232, 234, 236, 241, 244, 247, 249, 251, 254, 256, 265, 267, 268, 271, 274, 277, 283, 284, 285, 288, 289, 292, 294, 295, 297, 298, 299, 300, 301, 304, 305, 308, 310, 312, 315, 318, 320, 321, 322, 323, 325, 326, 328, 330, 331, 332, 334, 335, 337, 338, 339, 340, 341, 343, 345, 346, 348, 349, 350, 351, 353, 355, 356, 357, 359, 362, 363, 365, 366, 367, 370, 375, 376, 377, 378, 379, 380, 388, 389, 390, 391, 392, 393, 396, 399, 403, 406, 411, 415, 416, 417, 418, 420, 422, 423, 424, 425, 427, 429, 430, 432, 433, 435, 438, 439, 441, 442, 443, 444, 447, 449, 451, 454, 455, 457, 461, 463, 467, 469, 470, 472, 473, 474, 477, 478, 479, 483, 484, 488, 489, 491, 495, 497, 499, 500, 501, 506, 507, 508, 509, 510, 513, 514, 516, 520, 521, 522, 523, 525, 527, 528, 529, 532, 533, 537, 538, 539, 540, 543, 544, 546, 547, 549, 550, 552, 553, 554, 555, 556, 558, 560, 561, 562, 566, 567, 568, 569, 570, 571, 572, 575, 577, 578, 579, 580, 581, 582, 587, 589, 590, 591, 592, 595, 598, 599, 600, 607, 608, 610, 611, 612, 613, 614, 615, 618, 620, 621, 622, 624, 625, 626, 627, 631, 633, 635, 636, 637, 638, 640, 641, 646, 648, 653, 655, 657, 658, 660, 661, 663, 669, 670), ]
```

```{r}
#| include: false
is.character(restaurant_data$location.coordinates)
restaurant_data<- restaurant_data %>% mutate(location.coordinates = as.character(location.coordinates))

merged_restaurant_data<- full_join(restaurant_data, restaurant_rating_data, by = "location.coordinates")

sum(merged_restaurant_data$location.coordinates == "NULL", na.rm = TRUE)

merged_restaurant_data <-merged_restaurant_data[merged_restaurant_data$location.coordinates != "NULL", ]
```

```{r}
#| include: false
merged_restaurant_data[2,35]=4.7
merged_restaurant_data[3,35]=4.8
merged_restaurant_data[4,35]=4.0
merged_restaurant_data[6,35]=4.7
merged_restaurant_data[11,35]=4.9
merged_restaurant_data[13,35]=4.5
merged_restaurant_data[14,35]=4.1
merged_restaurant_data[16,35]=4.4
merged_restaurant_data[17,35]=4.8
merged_restaurant_data[18,35]=4.9
merged_restaurant_data[21,35]=4.2
merged_restaurant_data[22,35]=5.0
merged_restaurant_data[27,35]=4.4
merged_restaurant_data[28,35]=4.9
merged_restaurant_data[31,35]=4.4
merged_restaurant_data[32,35]=4.8
merged_restaurant_data[35,35]=4.4
merged_restaurant_data[39,35]=4.5
merged_restaurant_data[40,35]=4.6
merged_restaurant_data[44,35]=5.0
merged_restaurant_data[48,35]=5.0
merged_restaurant_data[49,35]=4.4 
merged_restaurant_data[50,35]=3.8
merged_restaurant_data[55,35]=4.9
merged_restaurant_data[58,35]=4.1
merged_restaurant_data[59,35]=4.3
merged_restaurant_data[61,35]=4.1
merged_restaurant_data[62,35]=4.4
merged_restaurant_data[63,35]=4.4
merged_restaurant_data[64,35]=3.8
merged_restaurant_data[67,35]=4.9
merged_restaurant_data[69,35]=4.6
merged_restaurant_data[73,35]=4.8
merged_restaurant_data[78,35]=5.0
merged_restaurant_data[82,35]=4.6
merged_restaurant_data[94,35]=4.8
merged_restaurant_data[96,35]=4.8
merged_restaurant_data[98,35]=4.2
merged_restaurant_data[103,35]=4.5
merged_restaurant_data[104,35]=4.9
merged_restaurant_data[105,35]=2.7
merged_restaurant_data[111,35]=4.1
merged_restaurant_data[113,35]=4.6
merged_restaurant_data[114,35]=4.4
merged_restaurant_data[115,35]=2.0
merged_restaurant_data[118,35]=4.6
merged_restaurant_data[130,35]=4.6
merged_restaurant_data[133,35]=3.0
merged_restaurant_data[134,35]=4.1
merged_restaurant_data[136,35]=4.7
merged_restaurant_data[142,35]=4.7
merged_restaurant_data[144,35]=4.0
merged_restaurant_data[146,35]=4.0
merged_restaurant_data[148,35]=3.5
merged_restaurant_data[150,35]=4.3
merged_restaurant_data[152,35]=4.8
merged_restaurant_data[153,35]=4.7
merged_restaurant_data[154,35]=5.0
merged_restaurant_data[159,35]=4.3
merged_restaurant_data[164,35]=4.7
merged_restaurant_data[169,35]=4.2
merged_restaurant_data[172,35]=4.6
merged_restaurant_data[173,35]=4.9
merged_restaurant_data[179,35]=4.7
merged_restaurant_data[180,35]=4.2
merged_restaurant_data[184,35]=4.4
merged_restaurant_data[185,35]=4.9
merged_restaurant_data[186,35]=4.5
merged_restaurant_data[189,35]=4.6
merged_restaurant_data[190,35]=5.0
merged_restaurant_data[191,35]=4.7
merged_restaurant_data[193,35]=4.8
merged_restaurant_data[195,35]=4.6
merged_restaurant_data[197,35]=4.8
merged_restaurant_data[199,35]=5.0
merged_restaurant_data[201,35]=4.5
merged_restaurant_data[207,35]=4.5
merged_restaurant_data[215,35]=4.2
merged_restaurant_data[217,35]=3.8
merged_restaurant_data[219,35]=4.8
merged_restaurant_data[221,35]=4.7
merged_restaurant_data[223,35]=4.6
merged_restaurant_data[229,35]=4.5
merged_restaurant_data[232,35]=4.7
merged_restaurant_data[233,35]=4.1
merged_restaurant_data[235,35]=4.6
merged_restaurant_data[236,35]=4.4
merged_restaurant_data[237,35]=4.3
merged_restaurant_data[241,35]=4.7
merged_restaurant_data[243,35]=4.5
merged_restaurant_data[245,35]=5.0
merged_restaurant_data[246,35]=4.7
merged_restaurant_data[260,35]=4.6
merged_restaurant_data[262,35]=4.3
merged_restaurant_data[270,35]=4.1
merged_restaurant_data[271,35]=4.9
merged_restaurant_data[273,35]=4.4
merged_restaurant_data[275,35]=4.9
merged_restaurant_data[278,35]=4.1
merged_restaurant_data[279,35]=4.5
merged_restaurant_data[280,35]=4.6
merged_restaurant_data[285,35]=4.3
merged_restaurant_data[286,35]=4.7
merged_restaurant_data[287,35]=4.8
merged_restaurant_data[288,35]=4.9
merged_restaurant_data[297,35]=4.5
merged_restaurant_data[304,35]=4.5
merged_restaurant_data[305,35]=4.7
merged_restaurant_data[308,35]=4.0
merged_restaurant_data[310,35]=4.5
merged_restaurant_data[314,35]=4.4
merged_restaurant_data[315,35]=4.7
merged_restaurant_data[319,35]=4.8
merged_restaurant_data[321,35]=4.9
merged_restaurant_data[322,35]=4.2 
merged_restaurant_data[328,35]=5.0
merged_restaurant_data[330,35]=4.6
merged_restaurant_data[335,35]=4.6
merged_restaurant_data[341,35]=5.0
merged_restaurant_data[342,35]=4.2
merged_restaurant_data[344,35]=3.6
merged_restaurant_data[346,35]=4.1
merged_restaurant_data[348,35]=4.9
merged_restaurant_data[350,35]=4.2
merged_restaurant_data[351,35]=4.1
merged_restaurant_data[352,35]=4.5
merged_restaurant_data[353,35]=4.5
merged_restaurant_data[356,35]=4.4
merged_restaurant_data[357,35]=4.3
merged_restaurant_data[358,35]=4.2
merged_restaurant_data[359,35]=4.8
merged_restaurant_data[363,35]=4.5
merged_restaurant_data[364,35]=4.8
merged_restaurant_data[367,35]=4.2
merged_restaurant_data[371,35]=4.6
merged_restaurant_data[374,35]=5.0
merged_restaurant_data[375,35]=3.9
merged_restaurant_data[376,35]=3.9
merged_restaurant_data[379,35]=3.8
merged_restaurant_data[382,35]=3.9
merged_restaurant_data[383,35]=5.0
merged_restaurant_data[384,35]=4.6
merged_restaurant_data[385,35]=4.6
merged_restaurant_data[387,35]=4.3
merged_restaurant_data[389,35]=4.9
merged_restaurant_data[391,35]=4.2
merged_restaurant_data[394,35]=4.5
merged_restaurant_data[395,35]=4.5
merged_restaurant_data[397,35]=4.8
merged_restaurant_data[404,35]=4.4
merged_restaurant_data[406,35]=4.5
merged_restaurant_data[408,35]=4.4
merged_restaurant_data[410,35]=3.8
merged_restaurant_data[411,35]=4.8
merged_restaurant_data[414,35]=3.9
merged_restaurant_data[416,35]=4.9
merged_restaurant_data[420,35]=4.6
merged_restaurant_data[422,35]=4.0
merged_restaurant_data[427,35]=4.8
merged_restaurant_data[433,35]=4.7
merged_restaurant_data[436,35]=3.7
merged_restaurant_data[437,35]=4.3
merged_restaurant_data[438,35]=4.6
merged_restaurant_data[440,35]=4.6
merged_restaurant_data[446,35]=4.7
merged_restaurant_data[452,35]=4.1
merged_restaurant_data[453,35]=4.3
merged_restaurant_data[454,35]=5.0
merged_restaurant_data[458,35]=4.3
merged_restaurant_data[459,35]=3.9
merged_restaurant_data[463,35]=4.0
merged_restaurant_data[467,35]=4.9
merged_restaurant_data[470,35]=4.0
merged_restaurant_data[471,35]=4.1
merged_restaurant_data[472,35]=4.0
merged_restaurant_data[486,35]=4.3
merged_restaurant_data[489,35]=5.0
merged_restaurant_data[494,35]=5.0
merged_restaurant_data[495,35]=4.9
merged_restaurant_data[496,35]=4.3
merged_restaurant_data[497,35]=4.2
merged_restaurant_data[501,35]=5.0
merged_restaurant_data[502,35]=4.1
merged_restaurant_data[506,35]=4.6
merged_restaurant_data[507,35]=4.6
merged_restaurant_data[509,35]=4.7
merged_restaurant_data[511,35]=4.5
merged_restaurant_data[512,35]=4.5
merged_restaurant_data[513,35]=3.3
merged_restaurant_data[515,35]=4.9
merged_restaurant_data[519,35]=4.8
merged_restaurant_data[520,35]=4.5
merged_restaurant_data[522,35]=4.9
merged_restaurant_data[523,35]=4.8
merged_restaurant_data[528,35]=4.9
merged_restaurant_data[533,35]=4.3
merged_restaurant_data[543,35]=4.6
merged_restaurant_data[546,35]=4.0
merged_restaurant_data[550,35]=4.8
merged_restaurant_data[552,35]=4.3
merged_restaurant_data[554,35]=3.7
merged_restaurant_data[555,35]=2.1
merged_restaurant_data[556,35]=4.7
merged_restaurant_data[557,35]=4.5
merged_restaurant_data[558,35]=5.0
merged_restaurant_data[562,35]=4.1
merged_restaurant_data[563,35]=4.3
merged_restaurant_data[566,35]=4.3
merged_restaurant_data[567,35]=4.5
merged_restaurant_data[568,35]=4.9
merged_restaurant_data[570,35]=4.3
merged_restaurant_data[573,35]=4.6
merged_restaurant_data[574,35]=4.1
merged_restaurant_data[575,35]=4.8
merged_restaurant_data[578,35]=4.4
merged_restaurant_data[581,35]=4.0
merged_restaurant_data[590,35]=4.1
merged_restaurant_data[592,35]=5.0
merged_restaurant_data[598,35]=3.9
merged_restaurant_data[601,35]=4.2
merged_restaurant_data[605,35]=4.6
merged_restaurant_data[608,35]=4.1
merged_restaurant_data[610,35]=4.1
merged_restaurant_data[613,35]=4.9
merged_restaurant_data[617,35]=4.4
merged_restaurant_data[622,35]=4.3
merged_restaurant_data[624,35]=4.0
merged_restaurant_data[625,35]=5.0
merged_restaurant_data[632,35]=4.4
merged_restaurant_data[633,35]=4.6
merged_restaurant_data[638,35]=4.2
merged_restaurant_data[640,35]=4.6
merged_restaurant_data[645,35]=4.6
merged_restaurant_data[647,35]=4.5
merged_restaurant_data[651,35]=4.9
merged_restaurant_data[660,35]=5.0
merged_restaurant_data[661,35]=4.7
merged_restaurant_data[662,35]=3.9
merged_restaurant_data[663,35]=4.0
merged_restaurant_data[664,35]=4.4
merged_restaurant_data[666,35]=4.3
merged_restaurant_data[677,35]=4.2
merged_restaurant_data[683,35]=4.5
merged_restaurant_data[686,35]=4.3
merged_restaurant_data[688,35]=4.8
merged_restaurant_data[689,35]=4.9
merged_restaurant_data[692,35]=4.9
merged_restaurant_data[693,35]=3.8
merged_restaurant_data[697,35]=4.9
merged_restaurant_data[700,35]=4.0
merged_restaurant_data[702,35]=4.8
merged_restaurant_data[714,35]=4.6
merged_restaurant_data[718,35]=4.6
merged_restaurant_data[719,35]=4.5
merged_restaurant_data[725,35]=4.5
merged_restaurant_data[728,35]=4.7
merged_restaurant_data[729,35]=4.8
merged_restaurant_data[731,35]=4.7
merged_restaurant_data[732,35]=4.2
merged_restaurant_data[733,35]=4.4
merged_restaurant_data[734,35]=3.8
merged_restaurant_data[735,35]=4.5
merged_restaurant_data[737,35]=4.5
merged_restaurant_data[738,35]=4.6
merged_restaurant_data[741,35]=3.8
merged_restaurant_data[744,35]=4.9
merged_restaurant_data[746,35]=4.3
merged_restaurant_data[747,35]=4.2
merged_restaurant_data[752,35]=3.7
merged_restaurant_data[755,35]=4.5
merged_restaurant_data[759,35]=4.0
merged_restaurant_data[762,35]=4.8
merged_restaurant_data[764,35]=4.3
merged_restaurant_data[767,35]=4.4
merged_restaurant_data[769,35]=4.3
merged_restaurant_data[770,35]=4.9
merged_restaurant_data[772,35]=4.0
merged_restaurant_data[774,35]=4.9
merged_restaurant_data[777,35]=4.8
merged_restaurant_data[779,35]=4.1
merged_restaurant_data[780,35]=4.4
merged_restaurant_data[782,35]=4.6
merged_restaurant_data[784,35]=4.1
merged_restaurant_data[785,35]=5.0
merged_restaurant_data[787,35]=4.1
merged_restaurant_data[788,35]=4.8
merged_restaurant_data[790,35]=4.1
merged_restaurant_data[791,35]=3.8
merged_restaurant_data[793,35]=4.4
merged_restaurant_data[796,35]=4.6
merged_restaurant_data[799,35]=5.0
merged_restaurant_data[802,35]=4.3
merged_restaurant_data[807,35]=4.2
merged_restaurant_data[809,35]=4.3
merged_restaurant_data[810,35]=3.9
merged_restaurant_data[811,35]=4.4
merged_restaurant_data[812,35]=4.5
merged_restaurant_data[816,35]=5.0
merged_restaurant_data[820,35]=4.6
merged_restaurant_data[825,35]=4.9
merged_restaurant_data[827,35]=4.8
merged_restaurant_data[828,35]=5.0
merged_restaurant_data[830,35]=4.5
merged_restaurant_data[834,35]=4.4
merged_restaurant_data[837,35]=4.3
merged_restaurant_data[838,35]=5.0
merged_restaurant_data[839,35]=3.0
merged_restaurant_data[841,35]=3.0
merged_restaurant_data[842,35]=4.6
merged_restaurant_data[852,35]=5.0
merged_restaurant_data[855,35]=4.9
merged_restaurant_data[856,35]=4.1
merged_restaurant_data[859,35]=4.5
merged_restaurant_data[861,35]=4.8
merged_restaurant_data[865,35]=4.6
merged_restaurant_data[868,35]=4.8
merged_restaurant_data[869,35]=5.0
merged_restaurant_data[870,35]=4.6
merged_restaurant_data[871,35]=4.1
merged_restaurant_data[872,35]=4.4
merged_restaurant_data[878,35]=4.4
merged_restaurant_data[883,35]=4.6
merged_restaurant_data[884,35]=4.3
merged_restaurant_data[889,35]=4.6
merged_restaurant_data[891,35]=4.4
merged_restaurant_data[893,35]=4.5
merged_restaurant_data[894,35]=4.5
merged_restaurant_data[896,35]=3.2
merged_restaurant_data[897,35]=3.8
merged_restaurant_data[899,35]=3.8
merged_restaurant_data[901,35]=4.6
merged_restaurant_data[902,35]=4.1
merged_restaurant_data[905,35]=3.7
merged_restaurant_data[906,35]=4.6
merged_restaurant_data[907,35]=4.5
merged_restaurant_data[909,35]=4.9
merged_restaurant_data[910,35]=4.1
merged_restaurant_data[913,35]=3.0
merged_restaurant_data[916,35]=4.8
merged_restaurant_data[920,35]=4.2
merged_restaurant_data[921,35]=4.3
merged_restaurant_data[924,35]=4.9
merged_restaurant_data[925,35]=5.0
merged_restaurant_data[929,35]=3.5
merged_restaurant_data[930,35]=4.8
merged_restaurant_data[933,35]=3.8
merged_restaurant_data[936,35]=4.4
merged_restaurant_data[939,35]=4.4
merged_restaurant_data[940,35]=4.3
merged_restaurant_data[941,35]=4.6
merged_restaurant_data[942,35]=4.6
merged_restaurant_data[943,35]=4.2
merged_restaurant_data[945,35]=3.8
merged_restaurant_data[946,35]=4.6
merged_restaurant_data[948,35]=4.6
merged_restaurant_data[951,35]=3.4
merged_restaurant_data[953,35]=4.9
merged_restaurant_data[954,35]=4.3
merged_restaurant_data[955,35]=3.2
merged_restaurant_data[957,35]=4.5
merged_restaurant_data[961,35]=4.5
merged_restaurant_data[962,35]=4.9
merged_restaurant_data[965,35]=4.4
merged_restaurant_data[968,35]=4.1
merged_restaurant_data[970,35]=4.4
merged_restaurant_data[971,35]=4.7
merged_restaurant_data[972,35]=4.6
merged_restaurant_data[974,35]=3.5
merged_restaurant_data[975,35]=4.5
merged_restaurant_data[977,35]=4.7
merged_restaurant_data[979,35]=4.2
merged_restaurant_data[981,35]=4.8
merged_restaurant_data[982,35]=4.4
merged_restaurant_data[984,35]=4.4
merged_restaurant_data[986,35]=4.3
merged_restaurant_data[987,35]=4.3
merged_restaurant_data[988,35]=4.6
merged_restaurant_data[989,35]=2.7
merged_restaurant_data[991,35]=4.7
merged_restaurant_data[992,35]=4.3
merged_restaurant_data[993,35]=4.1
merged_restaurant_data[997,35]=4.8
merged_restaurant_data[998,35]=4.8
merged_restaurant_data[999,35]=4.4

sum(is.na(merged_restaurant_data$Rating))

merged_restaurant_data<- merged_restaurant_data %>%
  filter(!is.na(Rating))

merged_restaurant_data$dba<- str_to_title(merged_restaurant_data$dba)

merged_restaurant_data$Restaurant_Name <-
  paste(
    coalesce(merged_restaurant_data$dba, ""),
    coalesce(merged_restaurant_data$Name, "")
  )
```

```{r}
#| include: false
merged_restaurant_data <- merged_restaurant_data %>% select(-dba, -boro, -building, -street, -zipcode, -phone, -community_board, -council_district, -census_tract, -bbl, -nta, -`:@computed_region_f5dn_yrer`, -`:@computed_region_yeji_bk3q`, -`:@computed_region_sbqj_enih`, -`:@computed_region_92fq_4b7q`, -cuisine_description, -bin, -grade, -grade_date, -URL, -Name, -`Rating Count`, -`Detailed Ratings`, -`Price Category`, -Address, -ZipCode)

str(merged_restaurant_data$Lat)

str(merged_restaurant_data$latitude)

merged_restaurant_data$latitude<-as.numeric(merged_restaurant_data$latitude)

merged_restaurant_data$Lat<-as.numeric(merged_restaurant_data$Lat)

merged_restaurant_data$Latitude <-
  coalesce(
    merged_restaurant_data$latitude, merged_restaurant_data$Lat
  )

merged_restaurant_data <- merged_restaurant_data %>% select(-Lat, -latitude)

str(merged_restaurant_data$Lon)

str(merged_restaurant_data$longitude)

merged_restaurant_data$Lon<-as.numeric(merged_restaurant_data$Lon)

merged_restaurant_data$longitude<-as.numeric(merged_restaurant_data$longitude)

merged_restaurant_data$Longitude <-
  coalesce(
    merged_restaurant_data$longitude, merged_restaurant_data$Lon
  )

merged_restaurant_data <- merged_restaurant_data %>% select(-Lon, -longitude)
```

```{r}
#| include: false
museum_data<- museum_data %>%
  select(-tel, -url, -adress1, -address2)

museum_data<- museum_data %>%
  mutate(
    cleaned_geom_coordinates = gsub("c\\(|\\)|\"", "", the_geom.coordinates)
    )

museum_data<-museum_data %>%
  separate(
    col = cleaned_geom_coordinates,
    into = c("Longitude", "Latitude"),
    sep = ","
  )

museum_data$Longitude<- as.numeric(museum_data$Longitude)

museum_data$Latitude<- 
  as.numeric(museum_data$Latitude)
```

```{r}
#| include: false
merged_restaurant_data$Near_Museum<- ""

merged_restaurant_data[,18]="No"
merged_restaurant_data[14,18]="Yes"
merged_restaurant_data[629,18]="Yes"
merged_restaurant_data[458,18]="Yes"
merged_restaurant_data[389,18]="Yes"
merged_restaurant_data[490,18]="Yes"
merged_restaurant_data[550,18]="Yes"
merged_restaurant_data[48,18]="Yes"
merged_restaurant_data[411,18]="Yes"
merged_restaurant_data[361,18]="Yes"
merged_restaurant_data[471,18]="Yes"
merged_restaurant_data[456,18]="Yes"
merged_restaurant_data[553,18]="Yes"
merged_restaurant_data[404,18]="Yes"
merged_restaurant_data[562,18]="Yes"
merged_restaurant_data[288,18]="Yes"
merged_restaurant_data[487,18]="Yes"
merged_restaurant_data[460,18]="Yes"
merged_restaurant_data[579,18]="Yes"
merged_restaurant_data[620,18]="Yes"
merged_restaurant_data[309,18]="Yes"
merged_restaurant_data[244,18]="Yes"
merged_restaurant_data[439,18]="Yes"
merged_restaurant_data[507,18]="Yes"
merged_restaurant_data[381,18]="Yes"
merged_restaurant_data[355,18]="Yes"
merged_restaurant_data[433,18]="Yes"
merged_restaurant_data[513,18]="Yes"
merged_restaurant_data[238,18]="Yes"
merged_restaurant_data[590,18]="Yes"
merged_restaurant_data[120,18]="Yes"
merged_restaurant_data[143,18]="Yes"
merged_restaurant_data[259,18]="Yes"
merged_restaurant_data[118,18]="Yes"
merged_restaurant_data[43,18]="Yes"
merged_restaurant_data[289,18]="Yes"
merged_restaurant_data[202,18]="Yes"
merged_restaurant_data[388,18]="Yes"
merged_restaurant_data[280,18]="Yes"
merged_restaurant_data[516,18]="Yes"
merged_restaurant_data[369,18]="Yes"
merged_restaurant_data[346,18]="Yes"
merged_restaurant_data[91,18]="Yes"
merged_restaurant_data[604,18]="Yes"
merged_restaurant_data[353,18]="Yes"
merged_restaurant_data[123,18]="Yes"
merged_restaurant_data[538,18]="Yes"
merged_restaurant_data[611,18]="Yes"
merged_restaurant_data[82,18]="Yes"
merged_restaurant_data[642,18]="Yes"
merged_restaurant_data[473,18]="Yes"
merged_restaurant_data[61,18]="Yes"
merged_restaurant_data[247,18]="Yes"
merged_restaurant_data[24,18]="Yes"
merged_restaurant_data[127,18]="Yes"
merged_restaurant_data[186,18]="Yes"
merged_restaurant_data[624,18]="Yes"
merged_restaurant_data[59,18]="Yes"
merged_restaurant_data[64,18]="Yes"
merged_restaurant_data[176,18]="Yes"
merged_restaurant_data[89,18]="Yes"
merged_restaurant_data[256,18]="Yes"
merged_restaurant_data[141,18]="Yes"
merged_restaurant_data[410,18]="Yes"
merged_restaurant_data[497,18]="Yes"
merged_restaurant_data[394,18]="Yes"
merged_restaurant_data[221,18]="Yes"
merged_restaurant_data[210,18]="Yes"
merged_restaurant_data[436,18]="Yes"
merged_restaurant_data[135,18]="Yes"
merged_restaurant_data[332,18]="Yes"
merged_restaurant_data[85,18]="Yes"
merged_restaurant_data[571,18]="Yes"
merged_restaurant_data[526,18]="Yes"
merged_restaurant_data[18,18]="Yes"
merged_restaurant_data[51,18]="Yes"
merged_restaurant_data[172,18]="Yes"
merged_restaurant_data[49,18]="Yes"
merged_restaurant_data[212,18]="Yes"
merged_restaurant_data[262,18]="Yes"
merged_restaurant_data[328,18]="Yes"
merged_restaurant_data[34,18]="Yes"
merged_restaurant_data[131,18]="Yes"
merged_restaurant_data[246,18]="Yes"
merged_restaurant_data[155,18]="Yes"
merged_restaurant_data[600,18]="Yes"

merged_restaurant_data<- merged_restaurant_data %>%
  mutate(Rating_Group = case_when(
    Rating <= 3.9 ~ "Low",
    Rating >= 4.0 & Rating <= 4.5 ~ "Average",
    Rating >= 4.6 ~ "High"
    )
  )

merged_restaurant_data<- merged_restaurant_data[-(623:642),]

view(merged_restaurant_data)
```

```{r}
#| include: false
contingency_table <- xtabs(~Rating_Group+Near_Museum, data=merged_restaurant_data)
contingency_table

contingency_table_check<- merged_restaurant_data %>%
  tabyl(Rating_Group, Near_Museum) %>%
  adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 1) %>%
  adorn_ns()
contingency_table_check
```

```{r}
#| label: Bar Graph of Goal 1
#| echo: false
Visual_1<- ggplot(merged_restaurant_data, aes(x = Near_Museum, fill = Rating_Group)) +
  geom_bar(position = "fill") + 
  labs(
    title = "Proportion of Rating Groups by if Restaurants are Near Museums",
    y = "Proportion of rating Groups ",
    x = "Near Museum?"
  ) +
  theme_solarized()
Visual_1
```

## Chi-Square Analysis for Goal 1

```{r}
#| include: false
library(readr)
library(tidyr)
library(dplyr)
library(tidyverse)
library(stringr)
library(readxl)
library(janitor)
library(ggthemes)
library(rcompanion)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(htmltools)

endpoint<- "https://data.cityofnewyork.us/resource/fn6f-htvy.json"
resp <- httr::GET(endpoint)
museum_data <- jsonlite::fromJSON(httr::content(resp, as = "text"), flatten = TRUE)



endpoint_1<-"https://data.cityofnewyork.us/resource/43nn-pn8j.json"
resp1 <- httr::GET(endpoint_1)
restaurant_data <- jsonlite::fromJSON(httr::content(resp1, as = "text"), flatten = TRUE)


restaurant_rating_data <- read_parquet(here("data", "raw", "restaurant_rating_data.parquet"),as_data_frame = TRUE )
```

```{r}
#| include: false
restaurant_rating_data$lat_new<- shQuote(restaurant_rating_data$Lat)
restaurant_rating_data$lon_new<- shQuote(restaurant_rating_data$Lon)
restaurant_rating_data$location.coordinates<- paste("c", "(", restaurant_rating_data$lon_new, ",", restaurant_rating_data$lat_new, ")", sep = "")

restaurant_rating_data <- restaurant_rating_data[-c(1, 2, 4, 5, 6, 8, 10, 11, 12, 15, 16, 26, 28, 32, 33,37, 38, 42, 45, 46, 47, 48, 50, 51, 57, 58, 61, 62, 63, 66, 68, 69, 74, 75, 79, 82, 85, 86, 89, 90, 93, 94, 95, 96, 97, 98, 99, 100, 103, 104, 105, 110, 111, 113, 117, 118, 119, 120, 128, 131, 133, 134, 138, 140, 144, 147, 151, 152, 153, 160, 165, 168, 174, 175, 176, 178, 179, 182, 183, 184, 186, 190, 192, 193, 195, 197, 198, 203, 204, 206, 208, 209, 212, 216, 218, 220, 223, 224, 225, 231, 232, 234, 236, 241, 244, 247, 249, 251, 254, 256, 265, 267, 268, 271, 274, 277, 283, 284, 285, 288, 289, 292, 294, 295, 297, 298, 299, 300, 301, 304, 305, 308, 310, 312, 315, 318, 320, 321, 322, 323, 325, 326, 328, 330, 331, 332, 334, 335, 337, 338, 339, 340, 341, 343, 345, 346, 348, 349, 350, 351, 353, 355, 356, 357, 359, 362, 363, 365, 366, 367, 370, 375, 376, 377, 378, 379, 380, 388, 389, 390, 391, 392, 393, 396, 399, 403, 406, 411, 415, 416, 417, 418, 420, 422, 423, 424, 425, 427, 429, 430, 432, 433, 435, 438, 439, 441, 442, 443, 444, 447, 449, 451, 454, 455, 457, 461, 463, 467, 469, 470, 472, 473, 474, 477, 478, 479, 483, 484, 488, 489, 491, 495, 497, 499, 500, 501, 506, 507, 508, 509, 510, 513, 514, 516, 520, 521, 522, 523, 525, 527, 528, 529, 532, 533, 537, 538, 539, 540, 543, 544, 546, 547, 549, 550, 552, 553, 554, 555, 556, 558, 560, 561, 562, 566, 567, 568, 569, 570, 571, 572, 575, 577, 578, 579, 580, 581, 582, 587, 589, 590, 591, 592, 595, 598, 599, 600, 607, 608, 610, 611, 612, 613, 614, 615, 618, 620, 621, 622, 624, 625, 626, 627, 631, 633, 635, 636, 637, 638, 640, 641, 646, 648, 653, 655, 657, 658, 660, 661, 663, 669, 670), ]
```

```{r}
#| include: false
is.character(restaurant_data$location.coordinates)
restaurant_data<- restaurant_data %>% mutate(location.coordinates = as.character(location.coordinates))

merged_restaurant_data<- full_join(restaurant_data, restaurant_rating_data, by = "location.coordinates")

sum(merged_restaurant_data$location.coordinates == "NULL", na.rm = TRUE)

merged_restaurant_data <-merged_restaurant_data[merged_restaurant_data$location.coordinates != "NULL", ]
```

```{r}
#| include: false
merged_restaurant_data[2,35]=4.7
merged_restaurant_data[3,35]=4.8
merged_restaurant_data[4,35]=4.0
merged_restaurant_data[6,35]=4.7
merged_restaurant_data[11,35]=4.9
merged_restaurant_data[13,35]=4.5
merged_restaurant_data[14,35]=4.1
merged_restaurant_data[16,35]=4.4
merged_restaurant_data[17,35]=4.8
merged_restaurant_data[18,35]=4.9
merged_restaurant_data[21,35]=4.2
merged_restaurant_data[22,35]=5.0
merged_restaurant_data[27,35]=4.4
merged_restaurant_data[28,35]=4.9
merged_restaurant_data[31,35]=4.4
merged_restaurant_data[32,35]=4.8
merged_restaurant_data[35,35]=4.4
merged_restaurant_data[39,35]=4.5
merged_restaurant_data[40,35]=4.6
merged_restaurant_data[44,35]=5.0
merged_restaurant_data[48,35]=5.0
merged_restaurant_data[49,35]=4.4 
merged_restaurant_data[50,35]=3.8
merged_restaurant_data[55,35]=4.9
merged_restaurant_data[58,35]=4.1
merged_restaurant_data[59,35]=4.3
merged_restaurant_data[61,35]=4.1
merged_restaurant_data[62,35]=4.4
merged_restaurant_data[63,35]=4.4
merged_restaurant_data[64,35]=3.8
merged_restaurant_data[67,35]=4.9
merged_restaurant_data[69,35]=4.6
merged_restaurant_data[73,35]=4.8
merged_restaurant_data[78,35]=5.0
merged_restaurant_data[82,35]=4.6
merged_restaurant_data[94,35]=4.8
merged_restaurant_data[96,35]=4.8
merged_restaurant_data[98,35]=4.2
merged_restaurant_data[103,35]=4.5
merged_restaurant_data[104,35]=4.9
merged_restaurant_data[105,35]=2.7
merged_restaurant_data[111,35]=4.1
merged_restaurant_data[113,35]=4.6
merged_restaurant_data[114,35]=4.4
merged_restaurant_data[115,35]=2.0
merged_restaurant_data[118,35]=4.6
merged_restaurant_data[130,35]=4.6
merged_restaurant_data[133,35]=3.0
merged_restaurant_data[134,35]=4.1
merged_restaurant_data[136,35]=4.7
merged_restaurant_data[142,35]=4.7
merged_restaurant_data[144,35]=4.0
merged_restaurant_data[146,35]=4.0
merged_restaurant_data[148,35]=3.5
merged_restaurant_data[150,35]=4.3
merged_restaurant_data[152,35]=4.8
merged_restaurant_data[153,35]=4.7
merged_restaurant_data[154,35]=5.0
merged_restaurant_data[159,35]=4.3
merged_restaurant_data[164,35]=4.7
merged_restaurant_data[169,35]=4.2
merged_restaurant_data[172,35]=4.6
merged_restaurant_data[173,35]=4.9
merged_restaurant_data[179,35]=4.7
merged_restaurant_data[180,35]=4.2
merged_restaurant_data[184,35]=4.4
merged_restaurant_data[185,35]=4.9
merged_restaurant_data[186,35]=4.5
merged_restaurant_data[189,35]=4.6
merged_restaurant_data[190,35]=5.0
merged_restaurant_data[191,35]=4.7
merged_restaurant_data[193,35]=4.8
merged_restaurant_data[195,35]=4.6
merged_restaurant_data[197,35]=4.8
merged_restaurant_data[199,35]=5.0
merged_restaurant_data[201,35]=4.5
merged_restaurant_data[207,35]=4.5
merged_restaurant_data[215,35]=4.2
merged_restaurant_data[217,35]=3.8
merged_restaurant_data[219,35]=4.8
merged_restaurant_data[221,35]=4.7
merged_restaurant_data[223,35]=4.6
merged_restaurant_data[229,35]=4.5
merged_restaurant_data[232,35]=4.7
merged_restaurant_data[233,35]=4.1
merged_restaurant_data[235,35]=4.6
merged_restaurant_data[236,35]=4.4
merged_restaurant_data[237,35]=4.3
merged_restaurant_data[241,35]=4.7
merged_restaurant_data[243,35]=4.5
merged_restaurant_data[245,35]=5.0
merged_restaurant_data[246,35]=4.7
merged_restaurant_data[260,35]=4.6
merged_restaurant_data[262,35]=4.3
merged_restaurant_data[270,35]=4.1
merged_restaurant_data[271,35]=4.9
merged_restaurant_data[273,35]=4.4
merged_restaurant_data[275,35]=4.9
merged_restaurant_data[278,35]=4.1
merged_restaurant_data[279,35]=4.5
merged_restaurant_data[280,35]=4.6
merged_restaurant_data[285,35]=4.3
merged_restaurant_data[286,35]=4.7
merged_restaurant_data[287,35]=4.8
merged_restaurant_data[288,35]=4.9
merged_restaurant_data[297,35]=4.5
merged_restaurant_data[304,35]=4.5
merged_restaurant_data[305,35]=4.7
merged_restaurant_data[308,35]=4.0
merged_restaurant_data[310,35]=4.5
merged_restaurant_data[314,35]=4.4
merged_restaurant_data[315,35]=4.7
merged_restaurant_data[319,35]=4.8
merged_restaurant_data[321,35]=4.9
merged_restaurant_data[322,35]=4.2 
merged_restaurant_data[328,35]=5.0
merged_restaurant_data[330,35]=4.6
merged_restaurant_data[335,35]=4.6
merged_restaurant_data[341,35]=5.0
merged_restaurant_data[342,35]=4.2
merged_restaurant_data[344,35]=3.6
merged_restaurant_data[346,35]=4.1
merged_restaurant_data[348,35]=4.9
merged_restaurant_data[350,35]=4.2
merged_restaurant_data[351,35]=4.1
merged_restaurant_data[352,35]=4.5
merged_restaurant_data[353,35]=4.5
merged_restaurant_data[356,35]=4.4
merged_restaurant_data[357,35]=4.3
merged_restaurant_data[358,35]=4.2
merged_restaurant_data[359,35]=4.8
merged_restaurant_data[363,35]=4.5
merged_restaurant_data[364,35]=4.8
merged_restaurant_data[367,35]=4.2
merged_restaurant_data[371,35]=4.6
merged_restaurant_data[374,35]=5.0
merged_restaurant_data[375,35]=3.9
merged_restaurant_data[376,35]=3.9
merged_restaurant_data[379,35]=3.8
merged_restaurant_data[382,35]=3.9
merged_restaurant_data[383,35]=5.0
merged_restaurant_data[384,35]=4.6
merged_restaurant_data[385,35]=4.6
merged_restaurant_data[387,35]=4.3
merged_restaurant_data[389,35]=4.9
merged_restaurant_data[391,35]=4.2
merged_restaurant_data[394,35]=4.5
merged_restaurant_data[395,35]=4.5
merged_restaurant_data[397,35]=4.8
merged_restaurant_data[404,35]=4.4
merged_restaurant_data[406,35]=4.5
merged_restaurant_data[408,35]=4.4
merged_restaurant_data[410,35]=3.8
merged_restaurant_data[411,35]=4.8
merged_restaurant_data[414,35]=3.9
merged_restaurant_data[416,35]=4.9
merged_restaurant_data[420,35]=4.6
merged_restaurant_data[422,35]=4.0
merged_restaurant_data[427,35]=4.8
merged_restaurant_data[433,35]=4.7
merged_restaurant_data[436,35]=3.7
merged_restaurant_data[437,35]=4.3
merged_restaurant_data[438,35]=4.6
merged_restaurant_data[440,35]=4.6
merged_restaurant_data[446,35]=4.7
merged_restaurant_data[452,35]=4.1
merged_restaurant_data[453,35]=4.3
merged_restaurant_data[454,35]=5.0
merged_restaurant_data[458,35]=4.3
merged_restaurant_data[459,35]=3.9
merged_restaurant_data[463,35]=4.0
merged_restaurant_data[467,35]=4.9
merged_restaurant_data[470,35]=4.0
merged_restaurant_data[471,35]=4.1
merged_restaurant_data[472,35]=4.0
merged_restaurant_data[486,35]=4.3
merged_restaurant_data[489,35]=5.0
merged_restaurant_data[494,35]=5.0
merged_restaurant_data[495,35]=4.9
merged_restaurant_data[496,35]=4.3
merged_restaurant_data[497,35]=4.2
merged_restaurant_data[501,35]=5.0
merged_restaurant_data[502,35]=4.1
merged_restaurant_data[506,35]=4.6
merged_restaurant_data[507,35]=4.6
merged_restaurant_data[509,35]=4.7
merged_restaurant_data[511,35]=4.5
merged_restaurant_data[512,35]=4.5
merged_restaurant_data[513,35]=3.3
merged_restaurant_data[515,35]=4.9
merged_restaurant_data[519,35]=4.8
merged_restaurant_data[520,35]=4.5
merged_restaurant_data[522,35]=4.9
merged_restaurant_data[523,35]=4.8
merged_restaurant_data[528,35]=4.9
merged_restaurant_data[533,35]=4.3
merged_restaurant_data[543,35]=4.6
merged_restaurant_data[546,35]=4.0
merged_restaurant_data[550,35]=4.8
merged_restaurant_data[552,35]=4.3
merged_restaurant_data[554,35]=3.7
merged_restaurant_data[555,35]=2.1
merged_restaurant_data[556,35]=4.7
merged_restaurant_data[557,35]=4.5
merged_restaurant_data[558,35]=5.0
merged_restaurant_data[562,35]=4.1
merged_restaurant_data[563,35]=4.3
merged_restaurant_data[566,35]=4.3
merged_restaurant_data[567,35]=4.5
merged_restaurant_data[568,35]=4.9
merged_restaurant_data[570,35]=4.3
merged_restaurant_data[573,35]=4.6
merged_restaurant_data[574,35]=4.1
merged_restaurant_data[575,35]=4.8
merged_restaurant_data[578,35]=4.4
merged_restaurant_data[581,35]=4.0
merged_restaurant_data[590,35]=4.1
merged_restaurant_data[592,35]=5.0
merged_restaurant_data[598,35]=3.9
merged_restaurant_data[601,35]=4.2
merged_restaurant_data[605,35]=4.6
merged_restaurant_data[608,35]=4.1
merged_restaurant_data[610,35]=4.1
merged_restaurant_data[613,35]=4.9
merged_restaurant_data[617,35]=4.4
merged_restaurant_data[622,35]=4.3
merged_restaurant_data[624,35]=4.0
merged_restaurant_data[625,35]=5.0
merged_restaurant_data[632,35]=4.4
merged_restaurant_data[633,35]=4.6
merged_restaurant_data[638,35]=4.2
merged_restaurant_data[640,35]=4.6
merged_restaurant_data[645,35]=4.6
merged_restaurant_data[647,35]=4.5
merged_restaurant_data[651,35]=4.9
merged_restaurant_data[660,35]=5.0
merged_restaurant_data[661,35]=4.7
merged_restaurant_data[662,35]=3.9
merged_restaurant_data[663,35]=4.0
merged_restaurant_data[664,35]=4.4
merged_restaurant_data[666,35]=4.3
merged_restaurant_data[677,35]=4.2
merged_restaurant_data[683,35]=4.5
merged_restaurant_data[686,35]=4.3
merged_restaurant_data[688,35]=4.8
merged_restaurant_data[689,35]=4.9
merged_restaurant_data[692,35]=4.9
merged_restaurant_data[693,35]=3.8
merged_restaurant_data[697,35]=4.9
merged_restaurant_data[700,35]=4.0
merged_restaurant_data[702,35]=4.8
merged_restaurant_data[714,35]=4.6
merged_restaurant_data[718,35]=4.6
merged_restaurant_data[719,35]=4.5
merged_restaurant_data[725,35]=4.5
merged_restaurant_data[728,35]=4.7
merged_restaurant_data[729,35]=4.8
merged_restaurant_data[731,35]=4.7
merged_restaurant_data[732,35]=4.2
merged_restaurant_data[733,35]=4.4
merged_restaurant_data[734,35]=3.8
merged_restaurant_data[735,35]=4.5
merged_restaurant_data[737,35]=4.5
merged_restaurant_data[738,35]=4.6
merged_restaurant_data[741,35]=3.8
merged_restaurant_data[744,35]=4.9
merged_restaurant_data[746,35]=4.3
merged_restaurant_data[747,35]=4.2
merged_restaurant_data[752,35]=3.7
merged_restaurant_data[755,35]=4.5
merged_restaurant_data[759,35]=4.0
merged_restaurant_data[762,35]=4.8
merged_restaurant_data[764,35]=4.3
merged_restaurant_data[767,35]=4.4
merged_restaurant_data[769,35]=4.3
merged_restaurant_data[770,35]=4.9
merged_restaurant_data[772,35]=4.0
merged_restaurant_data[774,35]=4.9
merged_restaurant_data[777,35]=4.8
merged_restaurant_data[779,35]=4.1
merged_restaurant_data[780,35]=4.4
merged_restaurant_data[782,35]=4.6
merged_restaurant_data[784,35]=4.1
merged_restaurant_data[785,35]=5.0
merged_restaurant_data[787,35]=4.1
merged_restaurant_data[788,35]=4.8
merged_restaurant_data[790,35]=4.1
merged_restaurant_data[791,35]=3.8
merged_restaurant_data[793,35]=4.4
merged_restaurant_data[796,35]=4.6
merged_restaurant_data[799,35]=5.0
merged_restaurant_data[802,35]=4.3
merged_restaurant_data[807,35]=4.2
merged_restaurant_data[809,35]=4.3
merged_restaurant_data[810,35]=3.9
merged_restaurant_data[811,35]=4.4
merged_restaurant_data[812,35]=4.5
merged_restaurant_data[816,35]=5.0
merged_restaurant_data[820,35]=4.6
merged_restaurant_data[825,35]=4.9
merged_restaurant_data[827,35]=4.8
merged_restaurant_data[828,35]=5.0
merged_restaurant_data[830,35]=4.5
merged_restaurant_data[834,35]=4.4
merged_restaurant_data[837,35]=4.3
merged_restaurant_data[838,35]=5.0
merged_restaurant_data[839,35]=3.0
merged_restaurant_data[841,35]=3.0
merged_restaurant_data[842,35]=4.6
merged_restaurant_data[852,35]=5.0
merged_restaurant_data[855,35]=4.9
merged_restaurant_data[856,35]=4.1
merged_restaurant_data[859,35]=4.5
merged_restaurant_data[861,35]=4.8
merged_restaurant_data[865,35]=4.6
merged_restaurant_data[868,35]=4.8
merged_restaurant_data[869,35]=5.0
merged_restaurant_data[870,35]=4.6
merged_restaurant_data[871,35]=4.1
merged_restaurant_data[872,35]=4.4
merged_restaurant_data[878,35]=4.4
merged_restaurant_data[883,35]=4.6
merged_restaurant_data[884,35]=4.3
merged_restaurant_data[889,35]=4.6
merged_restaurant_data[891,35]=4.4
merged_restaurant_data[893,35]=4.5
merged_restaurant_data[894,35]=4.5
merged_restaurant_data[896,35]=3.2
merged_restaurant_data[897,35]=3.8
merged_restaurant_data[899,35]=3.8
merged_restaurant_data[901,35]=4.6
merged_restaurant_data[902,35]=4.1
merged_restaurant_data[905,35]=3.7
merged_restaurant_data[906,35]=4.6
merged_restaurant_data[907,35]=4.5
merged_restaurant_data[909,35]=4.9
merged_restaurant_data[910,35]=4.1
merged_restaurant_data[913,35]=3.0
merged_restaurant_data[916,35]=4.8
merged_restaurant_data[920,35]=4.2
merged_restaurant_data[921,35]=4.3
merged_restaurant_data[924,35]=4.9
merged_restaurant_data[925,35]=5.0
merged_restaurant_data[929,35]=3.5
merged_restaurant_data[930,35]=4.8
merged_restaurant_data[933,35]=3.8
merged_restaurant_data[936,35]=4.4
merged_restaurant_data[939,35]=4.4
merged_restaurant_data[940,35]=4.3
merged_restaurant_data[941,35]=4.6
merged_restaurant_data[942,35]=4.6
merged_restaurant_data[943,35]=4.2
merged_restaurant_data[945,35]=3.8
merged_restaurant_data[946,35]=4.6
merged_restaurant_data[948,35]=4.6
merged_restaurant_data[951,35]=3.4
merged_restaurant_data[953,35]=4.9
merged_restaurant_data[954,35]=4.3
merged_restaurant_data[955,35]=3.2
merged_restaurant_data[957,35]=4.5
merged_restaurant_data[961,35]=4.5
merged_restaurant_data[962,35]=4.9
merged_restaurant_data[965,35]=4.4
merged_restaurant_data[968,35]=4.1
merged_restaurant_data[970,35]=4.4
merged_restaurant_data[971,35]=4.7
merged_restaurant_data[972,35]=4.6
merged_restaurant_data[974,35]=3.5
merged_restaurant_data[975,35]=4.5
merged_restaurant_data[977,35]=4.7
merged_restaurant_data[979,35]=4.2
merged_restaurant_data[981,35]=4.8
merged_restaurant_data[982,35]=4.4
merged_restaurant_data[984,35]=4.4
merged_restaurant_data[986,35]=4.3
merged_restaurant_data[987,35]=4.3
merged_restaurant_data[988,35]=4.6
merged_restaurant_data[989,35]=2.7
merged_restaurant_data[991,35]=4.7
merged_restaurant_data[992,35]=4.3
merged_restaurant_data[993,35]=4.1
merged_restaurant_data[997,35]=4.8
merged_restaurant_data[998,35]=4.8
merged_restaurant_data[999,35]=4.4

sum(is.na(merged_restaurant_data$Rating))

merged_restaurant_data<- merged_restaurant_data %>%
  filter(!is.na(Rating))

merged_restaurant_data$dba<- str_to_title(merged_restaurant_data$dba)

merged_restaurant_data$Restaurant_Name <-
  paste(
    coalesce(merged_restaurant_data$dba, ""),
    coalesce(merged_restaurant_data$Name, "")
  )
```

```{r}
#| include: false
merged_restaurant_data <- merged_restaurant_data %>% select(-dba, -boro, -building, -street, -zipcode, -phone, -community_board, -council_district, -census_tract, -bbl, -nta, -`:@computed_region_f5dn_yrer`, -`:@computed_region_yeji_bk3q`, -`:@computed_region_sbqj_enih`, -`:@computed_region_92fq_4b7q`, -cuisine_description, -bin, -grade, -grade_date, -URL, -Name, -`Rating Count`, -`Detailed Ratings`, -`Price Category`, -Address, -ZipCode)

str(merged_restaurant_data$Lat)

str(merged_restaurant_data$latitude)

merged_restaurant_data$latitude<-as.numeric(merged_restaurant_data$latitude)

merged_restaurant_data$Lat<-as.numeric(merged_restaurant_data$Lat)

merged_restaurant_data$Latitude <-
  coalesce(
    merged_restaurant_data$latitude, merged_restaurant_data$Lat
  )

merged_restaurant_data <- merged_restaurant_data %>% select(-Lat, -latitude)

str(merged_restaurant_data$Lon)

str(merged_restaurant_data$longitude)

merged_restaurant_data$Lon<-as.numeric(merged_restaurant_data$Lon)

merged_restaurant_data$longitude<-as.numeric(merged_restaurant_data$longitude)

merged_restaurant_data$Longitude <-
  coalesce(
    merged_restaurant_data$longitude, merged_restaurant_data$Lon
  )

merged_restaurant_data <- merged_restaurant_data %>% select(-Lon, -longitude)
```

```{r}
#| include: false
museum_data<- museum_data %>%
  select(-tel, -url, -adress1, -address2)

museum_data<- museum_data %>%
  mutate(
    cleaned_geom_coordinates = gsub("c\\(|\\)|\"", "", the_geom.coordinates)
    )

museum_data<-museum_data %>%
  separate(
    col = cleaned_geom_coordinates,
    into = c("Longitude", "Latitude"),
    sep = ","
  )

museum_data$Longitude<- as.numeric(museum_data$Longitude)

museum_data$Latitude<- 
  as.numeric(museum_data$Latitude)
```

```{r}
#| label: Chi-Square Analysis 
#| include: false
merged_restaurant_data$Near_Museum<- ""

merged_restaurant_data[,18]="No"
merged_restaurant_data[14,18]="Yes"
merged_restaurant_data[629,18]="Yes"
merged_restaurant_data[458,18]="Yes"
merged_restaurant_data[389,18]="Yes"
merged_restaurant_data[490,18]="Yes"
merged_restaurant_data[550,18]="Yes"
merged_restaurant_data[48,18]="Yes"
merged_restaurant_data[411,18]="Yes"
merged_restaurant_data[361,18]="Yes"
merged_restaurant_data[471,18]="Yes"
merged_restaurant_data[456,18]="Yes"
merged_restaurant_data[553,18]="Yes"
merged_restaurant_data[404,18]="Yes"
merged_restaurant_data[562,18]="Yes"
merged_restaurant_data[288,18]="Yes"
merged_restaurant_data[487,18]="Yes"
merged_restaurant_data[460,18]="Yes"
merged_restaurant_data[579,18]="Yes"
merged_restaurant_data[620,18]="Yes"
merged_restaurant_data[309,18]="Yes"
merged_restaurant_data[244,18]="Yes"
merged_restaurant_data[439,18]="Yes"
merged_restaurant_data[507,18]="Yes"
merged_restaurant_data[381,18]="Yes"
merged_restaurant_data[355,18]="Yes"
merged_restaurant_data[433,18]="Yes"
merged_restaurant_data[513,18]="Yes"
merged_restaurant_data[238,18]="Yes"
merged_restaurant_data[590,18]="Yes"
merged_restaurant_data[120,18]="Yes"
merged_restaurant_data[143,18]="Yes"
merged_restaurant_data[259,18]="Yes"
merged_restaurant_data[118,18]="Yes"
merged_restaurant_data[43,18]="Yes"
merged_restaurant_data[289,18]="Yes"
merged_restaurant_data[202,18]="Yes"
merged_restaurant_data[388,18]="Yes"
merged_restaurant_data[280,18]="Yes"
merged_restaurant_data[516,18]="Yes"
merged_restaurant_data[369,18]="Yes"
merged_restaurant_data[346,18]="Yes"
merged_restaurant_data[91,18]="Yes"
merged_restaurant_data[604,18]="Yes"
merged_restaurant_data[353,18]="Yes"
merged_restaurant_data[123,18]="Yes"
merged_restaurant_data[538,18]="Yes"
merged_restaurant_data[611,18]="Yes"
merged_restaurant_data[82,18]="Yes"
merged_restaurant_data[642,18]="Yes"
merged_restaurant_data[473,18]="Yes"
merged_restaurant_data[61,18]="Yes"
merged_restaurant_data[247,18]="Yes"
merged_restaurant_data[24,18]="Yes"
merged_restaurant_data[127,18]="Yes"
merged_restaurant_data[186,18]="Yes"
merged_restaurant_data[624,18]="Yes"
merged_restaurant_data[59,18]="Yes"
merged_restaurant_data[64,18]="Yes"
merged_restaurant_data[176,18]="Yes"
merged_restaurant_data[89,18]="Yes"
merged_restaurant_data[256,18]="Yes"
merged_restaurant_data[141,18]="Yes"
merged_restaurant_data[410,18]="Yes"
merged_restaurant_data[497,18]="Yes"
merged_restaurant_data[394,18]="Yes"
merged_restaurant_data[221,18]="Yes"
merged_restaurant_data[210,18]="Yes"
merged_restaurant_data[436,18]="Yes"
merged_restaurant_data[135,18]="Yes"
merged_restaurant_data[332,18]="Yes"
merged_restaurant_data[85,18]="Yes"
merged_restaurant_data[571,18]="Yes"
merged_restaurant_data[526,18]="Yes"
merged_restaurant_data[18,18]="Yes"
merged_restaurant_data[51,18]="Yes"
merged_restaurant_data[172,18]="Yes"
merged_restaurant_data[49,18]="Yes"
merged_restaurant_data[212,18]="Yes"
merged_restaurant_data[262,18]="Yes"
merged_restaurant_data[328,18]="Yes"
merged_restaurant_data[34,18]="Yes"
merged_restaurant_data[131,18]="Yes"
merged_restaurant_data[246,18]="Yes"
merged_restaurant_data[155,18]="Yes"
merged_restaurant_data[600,18]="Yes"

merged_restaurant_data<- merged_restaurant_data %>%
  mutate(Rating_Group = case_when(
    Rating <= 3.9 ~ "Low",
    Rating >= 4.0 & Rating <= 4.5 ~ "Average",
    Rating >= 4.6 ~ "High"
    )
  )

merged_restaurant_data<- merged_restaurant_data[-(623:642),]

view(merged_restaurant_data)
```

```{r}
#| label: Contingency Table
#| include: false
contingency_table <- xtabs(~Rating_Group+Near_Museum, data=merged_restaurant_data)
contingency_table

contingency_table_check<- merged_restaurant_data %>%
  tabyl(Rating_Group, Near_Museum) %>%
  adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 1) %>%
  adorn_ns()
contingency_table_check
```

```{r}
#| echo: false
chi_square_test<- chisq.test(contingency_table)
chi_square_test

cramerV(contingency_table)
```

-   The chi-square test shows X\^2 = 0.64691 (0.65), df = 2, p = 0.7236 (0.72)

-   There is **not** a statistically significant relationship between restaurants being near museums and rating.

-   Cramer's V tells us that the relationship is weak in strength.

## Goal 2: Visualizing the Analysis

We are visualizing the proportion of if a restaurant ever had violations (None, Critical) by if restaurants are near museums (yes,no).

```{r}
#| include: false
library(readr)
library(tidyr)
library(dplyr)
library(tidyverse)
library(stringr)
library(readxl)
library(janitor)
library(ggthemes)
library(rcompanion)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(htmltools)

endpoint<- "https://data.cityofnewyork.us/resource/fn6f-htvy.json"
resp <- httr::GET(endpoint)
museum_data <- jsonlite::fromJSON(httr::content(resp, as = "text"), flatten = TRUE)



endpoint_1<-"https://data.cityofnewyork.us/resource/43nn-pn8j.json"
resp1 <- httr::GET(endpoint_1)
restaurant_data <- jsonlite::fromJSON(httr::content(resp1, as = "text"), flatten = TRUE)


restaurant_rating_data <- read_parquet(here("data", "raw", "restaurant_rating_data.parquet"), as_data_frame = TRUE )
```

```{r}
#| include: false
restaurant_rating_data$lat_new<- shQuote(restaurant_rating_data$Lat)
restaurant_rating_data$lon_new<- shQuote(restaurant_rating_data$Lon)
restaurant_rating_data$location.coordinates<- paste("c", "(", restaurant_rating_data$lon_new, ",", restaurant_rating_data$lat_new, ")", sep = "")

restaurant_rating_data <- restaurant_rating_data[-c(1, 2, 4, 5, 6, 8, 10, 11, 12, 15, 16, 26, 28, 32, 33,37, 38, 42, 45, 46, 47, 48, 50, 51, 57, 58, 61, 62, 63, 66, 68, 69, 74, 75, 79, 82, 85, 86, 89, 90, 93, 94, 95, 96, 97, 98, 99, 100, 103, 104, 105, 110, 111, 113, 117, 118, 119, 120, 128, 131, 133, 134, 138, 140, 144, 147, 151, 152, 153, 160, 165, 168, 174, 175, 176, 178, 179, 182, 183, 184, 186, 190, 192, 193, 195, 197, 198, 203, 204, 206, 208, 209, 212, 216, 218, 220, 223, 224, 225, 231, 232, 234, 236, 241, 244, 247, 249, 251, 254, 256, 265, 267, 268, 271, 274, 277, 283, 284, 285, 288, 289, 292, 294, 295, 297, 298, 299, 300, 301, 304, 305, 308, 310, 312, 315, 318, 320, 321, 322, 323, 325, 326, 328, 330, 331, 332, 334, 335, 337, 338, 339, 340, 341, 343, 345, 346, 348, 349, 350, 351, 353, 355, 356, 357, 359, 362, 363, 365, 366, 367, 370, 375, 376, 377, 378, 379, 380, 388, 389, 390, 391, 392, 393, 396, 399, 403, 406, 411, 415, 416, 417, 418, 420, 422, 423, 424, 425, 427, 429, 430, 432, 433, 435, 438, 439, 441, 442, 443, 444, 447, 449, 451, 454, 455, 457, 461, 463, 467, 469, 470, 472, 473, 474, 477, 478, 479, 483, 484, 488, 489, 491, 495, 497, 499, 500, 501, 506, 507, 508, 509, 510, 513, 514, 516, 520, 521, 522, 523, 525, 527, 528, 529, 532, 533, 537, 538, 539, 540, 543, 544, 546, 547, 549, 550, 552, 553, 554, 555, 556, 558, 560, 561, 562, 566, 567, 568, 569, 570, 571, 572, 575, 577, 578, 579, 580, 581, 582, 587, 589, 590, 591, 592, 595, 598, 599, 600, 607, 608, 610, 611, 612, 613, 614, 615, 618, 620, 621, 622, 624, 625, 626, 627, 631, 633, 635, 636, 637, 638, 640, 641, 646, 648, 653, 655, 657, 658, 660, 661, 663, 669, 670), ]
```

```{r}
#| include: false
is.character(restaurant_data$location.coordinates)
restaurant_data<- restaurant_data %>% mutate(location.coordinates = as.character(location.coordinates))

merged_restaurant_data<- full_join(restaurant_data, restaurant_rating_data, by = "location.coordinates")

sum(merged_restaurant_data$location.coordinates == "NULL", na.rm = TRUE)

merged_restaurant_data <-merged_restaurant_data[merged_restaurant_data$location.coordinates != "NULL", ]
```

```{r}
#| include: false
merged_restaurant_data[2,35]=4.7
merged_restaurant_data[3,35]=4.8
merged_restaurant_data[4,35]=4.0
merged_restaurant_data[6,35]=4.7
merged_restaurant_data[11,35]=4.9
merged_restaurant_data[13,35]=4.5
merged_restaurant_data[14,35]=4.1
merged_restaurant_data[16,35]=4.4
merged_restaurant_data[17,35]=4.8
merged_restaurant_data[18,35]=4.9
merged_restaurant_data[21,35]=4.2
merged_restaurant_data[22,35]=5.0
merged_restaurant_data[27,35]=4.4
merged_restaurant_data[28,35]=4.9
merged_restaurant_data[31,35]=4.4
merged_restaurant_data[32,35]=4.8
merged_restaurant_data[35,35]=4.4
merged_restaurant_data[39,35]=4.5
merged_restaurant_data[40,35]=4.6
merged_restaurant_data[44,35]=5.0
merged_restaurant_data[48,35]=5.0
merged_restaurant_data[49,35]=4.4 
merged_restaurant_data[50,35]=3.8
merged_restaurant_data[55,35]=4.9
merged_restaurant_data[58,35]=4.1
merged_restaurant_data[59,35]=4.3
merged_restaurant_data[61,35]=4.1
merged_restaurant_data[62,35]=4.4
merged_restaurant_data[63,35]=4.4
merged_restaurant_data[64,35]=3.8
merged_restaurant_data[67,35]=4.9
merged_restaurant_data[69,35]=4.6
merged_restaurant_data[73,35]=4.8
merged_restaurant_data[78,35]=5.0
merged_restaurant_data[82,35]=4.6
merged_restaurant_data[94,35]=4.8
merged_restaurant_data[96,35]=4.8
merged_restaurant_data[98,35]=4.2
merged_restaurant_data[103,35]=4.5
merged_restaurant_data[104,35]=4.9
merged_restaurant_data[105,35]=2.7
merged_restaurant_data[111,35]=4.1
merged_restaurant_data[113,35]=4.6
merged_restaurant_data[114,35]=4.4
merged_restaurant_data[115,35]=2.0
merged_restaurant_data[118,35]=4.6
merged_restaurant_data[130,35]=4.6
merged_restaurant_data[133,35]=3.0
merged_restaurant_data[134,35]=4.1
merged_restaurant_data[136,35]=4.7
merged_restaurant_data[142,35]=4.7
merged_restaurant_data[144,35]=4.0
merged_restaurant_data[146,35]=4.0
merged_restaurant_data[148,35]=3.5
merged_restaurant_data[150,35]=4.3
merged_restaurant_data[152,35]=4.8
merged_restaurant_data[153,35]=4.7
merged_restaurant_data[154,35]=5.0
merged_restaurant_data[159,35]=4.3
merged_restaurant_data[164,35]=4.7
merged_restaurant_data[169,35]=4.2
merged_restaurant_data[172,35]=4.6
merged_restaurant_data[173,35]=4.9
merged_restaurant_data[179,35]=4.7
merged_restaurant_data[180,35]=4.2
merged_restaurant_data[184,35]=4.4
merged_restaurant_data[185,35]=4.9
merged_restaurant_data[186,35]=4.5
merged_restaurant_data[189,35]=4.6
merged_restaurant_data[190,35]=5.0
merged_restaurant_data[191,35]=4.7
merged_restaurant_data[193,35]=4.8
merged_restaurant_data[195,35]=4.6
merged_restaurant_data[197,35]=4.8
merged_restaurant_data[199,35]=5.0
merged_restaurant_data[201,35]=4.5
merged_restaurant_data[207,35]=4.5
merged_restaurant_data[215,35]=4.2
merged_restaurant_data[217,35]=3.8
merged_restaurant_data[219,35]=4.8
merged_restaurant_data[221,35]=4.7
merged_restaurant_data[223,35]=4.6
merged_restaurant_data[229,35]=4.5
merged_restaurant_data[232,35]=4.7
merged_restaurant_data[233,35]=4.1
merged_restaurant_data[235,35]=4.6
merged_restaurant_data[236,35]=4.4
merged_restaurant_data[237,35]=4.3
merged_restaurant_data[241,35]=4.7
merged_restaurant_data[243,35]=4.5
merged_restaurant_data[245,35]=5.0
merged_restaurant_data[246,35]=4.7
merged_restaurant_data[260,35]=4.6
merged_restaurant_data[262,35]=4.3
merged_restaurant_data[270,35]=4.1
merged_restaurant_data[271,35]=4.9
merged_restaurant_data[273,35]=4.4
merged_restaurant_data[275,35]=4.9
merged_restaurant_data[278,35]=4.1
merged_restaurant_data[279,35]=4.5
merged_restaurant_data[280,35]=4.6
merged_restaurant_data[285,35]=4.3
merged_restaurant_data[286,35]=4.7
merged_restaurant_data[287,35]=4.8
merged_restaurant_data[288,35]=4.9
merged_restaurant_data[297,35]=4.5
merged_restaurant_data[304,35]=4.5
merged_restaurant_data[305,35]=4.7
merged_restaurant_data[308,35]=4.0
merged_restaurant_data[310,35]=4.5
merged_restaurant_data[314,35]=4.4
merged_restaurant_data[315,35]=4.7
merged_restaurant_data[319,35]=4.8
merged_restaurant_data[321,35]=4.9
merged_restaurant_data[322,35]=4.2 
merged_restaurant_data[328,35]=5.0
merged_restaurant_data[330,35]=4.6
merged_restaurant_data[335,35]=4.6
merged_restaurant_data[341,35]=5.0
merged_restaurant_data[342,35]=4.2
merged_restaurant_data[344,35]=3.6
merged_restaurant_data[346,35]=4.1
merged_restaurant_data[348,35]=4.9
merged_restaurant_data[350,35]=4.2
merged_restaurant_data[351,35]=4.1
merged_restaurant_data[352,35]=4.5
merged_restaurant_data[353,35]=4.5
merged_restaurant_data[356,35]=4.4
merged_restaurant_data[357,35]=4.3
merged_restaurant_data[358,35]=4.2
merged_restaurant_data[359,35]=4.8
merged_restaurant_data[363,35]=4.5
merged_restaurant_data[364,35]=4.8
merged_restaurant_data[367,35]=4.2
merged_restaurant_data[371,35]=4.6
merged_restaurant_data[374,35]=5.0
merged_restaurant_data[375,35]=3.9
merged_restaurant_data[376,35]=3.9
merged_restaurant_data[379,35]=3.8
merged_restaurant_data[382,35]=3.9
merged_restaurant_data[383,35]=5.0
merged_restaurant_data[384,35]=4.6
merged_restaurant_data[385,35]=4.6
merged_restaurant_data[387,35]=4.3
merged_restaurant_data[389,35]=4.9
merged_restaurant_data[391,35]=4.2
merged_restaurant_data[394,35]=4.5
merged_restaurant_data[395,35]=4.5
merged_restaurant_data[397,35]=4.8
merged_restaurant_data[404,35]=4.4
merged_restaurant_data[406,35]=4.5
merged_restaurant_data[408,35]=4.4
merged_restaurant_data[410,35]=3.8
merged_restaurant_data[411,35]=4.8
merged_restaurant_data[414,35]=3.9
merged_restaurant_data[416,35]=4.9
merged_restaurant_data[420,35]=4.6
merged_restaurant_data[422,35]=4.0
merged_restaurant_data[427,35]=4.8
merged_restaurant_data[433,35]=4.7
merged_restaurant_data[436,35]=3.7
merged_restaurant_data[437,35]=4.3
merged_restaurant_data[438,35]=4.6
merged_restaurant_data[440,35]=4.6
merged_restaurant_data[446,35]=4.7
merged_restaurant_data[452,35]=4.1
merged_restaurant_data[453,35]=4.3
merged_restaurant_data[454,35]=5.0
merged_restaurant_data[458,35]=4.3
merged_restaurant_data[459,35]=3.9
merged_restaurant_data[463,35]=4.0
merged_restaurant_data[467,35]=4.9
merged_restaurant_data[470,35]=4.0
merged_restaurant_data[471,35]=4.1
merged_restaurant_data[472,35]=4.0
merged_restaurant_data[486,35]=4.3
merged_restaurant_data[489,35]=5.0
merged_restaurant_data[494,35]=5.0
merged_restaurant_data[495,35]=4.9
merged_restaurant_data[496,35]=4.3
merged_restaurant_data[497,35]=4.2
merged_restaurant_data[501,35]=5.0
merged_restaurant_data[502,35]=4.1
merged_restaurant_data[506,35]=4.6
merged_restaurant_data[507,35]=4.6
merged_restaurant_data[509,35]=4.7
merged_restaurant_data[511,35]=4.5
merged_restaurant_data[512,35]=4.5
merged_restaurant_data[513,35]=3.3
merged_restaurant_data[515,35]=4.9
merged_restaurant_data[519,35]=4.8
merged_restaurant_data[520,35]=4.5
merged_restaurant_data[522,35]=4.9
merged_restaurant_data[523,35]=4.8
merged_restaurant_data[528,35]=4.9
merged_restaurant_data[533,35]=4.3
merged_restaurant_data[543,35]=4.6
merged_restaurant_data[546,35]=4.0
merged_restaurant_data[550,35]=4.8
merged_restaurant_data[552,35]=4.3
merged_restaurant_data[554,35]=3.7
merged_restaurant_data[555,35]=2.1
merged_restaurant_data[556,35]=4.7
merged_restaurant_data[557,35]=4.5
merged_restaurant_data[558,35]=5.0
merged_restaurant_data[562,35]=4.1
merged_restaurant_data[563,35]=4.3
merged_restaurant_data[566,35]=4.3
merged_restaurant_data[567,35]=4.5
merged_restaurant_data[568,35]=4.9
merged_restaurant_data[570,35]=4.3
merged_restaurant_data[573,35]=4.6
merged_restaurant_data[574,35]=4.1
merged_restaurant_data[575,35]=4.8
merged_restaurant_data[578,35]=4.4
merged_restaurant_data[581,35]=4.0
merged_restaurant_data[590,35]=4.1
merged_restaurant_data[592,35]=5.0
merged_restaurant_data[598,35]=3.9
merged_restaurant_data[601,35]=4.2
merged_restaurant_data[605,35]=4.6
merged_restaurant_data[608,35]=4.1
merged_restaurant_data[610,35]=4.1
merged_restaurant_data[613,35]=4.9
merged_restaurant_data[617,35]=4.4
merged_restaurant_data[622,35]=4.3
merged_restaurant_data[624,35]=4.0
merged_restaurant_data[625,35]=5.0
merged_restaurant_data[632,35]=4.4
merged_restaurant_data[633,35]=4.6
merged_restaurant_data[638,35]=4.2
merged_restaurant_data[640,35]=4.6
merged_restaurant_data[645,35]=4.6
merged_restaurant_data[647,35]=4.5
merged_restaurant_data[651,35]=4.9
merged_restaurant_data[660,35]=5.0
merged_restaurant_data[661,35]=4.7
merged_restaurant_data[662,35]=3.9
merged_restaurant_data[663,35]=4.0
merged_restaurant_data[664,35]=4.4
merged_restaurant_data[666,35]=4.3
merged_restaurant_data[677,35]=4.2
merged_restaurant_data[683,35]=4.5
merged_restaurant_data[686,35]=4.3
merged_restaurant_data[688,35]=4.8
merged_restaurant_data[689,35]=4.9
merged_restaurant_data[692,35]=4.9
merged_restaurant_data[693,35]=3.8
merged_restaurant_data[697,35]=4.9
merged_restaurant_data[700,35]=4.0
merged_restaurant_data[702,35]=4.8
merged_restaurant_data[714,35]=4.6
merged_restaurant_data[718,35]=4.6
merged_restaurant_data[719,35]=4.5
merged_restaurant_data[725,35]=4.5
merged_restaurant_data[728,35]=4.7
merged_restaurant_data[729,35]=4.8
merged_restaurant_data[731,35]=4.7
merged_restaurant_data[732,35]=4.2
merged_restaurant_data[733,35]=4.4
merged_restaurant_data[734,35]=3.8
merged_restaurant_data[735,35]=4.5
merged_restaurant_data[737,35]=4.5
merged_restaurant_data[738,35]=4.6
merged_restaurant_data[741,35]=3.8
merged_restaurant_data[744,35]=4.9
merged_restaurant_data[746,35]=4.3
merged_restaurant_data[747,35]=4.2
merged_restaurant_data[752,35]=3.7
merged_restaurant_data[755,35]=4.5
merged_restaurant_data[759,35]=4.0
merged_restaurant_data[762,35]=4.8
merged_restaurant_data[764,35]=4.3
merged_restaurant_data[767,35]=4.4
merged_restaurant_data[769,35]=4.3
merged_restaurant_data[770,35]=4.9
merged_restaurant_data[772,35]=4.0
merged_restaurant_data[774,35]=4.9
merged_restaurant_data[777,35]=4.8
merged_restaurant_data[779,35]=4.1
merged_restaurant_data[780,35]=4.4
merged_restaurant_data[782,35]=4.6
merged_restaurant_data[784,35]=4.1
merged_restaurant_data[785,35]=5.0
merged_restaurant_data[787,35]=4.1
merged_restaurant_data[788,35]=4.8
merged_restaurant_data[790,35]=4.1
merged_restaurant_data[791,35]=3.8
merged_restaurant_data[793,35]=4.4
merged_restaurant_data[796,35]=4.6
merged_restaurant_data[799,35]=5.0
merged_restaurant_data[802,35]=4.3
merged_restaurant_data[807,35]=4.2
merged_restaurant_data[809,35]=4.3
merged_restaurant_data[810,35]=3.9
merged_restaurant_data[811,35]=4.4
merged_restaurant_data[812,35]=4.5
merged_restaurant_data[816,35]=5.0
merged_restaurant_data[820,35]=4.6
merged_restaurant_data[825,35]=4.9
merged_restaurant_data[827,35]=4.8
merged_restaurant_data[828,35]=5.0
merged_restaurant_data[830,35]=4.5
merged_restaurant_data[834,35]=4.4
merged_restaurant_data[837,35]=4.3
merged_restaurant_data[838,35]=5.0
merged_restaurant_data[839,35]=3.0
merged_restaurant_data[841,35]=3.0
merged_restaurant_data[842,35]=4.6
merged_restaurant_data[852,35]=5.0
merged_restaurant_data[855,35]=4.9
merged_restaurant_data[856,35]=4.1
merged_restaurant_data[859,35]=4.5
merged_restaurant_data[861,35]=4.8
merged_restaurant_data[865,35]=4.6
merged_restaurant_data[868,35]=4.8
merged_restaurant_data[869,35]=5.0
merged_restaurant_data[870,35]=4.6
merged_restaurant_data[871,35]=4.1
merged_restaurant_data[872,35]=4.4
merged_restaurant_data[878,35]=4.4
merged_restaurant_data[883,35]=4.6
merged_restaurant_data[884,35]=4.3
merged_restaurant_data[889,35]=4.6
merged_restaurant_data[891,35]=4.4
merged_restaurant_data[893,35]=4.5
merged_restaurant_data[894,35]=4.5
merged_restaurant_data[896,35]=3.2
merged_restaurant_data[897,35]=3.8
merged_restaurant_data[899,35]=3.8
merged_restaurant_data[901,35]=4.6
merged_restaurant_data[902,35]=4.1
merged_restaurant_data[905,35]=3.7
merged_restaurant_data[906,35]=4.6
merged_restaurant_data[907,35]=4.5
merged_restaurant_data[909,35]=4.9
merged_restaurant_data[910,35]=4.1
merged_restaurant_data[913,35]=3.0
merged_restaurant_data[916,35]=4.8
merged_restaurant_data[920,35]=4.2
merged_restaurant_data[921,35]=4.3
merged_restaurant_data[924,35]=4.9
merged_restaurant_data[925,35]=5.0
merged_restaurant_data[929,35]=3.5
merged_restaurant_data[930,35]=4.8
merged_restaurant_data[933,35]=3.8
merged_restaurant_data[936,35]=4.4
merged_restaurant_data[939,35]=4.4
merged_restaurant_data[940,35]=4.3
merged_restaurant_data[941,35]=4.6
merged_restaurant_data[942,35]=4.6
merged_restaurant_data[943,35]=4.2
merged_restaurant_data[945,35]=3.8
merged_restaurant_data[946,35]=4.6
merged_restaurant_data[948,35]=4.6
merged_restaurant_data[951,35]=3.4
merged_restaurant_data[953,35]=4.9
merged_restaurant_data[954,35]=4.3
merged_restaurant_data[955,35]=3.2
merged_restaurant_data[957,35]=4.5
merged_restaurant_data[961,35]=4.5
merged_restaurant_data[962,35]=4.9
merged_restaurant_data[965,35]=4.4
merged_restaurant_data[968,35]=4.1
merged_restaurant_data[970,35]=4.4
merged_restaurant_data[971,35]=4.7
merged_restaurant_data[972,35]=4.6
merged_restaurant_data[974,35]=3.5
merged_restaurant_data[975,35]=4.5
merged_restaurant_data[977,35]=4.7
merged_restaurant_data[979,35]=4.2
merged_restaurant_data[981,35]=4.8
merged_restaurant_data[982,35]=4.4
merged_restaurant_data[984,35]=4.4
merged_restaurant_data[986,35]=4.3
merged_restaurant_data[987,35]=4.3
merged_restaurant_data[988,35]=4.6
merged_restaurant_data[989,35]=2.7
merged_restaurant_data[991,35]=4.7
merged_restaurant_data[992,35]=4.3
merged_restaurant_data[993,35]=4.1
merged_restaurant_data[997,35]=4.8
merged_restaurant_data[998,35]=4.8
merged_restaurant_data[999,35]=4.4

sum(is.na(merged_restaurant_data$Rating))

merged_restaurant_data<- merged_restaurant_data %>%
  filter(!is.na(Rating))

merged_restaurant_data$dba<- str_to_title(merged_restaurant_data$dba)

merged_restaurant_data$Restaurant_Name <-
  paste(
    coalesce(merged_restaurant_data$dba, ""),
    coalesce(merged_restaurant_data$Name, "")
  )
```

```{r}
#| include: false
merged_restaurant_data <- merged_restaurant_data %>% select(-dba, -boro, -building, -street, -zipcode, -phone, -community_board, -council_district, -census_tract, -bbl, -nta, -`:@computed_region_f5dn_yrer`, -`:@computed_region_yeji_bk3q`, -`:@computed_region_sbqj_enih`, -`:@computed_region_92fq_4b7q`, -cuisine_description, -bin, -grade, -grade_date, -URL, -Name, -`Rating Count`, -`Detailed Ratings`, -`Price Category`, -Address, -ZipCode)

str(merged_restaurant_data$Lat)

str(merged_restaurant_data$latitude)

merged_restaurant_data$latitude<-as.numeric(merged_restaurant_data$latitude)

merged_restaurant_data$Lat<-as.numeric(merged_restaurant_data$Lat)

merged_restaurant_data$Latitude <-
  coalesce(
    merged_restaurant_data$latitude, merged_restaurant_data$Lat
  )

merged_restaurant_data <- merged_restaurant_data %>% select(-Lat, -latitude)

str(merged_restaurant_data$Lon)

str(merged_restaurant_data$longitude)

merged_restaurant_data$Lon<-as.numeric(merged_restaurant_data$Lon)

merged_restaurant_data$longitude<-as.numeric(merged_restaurant_data$longitude)

merged_restaurant_data$Longitude <-
  coalesce(
    merged_restaurant_data$longitude, merged_restaurant_data$Lon
  )

merged_restaurant_data <- merged_restaurant_data %>% select(-Lon, -longitude)
```

```{r}
#| include: false
museum_data<- museum_data %>%
  select(-tel, -url, -adress1, -address2)

museum_data<- museum_data %>%
  mutate(
    cleaned_geom_coordinates = gsub("c\\(|\\)|\"", "", the_geom.coordinates)
    )

museum_data<-museum_data %>%
  separate(
    col = cleaned_geom_coordinates,
    into = c("Longitude", "Latitude"),
    sep = ","
  )

museum_data$Longitude<- as.numeric(museum_data$Longitude)

museum_data$Latitude<- 
  as.numeric(museum_data$Latitude)
```

```{r}
#| include: false
merged_restaurant_data$Near_Museum<- ""

merged_restaurant_data[,18]="No"
merged_restaurant_data[14,18]="Yes"
merged_restaurant_data[629,18]="Yes"
merged_restaurant_data[458,18]="Yes"
merged_restaurant_data[389,18]="Yes"
merged_restaurant_data[490,18]="Yes"
merged_restaurant_data[550,18]="Yes"
merged_restaurant_data[48,18]="Yes"
merged_restaurant_data[411,18]="Yes"
merged_restaurant_data[361,18]="Yes"
merged_restaurant_data[471,18]="Yes"
merged_restaurant_data[456,18]="Yes"
merged_restaurant_data[553,18]="Yes"
merged_restaurant_data[404,18]="Yes"
merged_restaurant_data[562,18]="Yes"
merged_restaurant_data[288,18]="Yes"
merged_restaurant_data[487,18]="Yes"
merged_restaurant_data[460,18]="Yes"
merged_restaurant_data[579,18]="Yes"
merged_restaurant_data[620,18]="Yes"
merged_restaurant_data[309,18]="Yes"
merged_restaurant_data[244,18]="Yes"
merged_restaurant_data[439,18]="Yes"
merged_restaurant_data[507,18]="Yes"
merged_restaurant_data[381,18]="Yes"
merged_restaurant_data[355,18]="Yes"
merged_restaurant_data[433,18]="Yes"
merged_restaurant_data[513,18]="Yes"
merged_restaurant_data[238,18]="Yes"
merged_restaurant_data[590,18]="Yes"
merged_restaurant_data[120,18]="Yes"
merged_restaurant_data[143,18]="Yes"
merged_restaurant_data[259,18]="Yes"
merged_restaurant_data[118,18]="Yes"
merged_restaurant_data[43,18]="Yes"
merged_restaurant_data[289,18]="Yes"
merged_restaurant_data[202,18]="Yes"
merged_restaurant_data[388,18]="Yes"
merged_restaurant_data[280,18]="Yes"
merged_restaurant_data[516,18]="Yes"
merged_restaurant_data[369,18]="Yes"
merged_restaurant_data[346,18]="Yes"
merged_restaurant_data[91,18]="Yes"
merged_restaurant_data[604,18]="Yes"
merged_restaurant_data[353,18]="Yes"
merged_restaurant_data[123,18]="Yes"
merged_restaurant_data[538,18]="Yes"
merged_restaurant_data[611,18]="Yes"
merged_restaurant_data[82,18]="Yes"
merged_restaurant_data[642,18]="Yes"
merged_restaurant_data[473,18]="Yes"
merged_restaurant_data[61,18]="Yes"
merged_restaurant_data[247,18]="Yes"
merged_restaurant_data[24,18]="Yes"
merged_restaurant_data[127,18]="Yes"
merged_restaurant_data[186,18]="Yes"
merged_restaurant_data[624,18]="Yes"
merged_restaurant_data[59,18]="Yes"
merged_restaurant_data[64,18]="Yes"
merged_restaurant_data[176,18]="Yes"
merged_restaurant_data[89,18]="Yes"
merged_restaurant_data[256,18]="Yes"
merged_restaurant_data[141,18]="Yes"
merged_restaurant_data[410,18]="Yes"
merged_restaurant_data[497,18]="Yes"
merged_restaurant_data[394,18]="Yes"
merged_restaurant_data[221,18]="Yes"
merged_restaurant_data[210,18]="Yes"
merged_restaurant_data[436,18]="Yes"
merged_restaurant_data[135,18]="Yes"
merged_restaurant_data[332,18]="Yes"
merged_restaurant_data[85,18]="Yes"
merged_restaurant_data[571,18]="Yes"
merged_restaurant_data[526,18]="Yes"
merged_restaurant_data[18,18]="Yes"
merged_restaurant_data[51,18]="Yes"
merged_restaurant_data[172,18]="Yes"
merged_restaurant_data[49,18]="Yes"
merged_restaurant_data[212,18]="Yes"
merged_restaurant_data[262,18]="Yes"
merged_restaurant_data[328,18]="Yes"
merged_restaurant_data[34,18]="Yes"
merged_restaurant_data[131,18]="Yes"
merged_restaurant_data[246,18]="Yes"
merged_restaurant_data[155,18]="Yes"
merged_restaurant_data[600,18]="Yes"

merged_restaurant_data<- merged_restaurant_data %>%
  mutate(Rating_Group = case_when(
    Rating <= 3.9 ~ "Low",
    Rating >= 4.0 & Rating <= 4.5 ~ "Average",
    Rating >= 4.6 ~ "High"
    )
  )

merged_restaurant_data<- merged_restaurant_data[-(623:642),]

view(merged_restaurant_data)
```

```{r}
#| include: false
merged_restaurant_data$Restaurant_Violation<- ""

merged_restaurant_data[,20]="None"
merged_restaurant_data[40,20]="Critical"
merged_restaurant_data[49,20]="Critical"
merged_restaurant_data[55,20]="Critical"
merged_restaurant_data[56,20]="Critical"
merged_restaurant_data[67,20]="Critical"
merged_restaurant_data[95,20]="Critical"
merged_restaurant_data[98,20]="Critical"
merged_restaurant_data[99,20]="Critical"
merged_restaurant_data[106,20]="Critical"
merged_restaurant_data[157,20]="Critical"
merged_restaurant_data[160,20]="Critical"
merged_restaurant_data[167,20]="Critical"
merged_restaurant_data[170,20]="Critical"
merged_restaurant_data[171,20]="Critical"
merged_restaurant_data[172,20]="Critical"
merged_restaurant_data[213,20]="Critical"
merged_restaurant_data[214,20]="Critical"
merged_restaurant_data[220,20]="Critical"
merged_restaurant_data[221,20]="Critical"
merged_restaurant_data[224,20]="Critical"
merged_restaurant_data[230,20]="Critical"
merged_restaurant_data[236,20]="Critical"
merged_restaurant_data[238,20]="Critical"
merged_restaurant_data[239,20]="Critical"
merged_restaurant_data[275,20]="Critical"
merged_restaurant_data[278,20]="Critical"
merged_restaurant_data[279,20]="Critical"
merged_restaurant_data[289,20]="Critical"
merged_restaurant_data[291,20]="Critical"
merged_restaurant_data[301,20]="Critical"
merged_restaurant_data[305,20]="Critical"
merged_restaurant_data[306,20]="Critical"
merged_restaurant_data[307,20]="Critical"
merged_restaurant_data[308,20]="Critical"
merged_restaurant_data[310,20]="Critical"
```

```{r}
#| include: false
contingency_table_2 <- xtabs(~Restaurant_Violation+Near_Museum, data=merged_restaurant_data)
contingency_table_2

contingency_table_check_2<- merged_restaurant_data %>%
  tabyl(Restaurant_Violation, Near_Museum) %>%
  adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 1) %>%
  adorn_ns()
contingency_table_check_2
```

```{r}
#| echo: false
Visual_2<- ggplot(merged_restaurant_data, aes(x = Near_Museum, fill = Restaurant_Violation)) +
  geom_bar(position = "fill") + 
  labs(
    title = "Proportion of Restaurant Violations by Restaurants Near Museums",
    y = "Proportion of if Restaurant had Violations ",
    x = "Near Museum?"
  ) +
  theme_solarized()
Visual_2
```

## Chi-Square Analysis for Goal 2

```{r}
#| include: false
library(readr)
library(tidyr)
library(dplyr)
library(tidyverse)
library(stringr)
library(readxl)
library(janitor)
library(ggthemes)
library(rcompanion)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(htmltools)

endpoint<- "https://data.cityofnewyork.us/resource/fn6f-htvy.json"
resp <- httr::GET(endpoint)
museum_data <- jsonlite::fromJSON(httr::content(resp, as = "text"), flatten = TRUE)



endpoint_1<-"https://data.cityofnewyork.us/resource/43nn-pn8j.json"
resp1 <- httr::GET(endpoint_1)
restaurant_data <- jsonlite::fromJSON(httr::content(resp1, as = "text"), flatten = TRUE)


restaurant_rating_data <- read_parquet(here("data", "raw", "restaurant_rating_data.parquet"),    as_data_frame = TRUE )
```

```{r}
#| include: false
restaurant_rating_data$lat_new<- shQuote(restaurant_rating_data$Lat)
restaurant_rating_data$lon_new<- shQuote(restaurant_rating_data$Lon)
restaurant_rating_data$location.coordinates<- paste("c", "(", restaurant_rating_data$lon_new, ",", restaurant_rating_data$lat_new, ")", sep = "")

restaurant_rating_data <- restaurant_rating_data[-c(1, 2, 4, 5, 6, 8, 10, 11, 12, 15, 16, 26, 28, 32, 33,37, 38, 42, 45, 46, 47, 48, 50, 51, 57, 58, 61, 62, 63, 66, 68, 69, 74, 75, 79, 82, 85, 86, 89, 90, 93, 94, 95, 96, 97, 98, 99, 100, 103, 104, 105, 110, 111, 113, 117, 118, 119, 120, 128, 131, 133, 134, 138, 140, 144, 147, 151, 152, 153, 160, 165, 168, 174, 175, 176, 178, 179, 182, 183, 184, 186, 190, 192, 193, 195, 197, 198, 203, 204, 206, 208, 209, 212, 216, 218, 220, 223, 224, 225, 231, 232, 234, 236, 241, 244, 247, 249, 251, 254, 256, 265, 267, 268, 271, 274, 277, 283, 284, 285, 288, 289, 292, 294, 295, 297, 298, 299, 300, 301, 304, 305, 308, 310, 312, 315, 318, 320, 321, 322, 323, 325, 326, 328, 330, 331, 332, 334, 335, 337, 338, 339, 340, 341, 343, 345, 346, 348, 349, 350, 351, 353, 355, 356, 357, 359, 362, 363, 365, 366, 367, 370, 375, 376, 377, 378, 379, 380, 388, 389, 390, 391, 392, 393, 396, 399, 403, 406, 411, 415, 416, 417, 418, 420, 422, 423, 424, 425, 427, 429, 430, 432, 433, 435, 438, 439, 441, 442, 443, 444, 447, 449, 451, 454, 455, 457, 461, 463, 467, 469, 470, 472, 473, 474, 477, 478, 479, 483, 484, 488, 489, 491, 495, 497, 499, 500, 501, 506, 507, 508, 509, 510, 513, 514, 516, 520, 521, 522, 523, 525, 527, 528, 529, 532, 533, 537, 538, 539, 540, 543, 544, 546, 547, 549, 550, 552, 553, 554, 555, 556, 558, 560, 561, 562, 566, 567, 568, 569, 570, 571, 572, 575, 577, 578, 579, 580, 581, 582, 587, 589, 590, 591, 592, 595, 598, 599, 600, 607, 608, 610, 611, 612, 613, 614, 615, 618, 620, 621, 622, 624, 625, 626, 627, 631, 633, 635, 636, 637, 638, 640, 641, 646, 648, 653, 655, 657, 658, 660, 661, 663, 669, 670), ]
```

```{r}
#| include: false
is.character(restaurant_data$location.coordinates)
restaurant_data<- restaurant_data %>% mutate(location.coordinates = as.character(location.coordinates))

merged_restaurant_data<- full_join(restaurant_data, restaurant_rating_data, by = "location.coordinates")

sum(merged_restaurant_data$location.coordinates == "NULL", na.rm = TRUE)

merged_restaurant_data <-merged_restaurant_data[merged_restaurant_data$location.coordinates != "NULL", ]
```

```{r}
#| include: false
merged_restaurant_data[2,35]=4.7
merged_restaurant_data[3,35]=4.8
merged_restaurant_data[4,35]=4.0
merged_restaurant_data[6,35]=4.7
merged_restaurant_data[11,35]=4.9
merged_restaurant_data[13,35]=4.5
merged_restaurant_data[14,35]=4.1
merged_restaurant_data[16,35]=4.4
merged_restaurant_data[17,35]=4.8
merged_restaurant_data[18,35]=4.9
merged_restaurant_data[21,35]=4.2
merged_restaurant_data[22,35]=5.0
merged_restaurant_data[27,35]=4.4
merged_restaurant_data[28,35]=4.9
merged_restaurant_data[31,35]=4.4
merged_restaurant_data[32,35]=4.8
merged_restaurant_data[35,35]=4.4
merged_restaurant_data[39,35]=4.5
merged_restaurant_data[40,35]=4.6
merged_restaurant_data[44,35]=5.0
merged_restaurant_data[48,35]=5.0
merged_restaurant_data[49,35]=4.4 
merged_restaurant_data[50,35]=3.8
merged_restaurant_data[55,35]=4.9
merged_restaurant_data[58,35]=4.1
merged_restaurant_data[59,35]=4.3
merged_restaurant_data[61,35]=4.1
merged_restaurant_data[62,35]=4.4
merged_restaurant_data[63,35]=4.4
merged_restaurant_data[64,35]=3.8
merged_restaurant_data[67,35]=4.9
merged_restaurant_data[69,35]=4.6
merged_restaurant_data[73,35]=4.8
merged_restaurant_data[78,35]=5.0
merged_restaurant_data[82,35]=4.6
merged_restaurant_data[94,35]=4.8
merged_restaurant_data[96,35]=4.8
merged_restaurant_data[98,35]=4.2
merged_restaurant_data[103,35]=4.5
merged_restaurant_data[104,35]=4.9
merged_restaurant_data[105,35]=2.7
merged_restaurant_data[111,35]=4.1
merged_restaurant_data[113,35]=4.6
merged_restaurant_data[114,35]=4.4
merged_restaurant_data[115,35]=2.0
merged_restaurant_data[118,35]=4.6
merged_restaurant_data[130,35]=4.6
merged_restaurant_data[133,35]=3.0
merged_restaurant_data[134,35]=4.1
merged_restaurant_data[136,35]=4.7
merged_restaurant_data[142,35]=4.7
merged_restaurant_data[144,35]=4.0
merged_restaurant_data[146,35]=4.0
merged_restaurant_data[148,35]=3.5
merged_restaurant_data[150,35]=4.3
merged_restaurant_data[152,35]=4.8
merged_restaurant_data[153,35]=4.7
merged_restaurant_data[154,35]=5.0
merged_restaurant_data[159,35]=4.3
merged_restaurant_data[164,35]=4.7
merged_restaurant_data[169,35]=4.2
merged_restaurant_data[172,35]=4.6
merged_restaurant_data[173,35]=4.9
merged_restaurant_data[179,35]=4.7
merged_restaurant_data[180,35]=4.2
merged_restaurant_data[184,35]=4.4
merged_restaurant_data[185,35]=4.9
merged_restaurant_data[186,35]=4.5
merged_restaurant_data[189,35]=4.6
merged_restaurant_data[190,35]=5.0
merged_restaurant_data[191,35]=4.7
merged_restaurant_data[193,35]=4.8
merged_restaurant_data[195,35]=4.6
merged_restaurant_data[197,35]=4.8
merged_restaurant_data[199,35]=5.0
merged_restaurant_data[201,35]=4.5
merged_restaurant_data[207,35]=4.5
merged_restaurant_data[215,35]=4.2
merged_restaurant_data[217,35]=3.8
merged_restaurant_data[219,35]=4.8
merged_restaurant_data[221,35]=4.7
merged_restaurant_data[223,35]=4.6
merged_restaurant_data[229,35]=4.5
merged_restaurant_data[232,35]=4.7
merged_restaurant_data[233,35]=4.1
merged_restaurant_data[235,35]=4.6
merged_restaurant_data[236,35]=4.4
merged_restaurant_data[237,35]=4.3
merged_restaurant_data[241,35]=4.7
merged_restaurant_data[243,35]=4.5
merged_restaurant_data[245,35]=5.0
merged_restaurant_data[246,35]=4.7
merged_restaurant_data[260,35]=4.6
merged_restaurant_data[262,35]=4.3
merged_restaurant_data[270,35]=4.1
merged_restaurant_data[271,35]=4.9
merged_restaurant_data[273,35]=4.4
merged_restaurant_data[275,35]=4.9
merged_restaurant_data[278,35]=4.1
merged_restaurant_data[279,35]=4.5
merged_restaurant_data[280,35]=4.6
merged_restaurant_data[285,35]=4.3
merged_restaurant_data[286,35]=4.7
merged_restaurant_data[287,35]=4.8
merged_restaurant_data[288,35]=4.9
merged_restaurant_data[297,35]=4.5
merged_restaurant_data[304,35]=4.5
merged_restaurant_data[305,35]=4.7
merged_restaurant_data[308,35]=4.0
merged_restaurant_data[310,35]=4.5
merged_restaurant_data[314,35]=4.4
merged_restaurant_data[315,35]=4.7
merged_restaurant_data[319,35]=4.8
merged_restaurant_data[321,35]=4.9
merged_restaurant_data[322,35]=4.2 
merged_restaurant_data[328,35]=5.0
merged_restaurant_data[330,35]=4.6
merged_restaurant_data[335,35]=4.6
merged_restaurant_data[341,35]=5.0
merged_restaurant_data[342,35]=4.2
merged_restaurant_data[344,35]=3.6
merged_restaurant_data[346,35]=4.1
merged_restaurant_data[348,35]=4.9
merged_restaurant_data[350,35]=4.2
merged_restaurant_data[351,35]=4.1
merged_restaurant_data[352,35]=4.5
merged_restaurant_data[353,35]=4.5
merged_restaurant_data[356,35]=4.4
merged_restaurant_data[357,35]=4.3
merged_restaurant_data[358,35]=4.2
merged_restaurant_data[359,35]=4.8
merged_restaurant_data[363,35]=4.5
merged_restaurant_data[364,35]=4.8
merged_restaurant_data[367,35]=4.2
merged_restaurant_data[371,35]=4.6
merged_restaurant_data[374,35]=5.0
merged_restaurant_data[375,35]=3.9
merged_restaurant_data[376,35]=3.9
merged_restaurant_data[379,35]=3.8
merged_restaurant_data[382,35]=3.9
merged_restaurant_data[383,35]=5.0
merged_restaurant_data[384,35]=4.6
merged_restaurant_data[385,35]=4.6
merged_restaurant_data[387,35]=4.3
merged_restaurant_data[389,35]=4.9
merged_restaurant_data[391,35]=4.2
merged_restaurant_data[394,35]=4.5
merged_restaurant_data[395,35]=4.5
merged_restaurant_data[397,35]=4.8
merged_restaurant_data[404,35]=4.4
merged_restaurant_data[406,35]=4.5
merged_restaurant_data[408,35]=4.4
merged_restaurant_data[410,35]=3.8
merged_restaurant_data[411,35]=4.8
merged_restaurant_data[414,35]=3.9
merged_restaurant_data[416,35]=4.9
merged_restaurant_data[420,35]=4.6
merged_restaurant_data[422,35]=4.0
merged_restaurant_data[427,35]=4.8
merged_restaurant_data[433,35]=4.7
merged_restaurant_data[436,35]=3.7
merged_restaurant_data[437,35]=4.3
merged_restaurant_data[438,35]=4.6
merged_restaurant_data[440,35]=4.6
merged_restaurant_data[446,35]=4.7
merged_restaurant_data[452,35]=4.1
merged_restaurant_data[453,35]=4.3
merged_restaurant_data[454,35]=5.0
merged_restaurant_data[458,35]=4.3
merged_restaurant_data[459,35]=3.9
merged_restaurant_data[463,35]=4.0
merged_restaurant_data[467,35]=4.9
merged_restaurant_data[470,35]=4.0
merged_restaurant_data[471,35]=4.1
merged_restaurant_data[472,35]=4.0
merged_restaurant_data[486,35]=4.3
merged_restaurant_data[489,35]=5.0
merged_restaurant_data[494,35]=5.0
merged_restaurant_data[495,35]=4.9
merged_restaurant_data[496,35]=4.3
merged_restaurant_data[497,35]=4.2
merged_restaurant_data[501,35]=5.0
merged_restaurant_data[502,35]=4.1
merged_restaurant_data[506,35]=4.6
merged_restaurant_data[507,35]=4.6
merged_restaurant_data[509,35]=4.7
merged_restaurant_data[511,35]=4.5
merged_restaurant_data[512,35]=4.5
merged_restaurant_data[513,35]=3.3
merged_restaurant_data[515,35]=4.9
merged_restaurant_data[519,35]=4.8
merged_restaurant_data[520,35]=4.5
merged_restaurant_data[522,35]=4.9
merged_restaurant_data[523,35]=4.8
merged_restaurant_data[528,35]=4.9
merged_restaurant_data[533,35]=4.3
merged_restaurant_data[543,35]=4.6
merged_restaurant_data[546,35]=4.0
merged_restaurant_data[550,35]=4.8
merged_restaurant_data[552,35]=4.3
merged_restaurant_data[554,35]=3.7
merged_restaurant_data[555,35]=2.1
merged_restaurant_data[556,35]=4.7
merged_restaurant_data[557,35]=4.5
merged_restaurant_data[558,35]=5.0
merged_restaurant_data[562,35]=4.1
merged_restaurant_data[563,35]=4.3
merged_restaurant_data[566,35]=4.3
merged_restaurant_data[567,35]=4.5
merged_restaurant_data[568,35]=4.9
merged_restaurant_data[570,35]=4.3
merged_restaurant_data[573,35]=4.6
merged_restaurant_data[574,35]=4.1
merged_restaurant_data[575,35]=4.8
merged_restaurant_data[578,35]=4.4
merged_restaurant_data[581,35]=4.0
merged_restaurant_data[590,35]=4.1
merged_restaurant_data[592,35]=5.0
merged_restaurant_data[598,35]=3.9
merged_restaurant_data[601,35]=4.2
merged_restaurant_data[605,35]=4.6
merged_restaurant_data[608,35]=4.1
merged_restaurant_data[610,35]=4.1
merged_restaurant_data[613,35]=4.9
merged_restaurant_data[617,35]=4.4
merged_restaurant_data[622,35]=4.3
merged_restaurant_data[624,35]=4.0
merged_restaurant_data[625,35]=5.0
merged_restaurant_data[632,35]=4.4
merged_restaurant_data[633,35]=4.6
merged_restaurant_data[638,35]=4.2
merged_restaurant_data[640,35]=4.6
merged_restaurant_data[645,35]=4.6
merged_restaurant_data[647,35]=4.5
merged_restaurant_data[651,35]=4.9
merged_restaurant_data[660,35]=5.0
merged_restaurant_data[661,35]=4.7
merged_restaurant_data[662,35]=3.9
merged_restaurant_data[663,35]=4.0
merged_restaurant_data[664,35]=4.4
merged_restaurant_data[666,35]=4.3
merged_restaurant_data[677,35]=4.2
merged_restaurant_data[683,35]=4.5
merged_restaurant_data[686,35]=4.3
merged_restaurant_data[688,35]=4.8
merged_restaurant_data[689,35]=4.9
merged_restaurant_data[692,35]=4.9
merged_restaurant_data[693,35]=3.8
merged_restaurant_data[697,35]=4.9
merged_restaurant_data[700,35]=4.0
merged_restaurant_data[702,35]=4.8
merged_restaurant_data[714,35]=4.6
merged_restaurant_data[718,35]=4.6
merged_restaurant_data[719,35]=4.5
merged_restaurant_data[725,35]=4.5
merged_restaurant_data[728,35]=4.7
merged_restaurant_data[729,35]=4.8
merged_restaurant_data[731,35]=4.7
merged_restaurant_data[732,35]=4.2
merged_restaurant_data[733,35]=4.4
merged_restaurant_data[734,35]=3.8
merged_restaurant_data[735,35]=4.5
merged_restaurant_data[737,35]=4.5
merged_restaurant_data[738,35]=4.6
merged_restaurant_data[741,35]=3.8
merged_restaurant_data[744,35]=4.9
merged_restaurant_data[746,35]=4.3
merged_restaurant_data[747,35]=4.2
merged_restaurant_data[752,35]=3.7
merged_restaurant_data[755,35]=4.5
merged_restaurant_data[759,35]=4.0
merged_restaurant_data[762,35]=4.8
merged_restaurant_data[764,35]=4.3
merged_restaurant_data[767,35]=4.4
merged_restaurant_data[769,35]=4.3
merged_restaurant_data[770,35]=4.9
merged_restaurant_data[772,35]=4.0
merged_restaurant_data[774,35]=4.9
merged_restaurant_data[777,35]=4.8
merged_restaurant_data[779,35]=4.1
merged_restaurant_data[780,35]=4.4
merged_restaurant_data[782,35]=4.6
merged_restaurant_data[784,35]=4.1
merged_restaurant_data[785,35]=5.0
merged_restaurant_data[787,35]=4.1
merged_restaurant_data[788,35]=4.8
merged_restaurant_data[790,35]=4.1
merged_restaurant_data[791,35]=3.8
merged_restaurant_data[793,35]=4.4
merged_restaurant_data[796,35]=4.6
merged_restaurant_data[799,35]=5.0
merged_restaurant_data[802,35]=4.3
merged_restaurant_data[807,35]=4.2
merged_restaurant_data[809,35]=4.3
merged_restaurant_data[810,35]=3.9
merged_restaurant_data[811,35]=4.4
merged_restaurant_data[812,35]=4.5
merged_restaurant_data[816,35]=5.0
merged_restaurant_data[820,35]=4.6
merged_restaurant_data[825,35]=4.9
merged_restaurant_data[827,35]=4.8
merged_restaurant_data[828,35]=5.0
merged_restaurant_data[830,35]=4.5
merged_restaurant_data[834,35]=4.4
merged_restaurant_data[837,35]=4.3
merged_restaurant_data[838,35]=5.0
merged_restaurant_data[839,35]=3.0
merged_restaurant_data[841,35]=3.0
merged_restaurant_data[842,35]=4.6
merged_restaurant_data[852,35]=5.0
merged_restaurant_data[855,35]=4.9
merged_restaurant_data[856,35]=4.1
merged_restaurant_data[859,35]=4.5
merged_restaurant_data[861,35]=4.8
merged_restaurant_data[865,35]=4.6
merged_restaurant_data[868,35]=4.8
merged_restaurant_data[869,35]=5.0
merged_restaurant_data[870,35]=4.6
merged_restaurant_data[871,35]=4.1
merged_restaurant_data[872,35]=4.4
merged_restaurant_data[878,35]=4.4
merged_restaurant_data[883,35]=4.6
merged_restaurant_data[884,35]=4.3
merged_restaurant_data[889,35]=4.6
merged_restaurant_data[891,35]=4.4
merged_restaurant_data[893,35]=4.5
merged_restaurant_data[894,35]=4.5
merged_restaurant_data[896,35]=3.2
merged_restaurant_data[897,35]=3.8
merged_restaurant_data[899,35]=3.8
merged_restaurant_data[901,35]=4.6
merged_restaurant_data[902,35]=4.1
merged_restaurant_data[905,35]=3.7
merged_restaurant_data[906,35]=4.6
merged_restaurant_data[907,35]=4.5
merged_restaurant_data[909,35]=4.9
merged_restaurant_data[910,35]=4.1
merged_restaurant_data[913,35]=3.0
merged_restaurant_data[916,35]=4.8
merged_restaurant_data[920,35]=4.2
merged_restaurant_data[921,35]=4.3
merged_restaurant_data[924,35]=4.9
merged_restaurant_data[925,35]=5.0
merged_restaurant_data[929,35]=3.5
merged_restaurant_data[930,35]=4.8
merged_restaurant_data[933,35]=3.8
merged_restaurant_data[936,35]=4.4
merged_restaurant_data[939,35]=4.4
merged_restaurant_data[940,35]=4.3
merged_restaurant_data[941,35]=4.6
merged_restaurant_data[942,35]=4.6
merged_restaurant_data[943,35]=4.2
merged_restaurant_data[945,35]=3.8
merged_restaurant_data[946,35]=4.6
merged_restaurant_data[948,35]=4.6
merged_restaurant_data[951,35]=3.4
merged_restaurant_data[953,35]=4.9
merged_restaurant_data[954,35]=4.3
merged_restaurant_data[955,35]=3.2
merged_restaurant_data[957,35]=4.5
merged_restaurant_data[961,35]=4.5
merged_restaurant_data[962,35]=4.9
merged_restaurant_data[965,35]=4.4
merged_restaurant_data[968,35]=4.1
merged_restaurant_data[970,35]=4.4
merged_restaurant_data[971,35]=4.7
merged_restaurant_data[972,35]=4.6
merged_restaurant_data[974,35]=3.5
merged_restaurant_data[975,35]=4.5
merged_restaurant_data[977,35]=4.7
merged_restaurant_data[979,35]=4.2
merged_restaurant_data[981,35]=4.8
merged_restaurant_data[982,35]=4.4
merged_restaurant_data[984,35]=4.4
merged_restaurant_data[986,35]=4.3
merged_restaurant_data[987,35]=4.3
merged_restaurant_data[988,35]=4.6
merged_restaurant_data[989,35]=2.7
merged_restaurant_data[991,35]=4.7
merged_restaurant_data[992,35]=4.3
merged_restaurant_data[993,35]=4.1
merged_restaurant_data[997,35]=4.8
merged_restaurant_data[998,35]=4.8
merged_restaurant_data[999,35]=4.4

sum(is.na(merged_restaurant_data$Rating))

merged_restaurant_data<- merged_restaurant_data %>%
  filter(!is.na(Rating))

merged_restaurant_data$dba<- str_to_title(merged_restaurant_data$dba)

merged_restaurant_data$Restaurant_Name <-
  paste(
    coalesce(merged_restaurant_data$dba, ""),
    coalesce(merged_restaurant_data$Name, "")
  )
```

```{r}
#| include: false
merged_restaurant_data <- merged_restaurant_data %>% select(-dba, -boro, -building, -street, -zipcode, -phone, -community_board, -council_district, -census_tract, -bbl, -nta, -`:@computed_region_f5dn_yrer`, -`:@computed_region_yeji_bk3q`, -`:@computed_region_sbqj_enih`, -`:@computed_region_92fq_4b7q`, -cuisine_description, -bin, -grade, -grade_date, -URL, -Name, -`Rating Count`, -`Detailed Ratings`, -`Price Category`, -Address, -ZipCode)

str(merged_restaurant_data$Lat)

str(merged_restaurant_data$latitude)

merged_restaurant_data$latitude<-as.numeric(merged_restaurant_data$latitude)

merged_restaurant_data$Lat<-as.numeric(merged_restaurant_data$Lat)

merged_restaurant_data$Latitude <-
  coalesce(
    merged_restaurant_data$latitude, merged_restaurant_data$Lat
  )

merged_restaurant_data <- merged_restaurant_data %>% select(-Lat, -latitude)

str(merged_restaurant_data$Lon)

str(merged_restaurant_data$longitude)

merged_restaurant_data$Lon<-as.numeric(merged_restaurant_data$Lon)

merged_restaurant_data$longitude<-as.numeric(merged_restaurant_data$longitude)

merged_restaurant_data$Longitude <-
  coalesce(
    merged_restaurant_data$longitude, merged_restaurant_data$Lon
  )

merged_restaurant_data <- merged_restaurant_data %>% select(-Lon, -longitude)
```

```{r}
#| include: false
museum_data<- museum_data %>%
  select(-tel, -url, -adress1, -address2)

museum_data<- museum_data %>%
  mutate(
    cleaned_geom_coordinates = gsub("c\\(|\\)|\"", "", the_geom.coordinates)
    )

museum_data<-museum_data %>%
  separate(
    col = cleaned_geom_coordinates,
    into = c("Longitude", "Latitude"),
    sep = ","
  )

museum_data$Longitude<- as.numeric(museum_data$Longitude)

museum_data$Latitude<- 
  as.numeric(museum_data$Latitude)
```

```{r}
#| include: false
merged_restaurant_data$Near_Museum<- ""

merged_restaurant_data[,18]="No"
merged_restaurant_data[14,18]="Yes"
merged_restaurant_data[629,18]="Yes"
merged_restaurant_data[458,18]="Yes"
merged_restaurant_data[389,18]="Yes"
merged_restaurant_data[490,18]="Yes"
merged_restaurant_data[550,18]="Yes"
merged_restaurant_data[48,18]="Yes"
merged_restaurant_data[411,18]="Yes"
merged_restaurant_data[361,18]="Yes"
merged_restaurant_data[471,18]="Yes"
merged_restaurant_data[456,18]="Yes"
merged_restaurant_data[553,18]="Yes"
merged_restaurant_data[404,18]="Yes"
merged_restaurant_data[562,18]="Yes"
merged_restaurant_data[288,18]="Yes"
merged_restaurant_data[487,18]="Yes"
merged_restaurant_data[460,18]="Yes"
merged_restaurant_data[579,18]="Yes"
merged_restaurant_data[620,18]="Yes"
merged_restaurant_data[309,18]="Yes"
merged_restaurant_data[244,18]="Yes"
merged_restaurant_data[439,18]="Yes"
merged_restaurant_data[507,18]="Yes"
merged_restaurant_data[381,18]="Yes"
merged_restaurant_data[355,18]="Yes"
merged_restaurant_data[433,18]="Yes"
merged_restaurant_data[513,18]="Yes"
merged_restaurant_data[238,18]="Yes"
merged_restaurant_data[590,18]="Yes"
merged_restaurant_data[120,18]="Yes"
merged_restaurant_data[143,18]="Yes"
merged_restaurant_data[259,18]="Yes"
merged_restaurant_data[118,18]="Yes"
merged_restaurant_data[43,18]="Yes"
merged_restaurant_data[289,18]="Yes"
merged_restaurant_data[202,18]="Yes"
merged_restaurant_data[388,18]="Yes"
merged_restaurant_data[280,18]="Yes"
merged_restaurant_data[516,18]="Yes"
merged_restaurant_data[369,18]="Yes"
merged_restaurant_data[346,18]="Yes"
merged_restaurant_data[91,18]="Yes"
merged_restaurant_data[604,18]="Yes"
merged_restaurant_data[353,18]="Yes"
merged_restaurant_data[123,18]="Yes"
merged_restaurant_data[538,18]="Yes"
merged_restaurant_data[611,18]="Yes"
merged_restaurant_data[82,18]="Yes"
merged_restaurant_data[642,18]="Yes"
merged_restaurant_data[473,18]="Yes"
merged_restaurant_data[61,18]="Yes"
merged_restaurant_data[247,18]="Yes"
merged_restaurant_data[24,18]="Yes"
merged_restaurant_data[127,18]="Yes"
merged_restaurant_data[186,18]="Yes"
merged_restaurant_data[624,18]="Yes"
merged_restaurant_data[59,18]="Yes"
merged_restaurant_data[64,18]="Yes"
merged_restaurant_data[176,18]="Yes"
merged_restaurant_data[89,18]="Yes"
merged_restaurant_data[256,18]="Yes"
merged_restaurant_data[141,18]="Yes"
merged_restaurant_data[410,18]="Yes"
merged_restaurant_data[497,18]="Yes"
merged_restaurant_data[394,18]="Yes"
merged_restaurant_data[221,18]="Yes"
merged_restaurant_data[210,18]="Yes"
merged_restaurant_data[436,18]="Yes"
merged_restaurant_data[135,18]="Yes"
merged_restaurant_data[332,18]="Yes"
merged_restaurant_data[85,18]="Yes"
merged_restaurant_data[571,18]="Yes"
merged_restaurant_data[526,18]="Yes"
merged_restaurant_data[18,18]="Yes"
merged_restaurant_data[51,18]="Yes"
merged_restaurant_data[172,18]="Yes"
merged_restaurant_data[49,18]="Yes"
merged_restaurant_data[212,18]="Yes"
merged_restaurant_data[262,18]="Yes"
merged_restaurant_data[328,18]="Yes"
merged_restaurant_data[34,18]="Yes"
merged_restaurant_data[131,18]="Yes"
merged_restaurant_data[246,18]="Yes"
merged_restaurant_data[155,18]="Yes"
merged_restaurant_data[600,18]="Yes"

merged_restaurant_data<- merged_restaurant_data %>%
  mutate(Rating_Group = case_when(
    Rating <= 3.9 ~ "Low",
    Rating >= 4.0 & Rating <= 4.5 ~ "Average",
    Rating >= 4.6 ~ "High"
    )
  )

merged_restaurant_data<- merged_restaurant_data[-(623:642),]

view(merged_restaurant_data)
```

```{r}
#| include: false
merged_restaurant_data$Restaurant_Violation<- ""

merged_restaurant_data[,20]="None"
merged_restaurant_data[40,20]="Critical"
merged_restaurant_data[49,20]="Critical"
merged_restaurant_data[55,20]="Critical"
merged_restaurant_data[56,20]="Critical"
merged_restaurant_data[67,20]="Critical"
merged_restaurant_data[95,20]="Critical"
merged_restaurant_data[98,20]="Critical"
merged_restaurant_data[99,20]="Critical"
merged_restaurant_data[106,20]="Critical"
merged_restaurant_data[157,20]="Critical"
merged_restaurant_data[160,20]="Critical"
merged_restaurant_data[167,20]="Critical"
merged_restaurant_data[170,20]="Critical"
merged_restaurant_data[171,20]="Critical"
merged_restaurant_data[172,20]="Critical"
merged_restaurant_data[213,20]="Critical"
merged_restaurant_data[214,20]="Critical"
merged_restaurant_data[220,20]="Critical"
merged_restaurant_data[221,20]="Critical"
merged_restaurant_data[224,20]="Critical"
merged_restaurant_data[230,20]="Critical"
merged_restaurant_data[236,20]="Critical"
merged_restaurant_data[238,20]="Critical"
merged_restaurant_data[239,20]="Critical"
merged_restaurant_data[275,20]="Critical"
merged_restaurant_data[278,20]="Critical"
merged_restaurant_data[279,20]="Critical"
merged_restaurant_data[289,20]="Critical"
merged_restaurant_data[291,20]="Critical"
merged_restaurant_data[301,20]="Critical"
merged_restaurant_data[305,20]="Critical"
merged_restaurant_data[306,20]="Critical"
merged_restaurant_data[307,20]="Critical"
merged_restaurant_data[308,20]="Critical"
merged_restaurant_data[310,20]="Critical"
```

```{r}
#| include: false
contingency_table_2 <- xtabs(~Restaurant_Violation+Near_Museum, data=merged_restaurant_data)
contingency_table_2

contingency_table_check_2<- merged_restaurant_data %>%
  tabyl(Restaurant_Violation, Near_Museum) %>%
  adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 1) %>%
  adorn_ns()
contingency_table_check_2
```

```{r}
#| include: false
Visual_2<- ggplot(merged_restaurant_data, aes(x = Near_Museum, fill = Restaurant_Violation)) +
  geom_bar(position = "fill") + 
  labs(
    title = "Proportion of Restaurant Violations by Restaurants Near Museums",
    y = "Proportion of if Restaurant had Violations ",
    x = "Near Museum?"
  ) +
  theme_solarized()
Visual_2
```

```{r}
#| echo: false
chi_square_test<- chisq.test(contingency_table_2)
chi_square_test

chisq.test(contingency_table_2)$expected

cramerV(contingency_table_2)
```

-   The chi-square test shows X\^2 = 6.2237e-30, df = 2, p = 1

-   Cramer's V tells us that the relationship is very weak in strength (0.008128).

## Continuation

```{r}
#| include: false
library(readr)
library(tidyr)
library(dplyr)
library(tidyverse)
library(stringr)
library(readxl)
library(janitor)
library(ggthemes)
library(rcompanion)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(htmltools)

endpoint<- "https://data.cityofnewyork.us/resource/fn6f-htvy.json"
resp <- httr::GET(endpoint)
museum_data <- jsonlite::fromJSON(httr::content(resp, as = "text"), flatten = TRUE)



endpoint_1<-"https://data.cityofnewyork.us/resource/43nn-pn8j.json"
resp1 <- httr::GET(endpoint_1)
restaurant_data <- jsonlite::fromJSON(httr::content(resp1, as = "text"), flatten = TRUE)


restaurant_rating_data <- read_parquet(here("data", "raw","restaurant_rating_data.parquet"), as_data_frame = TRUE )
```

```{r}
#| include: false
restaurant_rating_data$lat_new<- shQuote(restaurant_rating_data$Lat)
restaurant_rating_data$lon_new<- shQuote(restaurant_rating_data$Lon)
restaurant_rating_data$location.coordinates<- paste("c", "(", restaurant_rating_data$lon_new, ",", restaurant_rating_data$lat_new, ")", sep = "")

restaurant_rating_data <- restaurant_rating_data[-c(1, 2, 4, 5, 6, 8, 10, 11, 12, 15, 16, 26, 28, 32, 33,37, 38, 42, 45, 46, 47, 48, 50, 51, 57, 58, 61, 62, 63, 66, 68, 69, 74, 75, 79, 82, 85, 86, 89, 90, 93, 94, 95, 96, 97, 98, 99, 100, 103, 104, 105, 110, 111, 113, 117, 118, 119, 120, 128, 131, 133, 134, 138, 140, 144, 147, 151, 152, 153, 160, 165, 168, 174, 175, 176, 178, 179, 182, 183, 184, 186, 190, 192, 193, 195, 197, 198, 203, 204, 206, 208, 209, 212, 216, 218, 220, 223, 224, 225, 231, 232, 234, 236, 241, 244, 247, 249, 251, 254, 256, 265, 267, 268, 271, 274, 277, 283, 284, 285, 288, 289, 292, 294, 295, 297, 298, 299, 300, 301, 304, 305, 308, 310, 312, 315, 318, 320, 321, 322, 323, 325, 326, 328, 330, 331, 332, 334, 335, 337, 338, 339, 340, 341, 343, 345, 346, 348, 349, 350, 351, 353, 355, 356, 357, 359, 362, 363, 365, 366, 367, 370, 375, 376, 377, 378, 379, 380, 388, 389, 390, 391, 392, 393, 396, 399, 403, 406, 411, 415, 416, 417, 418, 420, 422, 423, 424, 425, 427, 429, 430, 432, 433, 435, 438, 439, 441, 442, 443, 444, 447, 449, 451, 454, 455, 457, 461, 463, 467, 469, 470, 472, 473, 474, 477, 478, 479, 483, 484, 488, 489, 491, 495, 497, 499, 500, 501, 506, 507, 508, 509, 510, 513, 514, 516, 520, 521, 522, 523, 525, 527, 528, 529, 532, 533, 537, 538, 539, 540, 543, 544, 546, 547, 549, 550, 552, 553, 554, 555, 556, 558, 560, 561, 562, 566, 567, 568, 569, 570, 571, 572, 575, 577, 578, 579, 580, 581, 582, 587, 589, 590, 591, 592, 595, 598, 599, 600, 607, 608, 610, 611, 612, 613, 614, 615, 618, 620, 621, 622, 624, 625, 626, 627, 631, 633, 635, 636, 637, 638, 640, 641, 646, 648, 653, 655, 657, 658, 660, 661, 663, 669, 670), ]
```

```{r}
#| include: false
is.character(restaurant_data$location.coordinates)
restaurant_data<- restaurant_data %>% mutate(location.coordinates = as.character(location.coordinates))

merged_restaurant_data<- full_join(restaurant_data, restaurant_rating_data, by = "location.coordinates")

sum(merged_restaurant_data$location.coordinates == "NULL", na.rm = TRUE)

merged_restaurant_data <-merged_restaurant_data[merged_restaurant_data$location.coordinates != "NULL", ]
```

```{r}
#| include: false
merged_restaurant_data[2,35]=4.7
merged_restaurant_data[3,35]=4.8
merged_restaurant_data[4,35]=4.0
merged_restaurant_data[6,35]=4.7
merged_restaurant_data[11,35]=4.9
merged_restaurant_data[13,35]=4.5
merged_restaurant_data[14,35]=4.1
merged_restaurant_data[16,35]=4.4
merged_restaurant_data[17,35]=4.8
merged_restaurant_data[18,35]=4.9
merged_restaurant_data[21,35]=4.2
merged_restaurant_data[22,35]=5.0
merged_restaurant_data[27,35]=4.4
merged_restaurant_data[28,35]=4.9
merged_restaurant_data[31,35]=4.4
merged_restaurant_data[32,35]=4.8
merged_restaurant_data[35,35]=4.4
merged_restaurant_data[39,35]=4.5
merged_restaurant_data[40,35]=4.6
merged_restaurant_data[44,35]=5.0
merged_restaurant_data[48,35]=5.0
merged_restaurant_data[49,35]=4.4 
merged_restaurant_data[50,35]=3.8
merged_restaurant_data[55,35]=4.9
merged_restaurant_data[58,35]=4.1
merged_restaurant_data[59,35]=4.3
merged_restaurant_data[61,35]=4.1
merged_restaurant_data[62,35]=4.4
merged_restaurant_data[63,35]=4.4
merged_restaurant_data[64,35]=3.8
merged_restaurant_data[67,35]=4.9
merged_restaurant_data[69,35]=4.6
merged_restaurant_data[73,35]=4.8
merged_restaurant_data[78,35]=5.0
merged_restaurant_data[82,35]=4.6
merged_restaurant_data[94,35]=4.8
merged_restaurant_data[96,35]=4.8
merged_restaurant_data[98,35]=4.2
merged_restaurant_data[103,35]=4.5
merged_restaurant_data[104,35]=4.9
merged_restaurant_data[105,35]=2.7
merged_restaurant_data[111,35]=4.1
merged_restaurant_data[113,35]=4.6
merged_restaurant_data[114,35]=4.4
merged_restaurant_data[115,35]=2.0
merged_restaurant_data[118,35]=4.6
merged_restaurant_data[130,35]=4.6
merged_restaurant_data[133,35]=3.0
merged_restaurant_data[134,35]=4.1
merged_restaurant_data[136,35]=4.7
merged_restaurant_data[142,35]=4.7
merged_restaurant_data[144,35]=4.0
merged_restaurant_data[146,35]=4.0
merged_restaurant_data[148,35]=3.5
merged_restaurant_data[150,35]=4.3
merged_restaurant_data[152,35]=4.8
merged_restaurant_data[153,35]=4.7
merged_restaurant_data[154,35]=5.0
merged_restaurant_data[159,35]=4.3
merged_restaurant_data[164,35]=4.7
merged_restaurant_data[169,35]=4.2
merged_restaurant_data[172,35]=4.6
merged_restaurant_data[173,35]=4.9
merged_restaurant_data[179,35]=4.7
merged_restaurant_data[180,35]=4.2
merged_restaurant_data[184,35]=4.4
merged_restaurant_data[185,35]=4.9
merged_restaurant_data[186,35]=4.5
merged_restaurant_data[189,35]=4.6
merged_restaurant_data[190,35]=5.0
merged_restaurant_data[191,35]=4.7
merged_restaurant_data[193,35]=4.8
merged_restaurant_data[195,35]=4.6
merged_restaurant_data[197,35]=4.8
merged_restaurant_data[199,35]=5.0
merged_restaurant_data[201,35]=4.5
merged_restaurant_data[207,35]=4.5
merged_restaurant_data[215,35]=4.2
merged_restaurant_data[217,35]=3.8
merged_restaurant_data[219,35]=4.8
merged_restaurant_data[221,35]=4.7
merged_restaurant_data[223,35]=4.6
merged_restaurant_data[229,35]=4.5
merged_restaurant_data[232,35]=4.7
merged_restaurant_data[233,35]=4.1
merged_restaurant_data[235,35]=4.6
merged_restaurant_data[236,35]=4.4
merged_restaurant_data[237,35]=4.3
merged_restaurant_data[241,35]=4.7
merged_restaurant_data[243,35]=4.5
merged_restaurant_data[245,35]=5.0
merged_restaurant_data[246,35]=4.7
merged_restaurant_data[260,35]=4.6
merged_restaurant_data[262,35]=4.3
merged_restaurant_data[270,35]=4.1
merged_restaurant_data[271,35]=4.9
merged_restaurant_data[273,35]=4.4
merged_restaurant_data[275,35]=4.9
merged_restaurant_data[278,35]=4.1
merged_restaurant_data[279,35]=4.5
merged_restaurant_data[280,35]=4.6
merged_restaurant_data[285,35]=4.3
merged_restaurant_data[286,35]=4.7
merged_restaurant_data[287,35]=4.8
merged_restaurant_data[288,35]=4.9
merged_restaurant_data[297,35]=4.5
merged_restaurant_data[304,35]=4.5
merged_restaurant_data[305,35]=4.7
merged_restaurant_data[308,35]=4.0
merged_restaurant_data[310,35]=4.5
merged_restaurant_data[314,35]=4.4
merged_restaurant_data[315,35]=4.7
merged_restaurant_data[319,35]=4.8
merged_restaurant_data[321,35]=4.9
merged_restaurant_data[322,35]=4.2 
merged_restaurant_data[328,35]=5.0
merged_restaurant_data[330,35]=4.6
merged_restaurant_data[335,35]=4.6
merged_restaurant_data[341,35]=5.0
merged_restaurant_data[342,35]=4.2
merged_restaurant_data[344,35]=3.6
merged_restaurant_data[346,35]=4.1
merged_restaurant_data[348,35]=4.9
merged_restaurant_data[350,35]=4.2
merged_restaurant_data[351,35]=4.1
merged_restaurant_data[352,35]=4.5
merged_restaurant_data[353,35]=4.5
merged_restaurant_data[356,35]=4.4
merged_restaurant_data[357,35]=4.3
merged_restaurant_data[358,35]=4.2
merged_restaurant_data[359,35]=4.8
merged_restaurant_data[363,35]=4.5
merged_restaurant_data[364,35]=4.8
merged_restaurant_data[367,35]=4.2
merged_restaurant_data[371,35]=4.6
merged_restaurant_data[374,35]=5.0
merged_restaurant_data[375,35]=3.9
merged_restaurant_data[376,35]=3.9
merged_restaurant_data[379,35]=3.8
merged_restaurant_data[382,35]=3.9
merged_restaurant_data[383,35]=5.0
merged_restaurant_data[384,35]=4.6
merged_restaurant_data[385,35]=4.6
merged_restaurant_data[387,35]=4.3
merged_restaurant_data[389,35]=4.9
merged_restaurant_data[391,35]=4.2
merged_restaurant_data[394,35]=4.5
merged_restaurant_data[395,35]=4.5
merged_restaurant_data[397,35]=4.8
merged_restaurant_data[404,35]=4.4
merged_restaurant_data[406,35]=4.5
merged_restaurant_data[408,35]=4.4
merged_restaurant_data[410,35]=3.8
merged_restaurant_data[411,35]=4.8
merged_restaurant_data[414,35]=3.9
merged_restaurant_data[416,35]=4.9
merged_restaurant_data[420,35]=4.6
merged_restaurant_data[422,35]=4.0
merged_restaurant_data[427,35]=4.8
merged_restaurant_data[433,35]=4.7
merged_restaurant_data[436,35]=3.7
merged_restaurant_data[437,35]=4.3
merged_restaurant_data[438,35]=4.6
merged_restaurant_data[440,35]=4.6
merged_restaurant_data[446,35]=4.7
merged_restaurant_data[452,35]=4.1
merged_restaurant_data[453,35]=4.3
merged_restaurant_data[454,35]=5.0
merged_restaurant_data[458,35]=4.3
merged_restaurant_data[459,35]=3.9
merged_restaurant_data[463,35]=4.0
merged_restaurant_data[467,35]=4.9
merged_restaurant_data[470,35]=4.0
merged_restaurant_data[471,35]=4.1
merged_restaurant_data[472,35]=4.0
merged_restaurant_data[486,35]=4.3
merged_restaurant_data[489,35]=5.0
merged_restaurant_data[494,35]=5.0
merged_restaurant_data[495,35]=4.9
merged_restaurant_data[496,35]=4.3
merged_restaurant_data[497,35]=4.2
merged_restaurant_data[501,35]=5.0
merged_restaurant_data[502,35]=4.1
merged_restaurant_data[506,35]=4.6
merged_restaurant_data[507,35]=4.6
merged_restaurant_data[509,35]=4.7
merged_restaurant_data[511,35]=4.5
merged_restaurant_data[512,35]=4.5
merged_restaurant_data[513,35]=3.3
merged_restaurant_data[515,35]=4.9
merged_restaurant_data[519,35]=4.8
merged_restaurant_data[520,35]=4.5
merged_restaurant_data[522,35]=4.9
merged_restaurant_data[523,35]=4.8
merged_restaurant_data[528,35]=4.9
merged_restaurant_data[533,35]=4.3
merged_restaurant_data[543,35]=4.6
merged_restaurant_data[546,35]=4.0
merged_restaurant_data[550,35]=4.8
merged_restaurant_data[552,35]=4.3
merged_restaurant_data[554,35]=3.7
merged_restaurant_data[555,35]=2.1
merged_restaurant_data[556,35]=4.7
merged_restaurant_data[557,35]=4.5
merged_restaurant_data[558,35]=5.0
merged_restaurant_data[562,35]=4.1
merged_restaurant_data[563,35]=4.3
merged_restaurant_data[566,35]=4.3
merged_restaurant_data[567,35]=4.5
merged_restaurant_data[568,35]=4.9
merged_restaurant_data[570,35]=4.3
merged_restaurant_data[573,35]=4.6
merged_restaurant_data[574,35]=4.1
merged_restaurant_data[575,35]=4.8
merged_restaurant_data[578,35]=4.4
merged_restaurant_data[581,35]=4.0
merged_restaurant_data[590,35]=4.1
merged_restaurant_data[592,35]=5.0
merged_restaurant_data[598,35]=3.9
merged_restaurant_data[601,35]=4.2
merged_restaurant_data[605,35]=4.6
merged_restaurant_data[608,35]=4.1
merged_restaurant_data[610,35]=4.1
merged_restaurant_data[613,35]=4.9
merged_restaurant_data[617,35]=4.4
merged_restaurant_data[622,35]=4.3
merged_restaurant_data[624,35]=4.0
merged_restaurant_data[625,35]=5.0
merged_restaurant_data[632,35]=4.4
merged_restaurant_data[633,35]=4.6
merged_restaurant_data[638,35]=4.2
merged_restaurant_data[640,35]=4.6
merged_restaurant_data[645,35]=4.6
merged_restaurant_data[647,35]=4.5
merged_restaurant_data[651,35]=4.9
merged_restaurant_data[660,35]=5.0
merged_restaurant_data[661,35]=4.7
merged_restaurant_data[662,35]=3.9
merged_restaurant_data[663,35]=4.0
merged_restaurant_data[664,35]=4.4
merged_restaurant_data[666,35]=4.3
merged_restaurant_data[677,35]=4.2
merged_restaurant_data[683,35]=4.5
merged_restaurant_data[686,35]=4.3
merged_restaurant_data[688,35]=4.8
merged_restaurant_data[689,35]=4.9
merged_restaurant_data[692,35]=4.9
merged_restaurant_data[693,35]=3.8
merged_restaurant_data[697,35]=4.9
merged_restaurant_data[700,35]=4.0
merged_restaurant_data[702,35]=4.8
merged_restaurant_data[714,35]=4.6
merged_restaurant_data[718,35]=4.6
merged_restaurant_data[719,35]=4.5
merged_restaurant_data[725,35]=4.5
merged_restaurant_data[728,35]=4.7
merged_restaurant_data[729,35]=4.8
merged_restaurant_data[731,35]=4.7
merged_restaurant_data[732,35]=4.2
merged_restaurant_data[733,35]=4.4
merged_restaurant_data[734,35]=3.8
merged_restaurant_data[735,35]=4.5
merged_restaurant_data[737,35]=4.5
merged_restaurant_data[738,35]=4.6
merged_restaurant_data[741,35]=3.8
merged_restaurant_data[744,35]=4.9
merged_restaurant_data[746,35]=4.3
merged_restaurant_data[747,35]=4.2
merged_restaurant_data[752,35]=3.7
merged_restaurant_data[755,35]=4.5
merged_restaurant_data[759,35]=4.0
merged_restaurant_data[762,35]=4.8
merged_restaurant_data[764,35]=4.3
merged_restaurant_data[767,35]=4.4
merged_restaurant_data[769,35]=4.3
merged_restaurant_data[770,35]=4.9
merged_restaurant_data[772,35]=4.0
merged_restaurant_data[774,35]=4.9
merged_restaurant_data[777,35]=4.8
merged_restaurant_data[779,35]=4.1
merged_restaurant_data[780,35]=4.4
merged_restaurant_data[782,35]=4.6
merged_restaurant_data[784,35]=4.1
merged_restaurant_data[785,35]=5.0
merged_restaurant_data[787,35]=4.1
merged_restaurant_data[788,35]=4.8
merged_restaurant_data[790,35]=4.1
merged_restaurant_data[791,35]=3.8
merged_restaurant_data[793,35]=4.4
merged_restaurant_data[796,35]=4.6
merged_restaurant_data[799,35]=5.0
merged_restaurant_data[802,35]=4.3
merged_restaurant_data[807,35]=4.2
merged_restaurant_data[809,35]=4.3
merged_restaurant_data[810,35]=3.9
merged_restaurant_data[811,35]=4.4
merged_restaurant_data[812,35]=4.5
merged_restaurant_data[816,35]=5.0
merged_restaurant_data[820,35]=4.6
merged_restaurant_data[825,35]=4.9
merged_restaurant_data[827,35]=4.8
merged_restaurant_data[828,35]=5.0
merged_restaurant_data[830,35]=4.5
merged_restaurant_data[834,35]=4.4
merged_restaurant_data[837,35]=4.3
merged_restaurant_data[838,35]=5.0
merged_restaurant_data[839,35]=3.0
merged_restaurant_data[841,35]=3.0
merged_restaurant_data[842,35]=4.6
merged_restaurant_data[852,35]=5.0
merged_restaurant_data[855,35]=4.9
merged_restaurant_data[856,35]=4.1
merged_restaurant_data[859,35]=4.5
merged_restaurant_data[861,35]=4.8
merged_restaurant_data[865,35]=4.6
merged_restaurant_data[868,35]=4.8
merged_restaurant_data[869,35]=5.0
merged_restaurant_data[870,35]=4.6
merged_restaurant_data[871,35]=4.1
merged_restaurant_data[872,35]=4.4
merged_restaurant_data[878,35]=4.4
merged_restaurant_data[883,35]=4.6
merged_restaurant_data[884,35]=4.3
merged_restaurant_data[889,35]=4.6
merged_restaurant_data[891,35]=4.4
merged_restaurant_data[893,35]=4.5
merged_restaurant_data[894,35]=4.5
merged_restaurant_data[896,35]=3.2
merged_restaurant_data[897,35]=3.8
merged_restaurant_data[899,35]=3.8
merged_restaurant_data[901,35]=4.6
merged_restaurant_data[902,35]=4.1
merged_restaurant_data[905,35]=3.7
merged_restaurant_data[906,35]=4.6
merged_restaurant_data[907,35]=4.5
merged_restaurant_data[909,35]=4.9
merged_restaurant_data[910,35]=4.1
merged_restaurant_data[913,35]=3.0
merged_restaurant_data[916,35]=4.8
merged_restaurant_data[920,35]=4.2
merged_restaurant_data[921,35]=4.3
merged_restaurant_data[924,35]=4.9
merged_restaurant_data[925,35]=5.0
merged_restaurant_data[929,35]=3.5
merged_restaurant_data[930,35]=4.8
merged_restaurant_data[933,35]=3.8
merged_restaurant_data[936,35]=4.4
merged_restaurant_data[939,35]=4.4
merged_restaurant_data[940,35]=4.3
merged_restaurant_data[941,35]=4.6
merged_restaurant_data[942,35]=4.6
merged_restaurant_data[943,35]=4.2
merged_restaurant_data[945,35]=3.8
merged_restaurant_data[946,35]=4.6
merged_restaurant_data[948,35]=4.6
merged_restaurant_data[951,35]=3.4
merged_restaurant_data[953,35]=4.9
merged_restaurant_data[954,35]=4.3
merged_restaurant_data[955,35]=3.2
merged_restaurant_data[957,35]=4.5
merged_restaurant_data[961,35]=4.5
merged_restaurant_data[962,35]=4.9
merged_restaurant_data[965,35]=4.4
merged_restaurant_data[968,35]=4.1
merged_restaurant_data[970,35]=4.4
merged_restaurant_data[971,35]=4.7
merged_restaurant_data[972,35]=4.6
merged_restaurant_data[974,35]=3.5
merged_restaurant_data[975,35]=4.5
merged_restaurant_data[977,35]=4.7
merged_restaurant_data[979,35]=4.2
merged_restaurant_data[981,35]=4.8
merged_restaurant_data[982,35]=4.4
merged_restaurant_data[984,35]=4.4
merged_restaurant_data[986,35]=4.3
merged_restaurant_data[987,35]=4.3
merged_restaurant_data[988,35]=4.6
merged_restaurant_data[989,35]=2.7
merged_restaurant_data[991,35]=4.7
merged_restaurant_data[992,35]=4.3
merged_restaurant_data[993,35]=4.1
merged_restaurant_data[997,35]=4.8
merged_restaurant_data[998,35]=4.8
merged_restaurant_data[999,35]=4.4

sum(is.na(merged_restaurant_data$Rating))

merged_restaurant_data<- merged_restaurant_data %>%
  filter(!is.na(Rating))

merged_restaurant_data$dba<- str_to_title(merged_restaurant_data$dba)

merged_restaurant_data$Restaurant_Name <-
  paste(
    coalesce(merged_restaurant_data$dba, ""),
    coalesce(merged_restaurant_data$Name, "")
  )
```

```{r}
#| include: false
merged_restaurant_data <- merged_restaurant_data %>% select(-dba, -boro, -building, -street, -zipcode, -phone, -community_board, -council_district, -census_tract, -bbl, -nta, -`:@computed_region_f5dn_yrer`, -`:@computed_region_yeji_bk3q`, -`:@computed_region_sbqj_enih`, -`:@computed_region_92fq_4b7q`, -cuisine_description, -bin, -grade, -grade_date, -URL, -Name, -`Rating Count`, -`Detailed Ratings`, -`Price Category`, -Address, -ZipCode)

str(merged_restaurant_data$Lat)

str(merged_restaurant_data$latitude)

merged_restaurant_data$latitude<-as.numeric(merged_restaurant_data$latitude)

merged_restaurant_data$Lat<-as.numeric(merged_restaurant_data$Lat)

merged_restaurant_data$Latitude <-
  coalesce(
    merged_restaurant_data$latitude, merged_restaurant_data$Lat
  )

merged_restaurant_data <- merged_restaurant_data %>% select(-Lat, -latitude)

str(merged_restaurant_data$Lon)

str(merged_restaurant_data$longitude)

merged_restaurant_data$Lon<-as.numeric(merged_restaurant_data$Lon)

merged_restaurant_data$longitude<-as.numeric(merged_restaurant_data$longitude)

merged_restaurant_data$Longitude <-
  coalesce(
    merged_restaurant_data$longitude, merged_restaurant_data$Lon
  )

merged_restaurant_data <- merged_restaurant_data %>% select(-Lon, -longitude)
```

```{r}
#| include: false
museum_data<- museum_data %>%
  select(-tel, -url, -adress1, -address2)

museum_data<- museum_data %>%
  mutate(
    cleaned_geom_coordinates = gsub("c\\(|\\)|\"", "", the_geom.coordinates)
    )

museum_data<-museum_data %>%
  separate(
    col = cleaned_geom_coordinates,
    into = c("Longitude", "Latitude"),
    sep = ","
  )

museum_data$Longitude<- as.numeric(museum_data$Longitude)

museum_data$Latitude<- 
  as.numeric(museum_data$Latitude)
```

```{r}
#| include: false
merged_restaurant_data$Near_Museum<- ""

merged_restaurant_data[,18]="No"
merged_restaurant_data[14,18]="Yes"
merged_restaurant_data[629,18]="Yes"
merged_restaurant_data[458,18]="Yes"
merged_restaurant_data[389,18]="Yes"
merged_restaurant_data[490,18]="Yes"
merged_restaurant_data[550,18]="Yes"
merged_restaurant_data[48,18]="Yes"
merged_restaurant_data[411,18]="Yes"
merged_restaurant_data[361,18]="Yes"
merged_restaurant_data[471,18]="Yes"
merged_restaurant_data[456,18]="Yes"
merged_restaurant_data[553,18]="Yes"
merged_restaurant_data[404,18]="Yes"
merged_restaurant_data[562,18]="Yes"
merged_restaurant_data[288,18]="Yes"
merged_restaurant_data[487,18]="Yes"
merged_restaurant_data[460,18]="Yes"
merged_restaurant_data[579,18]="Yes"
merged_restaurant_data[620,18]="Yes"
merged_restaurant_data[309,18]="Yes"
merged_restaurant_data[244,18]="Yes"
merged_restaurant_data[439,18]="Yes"
merged_restaurant_data[507,18]="Yes"
merged_restaurant_data[381,18]="Yes"
merged_restaurant_data[355,18]="Yes"
merged_restaurant_data[433,18]="Yes"
merged_restaurant_data[513,18]="Yes"
merged_restaurant_data[238,18]="Yes"
merged_restaurant_data[590,18]="Yes"
merged_restaurant_data[120,18]="Yes"
merged_restaurant_data[143,18]="Yes"
merged_restaurant_data[259,18]="Yes"
merged_restaurant_data[118,18]="Yes"
merged_restaurant_data[43,18]="Yes"
merged_restaurant_data[289,18]="Yes"
merged_restaurant_data[202,18]="Yes"
merged_restaurant_data[388,18]="Yes"
merged_restaurant_data[280,18]="Yes"
merged_restaurant_data[516,18]="Yes"
merged_restaurant_data[369,18]="Yes"
merged_restaurant_data[346,18]="Yes"
merged_restaurant_data[91,18]="Yes"
merged_restaurant_data[604,18]="Yes"
merged_restaurant_data[353,18]="Yes"
merged_restaurant_data[123,18]="Yes"
merged_restaurant_data[538,18]="Yes"
merged_restaurant_data[611,18]="Yes"
merged_restaurant_data[82,18]="Yes"
merged_restaurant_data[642,18]="Yes"
merged_restaurant_data[473,18]="Yes"
merged_restaurant_data[61,18]="Yes"
merged_restaurant_data[247,18]="Yes"
merged_restaurant_data[24,18]="Yes"
merged_restaurant_data[127,18]="Yes"
merged_restaurant_data[186,18]="Yes"
merged_restaurant_data[624,18]="Yes"
merged_restaurant_data[59,18]="Yes"
merged_restaurant_data[64,18]="Yes"
merged_restaurant_data[176,18]="Yes"
merged_restaurant_data[89,18]="Yes"
merged_restaurant_data[256,18]="Yes"
merged_restaurant_data[141,18]="Yes"
merged_restaurant_data[410,18]="Yes"
merged_restaurant_data[497,18]="Yes"
merged_restaurant_data[394,18]="Yes"
merged_restaurant_data[221,18]="Yes"
merged_restaurant_data[210,18]="Yes"
merged_restaurant_data[436,18]="Yes"
merged_restaurant_data[135,18]="Yes"
merged_restaurant_data[332,18]="Yes"
merged_restaurant_data[85,18]="Yes"
merged_restaurant_data[571,18]="Yes"
merged_restaurant_data[526,18]="Yes"
merged_restaurant_data[18,18]="Yes"
merged_restaurant_data[51,18]="Yes"
merged_restaurant_data[172,18]="Yes"
merged_restaurant_data[49,18]="Yes"
merged_restaurant_data[212,18]="Yes"
merged_restaurant_data[262,18]="Yes"
merged_restaurant_data[328,18]="Yes"
merged_restaurant_data[34,18]="Yes"
merged_restaurant_data[131,18]="Yes"
merged_restaurant_data[246,18]="Yes"
merged_restaurant_data[155,18]="Yes"
merged_restaurant_data[600,18]="Yes"

merged_restaurant_data<- merged_restaurant_data %>%
  mutate(Rating_Group = case_when(
    Rating <= 3.9 ~ "Low",
    Rating >= 4.0 & Rating <= 4.5 ~ "Average",
    Rating >= 4.6 ~ "High"
    )
  )

merged_restaurant_data<- merged_restaurant_data[-(623:642),]

view(merged_restaurant_data)
```

```{r}
#| include: false
merged_restaurant_data$Restaurant_Violation<- ""

merged_restaurant_data[,20]="None"
merged_restaurant_data[40,20]="Critical"
merged_restaurant_data[49,20]="Critical"
merged_restaurant_data[55,20]="Critical"
merged_restaurant_data[56,20]="Critical"
merged_restaurant_data[67,20]="Critical"
merged_restaurant_data[95,20]="Critical"
merged_restaurant_data[98,20]="Critical"
merged_restaurant_data[99,20]="Critical"
merged_restaurant_data[106,20]="Critical"
merged_restaurant_data[157,20]="Critical"
merged_restaurant_data[160,20]="Critical"
merged_restaurant_data[167,20]="Critical"
merged_restaurant_data[170,20]="Critical"
merged_restaurant_data[171,20]="Critical"
merged_restaurant_data[172,20]="Critical"
merged_restaurant_data[213,20]="Critical"
merged_restaurant_data[214,20]="Critical"
merged_restaurant_data[220,20]="Critical"
merged_restaurant_data[221,20]="Critical"
merged_restaurant_data[224,20]="Critical"
merged_restaurant_data[230,20]="Critical"
merged_restaurant_data[236,20]="Critical"
merged_restaurant_data[238,20]="Critical"
merged_restaurant_data[239,20]="Critical"
merged_restaurant_data[275,20]="Critical"
merged_restaurant_data[278,20]="Critical"
merged_restaurant_data[279,20]="Critical"
merged_restaurant_data[289,20]="Critical"
merged_restaurant_data[291,20]="Critical"
merged_restaurant_data[301,20]="Critical"
merged_restaurant_data[305,20]="Critical"
merged_restaurant_data[306,20]="Critical"
merged_restaurant_data[307,20]="Critical"
merged_restaurant_data[308,20]="Critical"
merged_restaurant_data[310,20]="Critical"
```

```{r}
#| include: false
contingency_table_2 <- xtabs(~Restaurant_Violation+Near_Museum, data=merged_restaurant_data)
contingency_table_2

contingency_table_check_2<- merged_restaurant_data %>%
  tabyl(Restaurant_Violation, Near_Museum) %>%
  adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 1) %>%
  adorn_ns()
contingency_table_check_2
```

```{r}
#| include: false
Visual_2<- ggplot(merged_restaurant_data, aes(x = Near_Museum, fill = Restaurant_Violation)) +
  geom_bar(position = "fill") + 
  labs(
    title = "Proportion of Restaurant Violations by Restaurants Near Museums",
    y = "Proportion of if Restaurant had Violations ",
    x = "Near Museum?"
  ) +
  theme_solarized()
Visual_2
```

```{r}
#| include: false
chi_square_test<- chisq.test(contingency_table_2)
chi_square_test

chisq.test(contingency_table_2)$expected

cramerV(contingency_table_2)
```

```{r}
#| echo: false
fisher.test(contingency_table_2)
```

-   p value is 0.7975, which is still **not** a statistically significant relationship between restaurants being near museums and restaurant violations.

## Goal 3: Creating an interactive Map

```{r}
#| include: false
library(readr)
library(tidyr)
library(dplyr)
library(tidyverse)
library(stringr)
library(readxl)
library(janitor)
library(ggthemes)
library(rcompanion)
library(leaflet)
library(leaflet.extras)
library(leaflet.providers)
library(htmltools)

endpoint<- "https://data.cityofnewyork.us/resource/fn6f-htvy.json"
resp <- httr::GET(endpoint)
museum_data <- jsonlite::fromJSON(httr::content(resp, as = "text"), flatten = TRUE)



endpoint_1<-"https://data.cityofnewyork.us/resource/43nn-pn8j.json"
resp1 <- httr::GET(endpoint_1)
restaurant_data <- jsonlite::fromJSON(httr::content(resp1, as = "text"), flatten = TRUE)


restaurant_rating_data <- read_parquet(here("data", "raw", "restaurant_rating_data.parquet"), as_data_frame = TRUE )
```

```{r}
#| include: false
restaurant_rating_data$lat_new<- shQuote(restaurant_rating_data$Lat)
restaurant_rating_data$lon_new<- shQuote(restaurant_rating_data$Lon)
restaurant_rating_data$location.coordinates<- paste("c", "(", restaurant_rating_data$lon_new, ",", restaurant_rating_data$lat_new, ")", sep = "")

restaurant_rating_data <- restaurant_rating_data[-c(1, 2, 4, 5, 6, 8, 10, 11, 12, 15, 16, 26, 28, 32, 33,37, 38, 42, 45, 46, 47, 48, 50, 51, 57, 58, 61, 62, 63, 66, 68, 69, 74, 75, 79, 82, 85, 86, 89, 90, 93, 94, 95, 96, 97, 98, 99, 100, 103, 104, 105, 110, 111, 113, 117, 118, 119, 120, 128, 131, 133, 134, 138, 140, 144, 147, 151, 152, 153, 160, 165, 168, 174, 175, 176, 178, 179, 182, 183, 184, 186, 190, 192, 193, 195, 197, 198, 203, 204, 206, 208, 209, 212, 216, 218, 220, 223, 224, 225, 231, 232, 234, 236, 241, 244, 247, 249, 251, 254, 256, 265, 267, 268, 271, 274, 277, 283, 284, 285, 288, 289, 292, 294, 295, 297, 298, 299, 300, 301, 304, 305, 308, 310, 312, 315, 318, 320, 321, 322, 323, 325, 326, 328, 330, 331, 332, 334, 335, 337, 338, 339, 340, 341, 343, 345, 346, 348, 349, 350, 351, 353, 355, 356, 357, 359, 362, 363, 365, 366, 367, 370, 375, 376, 377, 378, 379, 380, 388, 389, 390, 391, 392, 393, 396, 399, 403, 406, 411, 415, 416, 417, 418, 420, 422, 423, 424, 425, 427, 429, 430, 432, 433, 435, 438, 439, 441, 442, 443, 444, 447, 449, 451, 454, 455, 457, 461, 463, 467, 469, 470, 472, 473, 474, 477, 478, 479, 483, 484, 488, 489, 491, 495, 497, 499, 500, 501, 506, 507, 508, 509, 510, 513, 514, 516, 520, 521, 522, 523, 525, 527, 528, 529, 532, 533, 537, 538, 539, 540, 543, 544, 546, 547, 549, 550, 552, 553, 554, 555, 556, 558, 560, 561, 562, 566, 567, 568, 569, 570, 571, 572, 575, 577, 578, 579, 580, 581, 582, 587, 589, 590, 591, 592, 595, 598, 599, 600, 607, 608, 610, 611, 612, 613, 614, 615, 618, 620, 621, 622, 624, 625, 626, 627, 631, 633, 635, 636, 637, 638, 640, 641, 646, 648, 653, 655, 657, 658, 660, 661, 663, 669, 670), ]
```

```{r}
#| include: false
is.character(restaurant_data$location.coordinates)
restaurant_data<- restaurant_data %>% mutate(location.coordinates = as.character(location.coordinates))

merged_restaurant_data<- full_join(restaurant_data, restaurant_rating_data, by = "location.coordinates")

sum(merged_restaurant_data$location.coordinates == "NULL", na.rm = TRUE)

merged_restaurant_data <-merged_restaurant_data[merged_restaurant_data$location.coordinates != "NULL", ]
```

```{r}
#| include: false
merged_restaurant_data[2,35]=4.7
merged_restaurant_data[3,35]=4.8
merged_restaurant_data[4,35]=4.0
merged_restaurant_data[6,35]=4.7
merged_restaurant_data[11,35]=4.9
merged_restaurant_data[13,35]=4.5
merged_restaurant_data[14,35]=4.1
merged_restaurant_data[16,35]=4.4
merged_restaurant_data[17,35]=4.8
merged_restaurant_data[18,35]=4.9
merged_restaurant_data[21,35]=4.2
merged_restaurant_data[22,35]=5.0
merged_restaurant_data[27,35]=4.4
merged_restaurant_data[28,35]=4.9
merged_restaurant_data[31,35]=4.4
merged_restaurant_data[32,35]=4.8
merged_restaurant_data[35,35]=4.4
merged_restaurant_data[39,35]=4.5
merged_restaurant_data[40,35]=4.6
merged_restaurant_data[44,35]=5.0
merged_restaurant_data[48,35]=5.0
merged_restaurant_data[49,35]=4.4 
merged_restaurant_data[50,35]=3.8
merged_restaurant_data[55,35]=4.9
merged_restaurant_data[58,35]=4.1
merged_restaurant_data[59,35]=4.3
merged_restaurant_data[61,35]=4.1
merged_restaurant_data[62,35]=4.4
merged_restaurant_data[63,35]=4.4
merged_restaurant_data[64,35]=3.8
merged_restaurant_data[67,35]=4.9
merged_restaurant_data[69,35]=4.6
merged_restaurant_data[73,35]=4.8
merged_restaurant_data[78,35]=5.0
merged_restaurant_data[82,35]=4.6
merged_restaurant_data[94,35]=4.8
merged_restaurant_data[96,35]=4.8
merged_restaurant_data[98,35]=4.2
merged_restaurant_data[103,35]=4.5
merged_restaurant_data[104,35]=4.9
merged_restaurant_data[105,35]=2.7
merged_restaurant_data[111,35]=4.1
merged_restaurant_data[113,35]=4.6
merged_restaurant_data[114,35]=4.4
merged_restaurant_data[115,35]=2.0
merged_restaurant_data[118,35]=4.6
merged_restaurant_data[130,35]=4.6
merged_restaurant_data[133,35]=3.0
merged_restaurant_data[134,35]=4.1
merged_restaurant_data[136,35]=4.7
merged_restaurant_data[142,35]=4.7
merged_restaurant_data[144,35]=4.0
merged_restaurant_data[146,35]=4.0
merged_restaurant_data[148,35]=3.5
merged_restaurant_data[150,35]=4.3
merged_restaurant_data[152,35]=4.8
merged_restaurant_data[153,35]=4.7
merged_restaurant_data[154,35]=5.0
merged_restaurant_data[159,35]=4.3
merged_restaurant_data[164,35]=4.7
merged_restaurant_data[169,35]=4.2
merged_restaurant_data[172,35]=4.6
merged_restaurant_data[173,35]=4.9
merged_restaurant_data[179,35]=4.7
merged_restaurant_data[180,35]=4.2
merged_restaurant_data[184,35]=4.4
merged_restaurant_data[185,35]=4.9
merged_restaurant_data[186,35]=4.5
merged_restaurant_data[189,35]=4.6
merged_restaurant_data[190,35]=5.0
merged_restaurant_data[191,35]=4.7
merged_restaurant_data[193,35]=4.8
merged_restaurant_data[195,35]=4.6
merged_restaurant_data[197,35]=4.8
merged_restaurant_data[199,35]=5.0
merged_restaurant_data[201,35]=4.5
merged_restaurant_data[207,35]=4.5
merged_restaurant_data[215,35]=4.2
merged_restaurant_data[217,35]=3.8
merged_restaurant_data[219,35]=4.8
merged_restaurant_data[221,35]=4.7
merged_restaurant_data[223,35]=4.6
merged_restaurant_data[229,35]=4.5
merged_restaurant_data[232,35]=4.7
merged_restaurant_data[233,35]=4.1
merged_restaurant_data[235,35]=4.6
merged_restaurant_data[236,35]=4.4
merged_restaurant_data[237,35]=4.3
merged_restaurant_data[241,35]=4.7
merged_restaurant_data[243,35]=4.5
merged_restaurant_data[245,35]=5.0
merged_restaurant_data[246,35]=4.7
merged_restaurant_data[260,35]=4.6
merged_restaurant_data[262,35]=4.3
merged_restaurant_data[270,35]=4.1
merged_restaurant_data[271,35]=4.9
merged_restaurant_data[273,35]=4.4
merged_restaurant_data[275,35]=4.9
merged_restaurant_data[278,35]=4.1
merged_restaurant_data[279,35]=4.5
merged_restaurant_data[280,35]=4.6
merged_restaurant_data[285,35]=4.3
merged_restaurant_data[286,35]=4.7
merged_restaurant_data[287,35]=4.8
merged_restaurant_data[288,35]=4.9
merged_restaurant_data[297,35]=4.5
merged_restaurant_data[304,35]=4.5
merged_restaurant_data[305,35]=4.7
merged_restaurant_data[308,35]=4.0
merged_restaurant_data[310,35]=4.5
merged_restaurant_data[314,35]=4.4
merged_restaurant_data[315,35]=4.7
merged_restaurant_data[319,35]=4.8
merged_restaurant_data[321,35]=4.9
merged_restaurant_data[322,35]=4.2 
merged_restaurant_data[328,35]=5.0
merged_restaurant_data[330,35]=4.6
merged_restaurant_data[335,35]=4.6
merged_restaurant_data[341,35]=5.0
merged_restaurant_data[342,35]=4.2
merged_restaurant_data[344,35]=3.6
merged_restaurant_data[346,35]=4.1
merged_restaurant_data[348,35]=4.9
merged_restaurant_data[350,35]=4.2
merged_restaurant_data[351,35]=4.1
merged_restaurant_data[352,35]=4.5
merged_restaurant_data[353,35]=4.5
merged_restaurant_data[356,35]=4.4
merged_restaurant_data[357,35]=4.3
merged_restaurant_data[358,35]=4.2
merged_restaurant_data[359,35]=4.8
merged_restaurant_data[363,35]=4.5
merged_restaurant_data[364,35]=4.8
merged_restaurant_data[367,35]=4.2
merged_restaurant_data[371,35]=4.6
merged_restaurant_data[374,35]=5.0
merged_restaurant_data[375,35]=3.9
merged_restaurant_data[376,35]=3.9
merged_restaurant_data[379,35]=3.8
merged_restaurant_data[382,35]=3.9
merged_restaurant_data[383,35]=5.0
merged_restaurant_data[384,35]=4.6
merged_restaurant_data[385,35]=4.6
merged_restaurant_data[387,35]=4.3
merged_restaurant_data[389,35]=4.9
merged_restaurant_data[391,35]=4.2
merged_restaurant_data[394,35]=4.5
merged_restaurant_data[395,35]=4.5
merged_restaurant_data[397,35]=4.8
merged_restaurant_data[404,35]=4.4
merged_restaurant_data[406,35]=4.5
merged_restaurant_data[408,35]=4.4
merged_restaurant_data[410,35]=3.8
merged_restaurant_data[411,35]=4.8
merged_restaurant_data[414,35]=3.9
merged_restaurant_data[416,35]=4.9
merged_restaurant_data[420,35]=4.6
merged_restaurant_data[422,35]=4.0
merged_restaurant_data[427,35]=4.8
merged_restaurant_data[433,35]=4.7
merged_restaurant_data[436,35]=3.7
merged_restaurant_data[437,35]=4.3
merged_restaurant_data[438,35]=4.6
merged_restaurant_data[440,35]=4.6
merged_restaurant_data[446,35]=4.7
merged_restaurant_data[452,35]=4.1
merged_restaurant_data[453,35]=4.3
merged_restaurant_data[454,35]=5.0
merged_restaurant_data[458,35]=4.3
merged_restaurant_data[459,35]=3.9
merged_restaurant_data[463,35]=4.0
merged_restaurant_data[467,35]=4.9
merged_restaurant_data[470,35]=4.0
merged_restaurant_data[471,35]=4.1
merged_restaurant_data[472,35]=4.0
merged_restaurant_data[486,35]=4.3
merged_restaurant_data[489,35]=5.0
merged_restaurant_data[494,35]=5.0
merged_restaurant_data[495,35]=4.9
merged_restaurant_data[496,35]=4.3
merged_restaurant_data[497,35]=4.2
merged_restaurant_data[501,35]=5.0
merged_restaurant_data[502,35]=4.1
merged_restaurant_data[506,35]=4.6
merged_restaurant_data[507,35]=4.6
merged_restaurant_data[509,35]=4.7
merged_restaurant_data[511,35]=4.5
merged_restaurant_data[512,35]=4.5
merged_restaurant_data[513,35]=3.3
merged_restaurant_data[515,35]=4.9
merged_restaurant_data[519,35]=4.8
merged_restaurant_data[520,35]=4.5
merged_restaurant_data[522,35]=4.9
merged_restaurant_data[523,35]=4.8
merged_restaurant_data[528,35]=4.9
merged_restaurant_data[533,35]=4.3
merged_restaurant_data[543,35]=4.6
merged_restaurant_data[546,35]=4.0
merged_restaurant_data[550,35]=4.8
merged_restaurant_data[552,35]=4.3
merged_restaurant_data[554,35]=3.7
merged_restaurant_data[555,35]=2.1
merged_restaurant_data[556,35]=4.7
merged_restaurant_data[557,35]=4.5
merged_restaurant_data[558,35]=5.0
merged_restaurant_data[562,35]=4.1
merged_restaurant_data[563,35]=4.3
merged_restaurant_data[566,35]=4.3
merged_restaurant_data[567,35]=4.5
merged_restaurant_data[568,35]=4.9
merged_restaurant_data[570,35]=4.3
merged_restaurant_data[573,35]=4.6
merged_restaurant_data[574,35]=4.1
merged_restaurant_data[575,35]=4.8
merged_restaurant_data[578,35]=4.4
merged_restaurant_data[581,35]=4.0
merged_restaurant_data[590,35]=4.1
merged_restaurant_data[592,35]=5.0
merged_restaurant_data[598,35]=3.9
merged_restaurant_data[601,35]=4.2
merged_restaurant_data[605,35]=4.6
merged_restaurant_data[608,35]=4.1
merged_restaurant_data[610,35]=4.1
merged_restaurant_data[613,35]=4.9
merged_restaurant_data[617,35]=4.4
merged_restaurant_data[622,35]=4.3
merged_restaurant_data[624,35]=4.0
merged_restaurant_data[625,35]=5.0
merged_restaurant_data[632,35]=4.4
merged_restaurant_data[633,35]=4.6
merged_restaurant_data[638,35]=4.2
merged_restaurant_data[640,35]=4.6
merged_restaurant_data[645,35]=4.6
merged_restaurant_data[647,35]=4.5
merged_restaurant_data[651,35]=4.9
merged_restaurant_data[660,35]=5.0
merged_restaurant_data[661,35]=4.7
merged_restaurant_data[662,35]=3.9
merged_restaurant_data[663,35]=4.0
merged_restaurant_data[664,35]=4.4
merged_restaurant_data[666,35]=4.3
merged_restaurant_data[677,35]=4.2
merged_restaurant_data[683,35]=4.5
merged_restaurant_data[686,35]=4.3
merged_restaurant_data[688,35]=4.8
merged_restaurant_data[689,35]=4.9
merged_restaurant_data[692,35]=4.9
merged_restaurant_data[693,35]=3.8
merged_restaurant_data[697,35]=4.9
merged_restaurant_data[700,35]=4.0
merged_restaurant_data[702,35]=4.8
merged_restaurant_data[714,35]=4.6
merged_restaurant_data[718,35]=4.6
merged_restaurant_data[719,35]=4.5
merged_restaurant_data[725,35]=4.5
merged_restaurant_data[728,35]=4.7
merged_restaurant_data[729,35]=4.8
merged_restaurant_data[731,35]=4.7
merged_restaurant_data[732,35]=4.2
merged_restaurant_data[733,35]=4.4
merged_restaurant_data[734,35]=3.8
merged_restaurant_data[735,35]=4.5
merged_restaurant_data[737,35]=4.5
merged_restaurant_data[738,35]=4.6
merged_restaurant_data[741,35]=3.8
merged_restaurant_data[744,35]=4.9
merged_restaurant_data[746,35]=4.3
merged_restaurant_data[747,35]=4.2
merged_restaurant_data[752,35]=3.7
merged_restaurant_data[755,35]=4.5
merged_restaurant_data[759,35]=4.0
merged_restaurant_data[762,35]=4.8
merged_restaurant_data[764,35]=4.3
merged_restaurant_data[767,35]=4.4
merged_restaurant_data[769,35]=4.3
merged_restaurant_data[770,35]=4.9
merged_restaurant_data[772,35]=4.0
merged_restaurant_data[774,35]=4.9
merged_restaurant_data[777,35]=4.8
merged_restaurant_data[779,35]=4.1
merged_restaurant_data[780,35]=4.4
merged_restaurant_data[782,35]=4.6
merged_restaurant_data[784,35]=4.1
merged_restaurant_data[785,35]=5.0
merged_restaurant_data[787,35]=4.1
merged_restaurant_data[788,35]=4.8
merged_restaurant_data[790,35]=4.1
merged_restaurant_data[791,35]=3.8
merged_restaurant_data[793,35]=4.4
merged_restaurant_data[796,35]=4.6
merged_restaurant_data[799,35]=5.0
merged_restaurant_data[802,35]=4.3
merged_restaurant_data[807,35]=4.2
merged_restaurant_data[809,35]=4.3
merged_restaurant_data[810,35]=3.9
merged_restaurant_data[811,35]=4.4
merged_restaurant_data[812,35]=4.5
merged_restaurant_data[816,35]=5.0
merged_restaurant_data[820,35]=4.6
merged_restaurant_data[825,35]=4.9
merged_restaurant_data[827,35]=4.8
merged_restaurant_data[828,35]=5.0
merged_restaurant_data[830,35]=4.5
merged_restaurant_data[834,35]=4.4
merged_restaurant_data[837,35]=4.3
merged_restaurant_data[838,35]=5.0
merged_restaurant_data[839,35]=3.0
merged_restaurant_data[841,35]=3.0
merged_restaurant_data[842,35]=4.6
merged_restaurant_data[852,35]=5.0
merged_restaurant_data[855,35]=4.9
merged_restaurant_data[856,35]=4.1
merged_restaurant_data[859,35]=4.5
merged_restaurant_data[861,35]=4.8
merged_restaurant_data[865,35]=4.6
merged_restaurant_data[868,35]=4.8
merged_restaurant_data[869,35]=5.0
merged_restaurant_data[870,35]=4.6
merged_restaurant_data[871,35]=4.1
merged_restaurant_data[872,35]=4.4
merged_restaurant_data[878,35]=4.4
merged_restaurant_data[883,35]=4.6
merged_restaurant_data[884,35]=4.3
merged_restaurant_data[889,35]=4.6
merged_restaurant_data[891,35]=4.4
merged_restaurant_data[893,35]=4.5
merged_restaurant_data[894,35]=4.5
merged_restaurant_data[896,35]=3.2
merged_restaurant_data[897,35]=3.8
merged_restaurant_data[899,35]=3.8
merged_restaurant_data[901,35]=4.6
merged_restaurant_data[902,35]=4.1
merged_restaurant_data[905,35]=3.7
merged_restaurant_data[906,35]=4.6
merged_restaurant_data[907,35]=4.5
merged_restaurant_data[909,35]=4.9
merged_restaurant_data[910,35]=4.1
merged_restaurant_data[913,35]=3.0
merged_restaurant_data[916,35]=4.8
merged_restaurant_data[920,35]=4.2
merged_restaurant_data[921,35]=4.3
merged_restaurant_data[924,35]=4.9
merged_restaurant_data[925,35]=5.0
merged_restaurant_data[929,35]=3.5
merged_restaurant_data[930,35]=4.8
merged_restaurant_data[933,35]=3.8
merged_restaurant_data[936,35]=4.4
merged_restaurant_data[939,35]=4.4
merged_restaurant_data[940,35]=4.3
merged_restaurant_data[941,35]=4.6
merged_restaurant_data[942,35]=4.6
merged_restaurant_data[943,35]=4.2
merged_restaurant_data[945,35]=3.8
merged_restaurant_data[946,35]=4.6
merged_restaurant_data[948,35]=4.6
merged_restaurant_data[951,35]=3.4
merged_restaurant_data[953,35]=4.9
merged_restaurant_data[954,35]=4.3
merged_restaurant_data[955,35]=3.2
merged_restaurant_data[957,35]=4.5
merged_restaurant_data[961,35]=4.5
merged_restaurant_data[962,35]=4.9
merged_restaurant_data[965,35]=4.4
merged_restaurant_data[968,35]=4.1
merged_restaurant_data[970,35]=4.4
merged_restaurant_data[971,35]=4.7
merged_restaurant_data[972,35]=4.6
merged_restaurant_data[974,35]=3.5
merged_restaurant_data[975,35]=4.5
merged_restaurant_data[977,35]=4.7
merged_restaurant_data[979,35]=4.2
merged_restaurant_data[981,35]=4.8
merged_restaurant_data[982,35]=4.4
merged_restaurant_data[984,35]=4.4
merged_restaurant_data[986,35]=4.3
merged_restaurant_data[987,35]=4.3
merged_restaurant_data[988,35]=4.6
merged_restaurant_data[989,35]=2.7
merged_restaurant_data[991,35]=4.7
merged_restaurant_data[992,35]=4.3
merged_restaurant_data[993,35]=4.1
merged_restaurant_data[997,35]=4.8
merged_restaurant_data[998,35]=4.8
merged_restaurant_data[999,35]=4.4

sum(is.na(merged_restaurant_data$Rating))

merged_restaurant_data<- merged_restaurant_data %>%
  filter(!is.na(Rating))

merged_restaurant_data$dba<- str_to_title(merged_restaurant_data$dba)

merged_restaurant_data$Restaurant_Name <-
  paste(
    coalesce(merged_restaurant_data$dba, ""),
    coalesce(merged_restaurant_data$Name, "")
  )
```

```{r}
#| include: false
merged_restaurant_data <- merged_restaurant_data %>% select(-dba, -boro, -building, -street, -zipcode, -phone, -community_board, -council_district, -census_tract, -bbl, -nta, -`:@computed_region_f5dn_yrer`, -`:@computed_region_yeji_bk3q`, -`:@computed_region_sbqj_enih`, -`:@computed_region_92fq_4b7q`, -cuisine_description, -bin, -grade, -grade_date, -URL, -Name, -`Rating Count`, -`Detailed Ratings`, -`Price Category`, -Address, -ZipCode)

str(merged_restaurant_data$Lat)

str(merged_restaurant_data$latitude)

merged_restaurant_data$latitude<-as.numeric(merged_restaurant_data$latitude)

merged_restaurant_data$Lat<-as.numeric(merged_restaurant_data$Lat)

merged_restaurant_data$Latitude <-
  coalesce(
    merged_restaurant_data$latitude, merged_restaurant_data$Lat
  )

merged_restaurant_data <- merged_restaurant_data %>% select(-Lat, -latitude)

str(merged_restaurant_data$Lon)

str(merged_restaurant_data$longitude)

merged_restaurant_data$Lon<-as.numeric(merged_restaurant_data$Lon)

merged_restaurant_data$longitude<-as.numeric(merged_restaurant_data$longitude)

merged_restaurant_data$Longitude <-
  coalesce(
    merged_restaurant_data$longitude, merged_restaurant_data$Lon
  )

merged_restaurant_data <- merged_restaurant_data %>% select(-Lon, -longitude)
```

```{r}
#| include: false
museum_data<- museum_data %>%
  select(-tel, -url, -adress1, -address2)

museum_data<- museum_data %>%
  mutate(
    cleaned_geom_coordinates = gsub("c\\(|\\)|\"", "", the_geom.coordinates)
    )

museum_data<-museum_data %>%
  separate(
    col = cleaned_geom_coordinates,
    into = c("Longitude", "Latitude"),
    sep = ","
  )

museum_data$Longitude<- as.numeric(museum_data$Longitude)

museum_data$Latitude<- 
  as.numeric(museum_data$Latitude)
```

```{r}
#| include: false
merged_restaurant_data$Near_Museum<- ""

merged_restaurant_data[,18]="No"
merged_restaurant_data[14,18]="Yes"
merged_restaurant_data[629,18]="Yes"
merged_restaurant_data[458,18]="Yes"
merged_restaurant_data[389,18]="Yes"
merged_restaurant_data[490,18]="Yes"
merged_restaurant_data[550,18]="Yes"
merged_restaurant_data[48,18]="Yes"
merged_restaurant_data[411,18]="Yes"
merged_restaurant_data[361,18]="Yes"
merged_restaurant_data[471,18]="Yes"
merged_restaurant_data[456,18]="Yes"
merged_restaurant_data[553,18]="Yes"
merged_restaurant_data[404,18]="Yes"
merged_restaurant_data[562,18]="Yes"
merged_restaurant_data[288,18]="Yes"
merged_restaurant_data[487,18]="Yes"
merged_restaurant_data[460,18]="Yes"
merged_restaurant_data[579,18]="Yes"
merged_restaurant_data[620,18]="Yes"
merged_restaurant_data[309,18]="Yes"
merged_restaurant_data[244,18]="Yes"
merged_restaurant_data[439,18]="Yes"
merged_restaurant_data[507,18]="Yes"
merged_restaurant_data[381,18]="Yes"
merged_restaurant_data[355,18]="Yes"
merged_restaurant_data[433,18]="Yes"
merged_restaurant_data[513,18]="Yes"
merged_restaurant_data[238,18]="Yes"
merged_restaurant_data[590,18]="Yes"
merged_restaurant_data[120,18]="Yes"
merged_restaurant_data[143,18]="Yes"
merged_restaurant_data[259,18]="Yes"
merged_restaurant_data[118,18]="Yes"
merged_restaurant_data[43,18]="Yes"
merged_restaurant_data[289,18]="Yes"
merged_restaurant_data[202,18]="Yes"
merged_restaurant_data[388,18]="Yes"
merged_restaurant_data[280,18]="Yes"
merged_restaurant_data[516,18]="Yes"
merged_restaurant_data[369,18]="Yes"
merged_restaurant_data[346,18]="Yes"
merged_restaurant_data[91,18]="Yes"
merged_restaurant_data[604,18]="Yes"
merged_restaurant_data[353,18]="Yes"
merged_restaurant_data[123,18]="Yes"
merged_restaurant_data[538,18]="Yes"
merged_restaurant_data[611,18]="Yes"
merged_restaurant_data[82,18]="Yes"
merged_restaurant_data[642,18]="Yes"
merged_restaurant_data[473,18]="Yes"
merged_restaurant_data[61,18]="Yes"
merged_restaurant_data[247,18]="Yes"
merged_restaurant_data[24,18]="Yes"
merged_restaurant_data[127,18]="Yes"
merged_restaurant_data[186,18]="Yes"
merged_restaurant_data[624,18]="Yes"
merged_restaurant_data[59,18]="Yes"
merged_restaurant_data[64,18]="Yes"
merged_restaurant_data[176,18]="Yes"
merged_restaurant_data[89,18]="Yes"
merged_restaurant_data[256,18]="Yes"
merged_restaurant_data[141,18]="Yes"
merged_restaurant_data[410,18]="Yes"
merged_restaurant_data[497,18]="Yes"
merged_restaurant_data[394,18]="Yes"
merged_restaurant_data[221,18]="Yes"
merged_restaurant_data[210,18]="Yes"
merged_restaurant_data[436,18]="Yes"
merged_restaurant_data[135,18]="Yes"
merged_restaurant_data[332,18]="Yes"
merged_restaurant_data[85,18]="Yes"
merged_restaurant_data[571,18]="Yes"
merged_restaurant_data[526,18]="Yes"
merged_restaurant_data[18,18]="Yes"
merged_restaurant_data[51,18]="Yes"
merged_restaurant_data[172,18]="Yes"
merged_restaurant_data[49,18]="Yes"
merged_restaurant_data[212,18]="Yes"
merged_restaurant_data[262,18]="Yes"
merged_restaurant_data[328,18]="Yes"
merged_restaurant_data[34,18]="Yes"
merged_restaurant_data[131,18]="Yes"
merged_restaurant_data[246,18]="Yes"
merged_restaurant_data[155,18]="Yes"
merged_restaurant_data[600,18]="Yes"

merged_restaurant_data<- merged_restaurant_data %>%
  mutate(Rating_Group = case_when(
    Rating <= 3.9 ~ "Low",
    Rating >= 4.0 & Rating <= 4.5 ~ "Average",
    Rating >= 4.6 ~ "High"
    )
  )

merged_restaurant_data<- merged_restaurant_data[-(623:642),]

view(merged_restaurant_data)
```

```{r}
#| include: false
merged_restaurant_data$Restaurant_Violation<- ""

merged_restaurant_data[,20]="None"
merged_restaurant_data[40,20]="Critical"
merged_restaurant_data[49,20]="Critical"
merged_restaurant_data[55,20]="Critical"
merged_restaurant_data[56,20]="Critical"
merged_restaurant_data[67,20]="Critical"
merged_restaurant_data[95,20]="Critical"
merged_restaurant_data[98,20]="Critical"
merged_restaurant_data[99,20]="Critical"
merged_restaurant_data[106,20]="Critical"
merged_restaurant_data[157,20]="Critical"
merged_restaurant_data[160,20]="Critical"
merged_restaurant_data[167,20]="Critical"
merged_restaurant_data[170,20]="Critical"
merged_restaurant_data[171,20]="Critical"
merged_restaurant_data[172,20]="Critical"
merged_restaurant_data[213,20]="Critical"
merged_restaurant_data[214,20]="Critical"
merged_restaurant_data[220,20]="Critical"
merged_restaurant_data[221,20]="Critical"
merged_restaurant_data[224,20]="Critical"
merged_restaurant_data[230,20]="Critical"
merged_restaurant_data[236,20]="Critical"
merged_restaurant_data[238,20]="Critical"
merged_restaurant_data[239,20]="Critical"
merged_restaurant_data[275,20]="Critical"
merged_restaurant_data[278,20]="Critical"
merged_restaurant_data[279,20]="Critical"
merged_restaurant_data[289,20]="Critical"
merged_restaurant_data[291,20]="Critical"
merged_restaurant_data[301,20]="Critical"
merged_restaurant_data[305,20]="Critical"
merged_restaurant_data[306,20]="Critical"
merged_restaurant_data[307,20]="Critical"
merged_restaurant_data[308,20]="Critical"
merged_restaurant_data[310,20]="Critical"
```

```{r}
#| include: false
contingency_table_2 <- xtabs(~Restaurant_Violation+Near_Museum, data=merged_restaurant_data)
contingency_table_2

contingency_table_check_2<- merged_restaurant_data %>%
  tabyl(Restaurant_Violation, Near_Museum) %>%
  adorn_totals("row") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 1) %>%
  adorn_ns()
contingency_table_check_2
```

```{r}
#| include: false
Visual_2<- ggplot(merged_restaurant_data, aes(x = Near_Museum, fill = Restaurant_Violation)) +
  geom_bar(position = "fill") + 
  labs(
    title = "Proportion of Restaurant Violations by Restaurants Near Museums",
    y = "Proportion of if Restaurant had Violations ",
    x = "Near Museum?"
  ) +
  theme_solarized()
Visual_2
```

```{r}
#| echo: false
merged_restaurant_data$labels<- paste( "Restaurant:", merged_restaurant_data$Restaurant_Name, ".",
                "Rating:", merged_restaurant_data$Rating) %>%
                 lapply(HTML)
               


museum_data$Labels<-paste("Museum:", museum_data$name) %>%
  lapply(HTML)


merged_restaurant_data$color<- case_when(
  merged_restaurant_data$Rating_Group == "Low"~"red",
  merged_restaurant_data$Rating_Group == "Average"~"purple",
  merged_restaurant_data$Rating_Group == "High"~"darkblue"
)


leaflet(data=merged_restaurant_data) %>%
  addTiles() %>%
  setView(lng = -74.0060, lat = 40.7128, zoom = 11
          ) %>%
  addCircleMarkers(lng = ~Longitude,
             lat = ~Latitude,
             label = ~labels,
             radius = 5,
             color = ~color,
             weight = 2, 
             opacity= 1
             ) %>%
  addCircleMarkers(
    data = museum_data,
    lng = ~Longitude, 
    lat = ~Latitude,
    label = ~Labels,
    radius = 5,
    color = "black",
    weight = 2,
    opacity = 1
  )
```

**Red**: Low Rated Restaurants **Purple**: Average Rated Restaurants Dark **Blue**: High Rated Restaurants. **Black**: Museums

## Project Relevance to New Yorkers

I believe that this project is relevant to New Yorkers who like to go to museums or restaurants and would like to plan an outing for a nice museum day in NYC. These types of New Yorkers would care about this type of project because they no longer have to rely on using Google to search each individual museum and instead have a map that is accessible and easy to use.

## Thank you!

------------------------------------------------------------------------

## Robert Hutto

### The Madison Square Garden Effect in the NBA

#### "Using basic statistics to investigate The Garden's influence on basketball performances"

```{r}
library(hoopR)
library(dplyr)
library(ggplot2)
library(tidyr)
library(scales)

seasons <- 2002:most_recent_nba_season()
sched <- load_nba_schedule(seasons = seasons) |>
  filter(type_abbreviation == "STD")

nba_abbrevs <- sched |>
  select(home_abbreviation, away_abbreviation) |>
  pivot_longer(cols = everything(), values_to = "team_abbreviation") |>
  distinct(team_abbreviation)

msg_games <- sched |>
  filter(venue_full_name == "Madison Square Garden") |>
  transmute(
    game_id, season, season_type, game_date, venue_full_name,
    home_abbreviation, away_abbreviation,
    home_score, away_score, home_winner, neutral_site
  )

msg_knicks_home_games <- msg_games |>
  filter(home_abbreviation == "NY", neutral_site == FALSE)

pb <- load_nba_player_box(seasons = seasons) |>
  filter(!did_not_play, minutes > 0) |>
  mutate(
    denom = 2 * (field_goals_attempted + 0.44 * free_throws_attempted),
    ts = if_else(denom > 0, points / denom, NA_real_),
    offensive_output = points + rebounds + assists,
    defensive_output = steals + blocks
  )

pb_msg <- pb |>
  inner_join(
    msg_knicks_home_games,
    by = c("game_id", "season", "season_type", "game_date")
  ) |>
  mutate(
    at_msg   = TRUE,
    is_knicks = (team_abbreviation == "NY"),
    is_home  = (home_away == "home"),
    is_away  = (home_away == "away"),
    ts = points / (2 * (field_goals_attempted + 0.44 * free_throws_attempted))
  )

pb_road_flagged <- pb |>
  filter(home_away == "away", !did_not_play, minutes > 0) |>
  left_join(
    msg_knicks_home_games |> transmute(game_id, at_msg = TRUE),
    by = "game_id"
  ) |>
  mutate(
    at_msg = if_else(is.na(at_msg), FALSE, at_msg),
    ts = points / (2 * (field_goals_attempted + 0.44 * free_throws_attempted))
  )
```

## Background {background-color="#1a1a2e"}

::::: columns
::: {.column width="45%"}
-   Oldest active NBA arena (est. February 11, 1968)
-   Home-court of the New York Knicks, one of the league's most valuable franchises
-   NYC's premier indoor venue comes with prestige and disproportionate national coverage
-   Dozens of celebrities, athletes, public figures in attendance of every game
-   Iconic performances: Jordan's 55-pt return from retirement (1995), Kobe's MSG record-setting 61-pt game (2009), Curry's 54-pt 11/13 from three breakout game (2013)
:::

::: {.column width="45%"}
> Madison Square Garden, *"The Mecca of Basketball"*

The narrative: MSG uniquely influences players' performances under its bright lights.

**But is that narrative supported by data?**
:::
:::::

## Research Questions {background-color="#1a1a2e"}

::: incremental
1.  **Q1:** Do the Knicks experience a *special* home-court advantage at MSG compared to other NBA teams at their home arenas?

2.  **Q2:** Do visiting players perform differently at MSG than at other away arenas?

3.  **Q3:** Which players benefit most (or least) from playing at MSG?
:::

## Methods & Data {background-color="#1a1a2e"}

-   **Source:** `hoopR` R package: NBA game and player box score data, 2002–present
-   **Scope:** Standard regular season and playoff games only
-   **Key metrics:** Points, True Shooting % (TS%), Turnovers, Offensive Output (PTS + REB + AST), Defensive Output (STL + BLK)
-   **Player analyses** excludes Knicks players home games; MSG data reflects **visiting teams only**
-   Comparisons use independent samples *t*-tests

## Q1: Knicks Home-Court Advantage {background-color="#1a1a2e"}

```{r}
#| label: fig-q1-plot
#| echo: false
non_nba_teams <- c("EAST", "WEST", "USA", "WORLD", "GIA", "LEB")
knicks_abbrevs <- c("NY", "NYK")

team_home_advantage <- pb |>
  filter(!did_not_play, minutes > 0, !team_abbreviation %in% non_nba_teams) |>
  group_by(game_id, team_abbreviation, home_away) |>
  summarise(team_points = sum(points, na.rm = TRUE), .groups = "drop") |>
  group_by(team_abbreviation, home_away) |>
  summarise(avg_points = mean(team_points, na.rm = TRUE), .groups = "drop") |>
  pivot_wider(names_from = home_away, values_from = avg_points) |>
  mutate(home_court_advantage = home - away) |>
  semi_join(nba_abbrevs, by = "team_abbreviation") |>
  mutate(
    is_knicks = team_abbreviation %in% knicks_abbrevs,
    rank = rank(desc(home_court_advantage))
  ) |>
  arrange(desc(home_court_advantage))

knicks_rank <- team_home_advantage |> filter(is_knicks) |> pull(rank)

ggplot(team_home_advantage,
       aes(x = reorder(team_abbreviation, home_court_advantage),
           y = home_court_advantage,
           fill = is_knicks)) +
  geom_col(width = 0.8) +
  geom_hline(yintercept = mean(team_home_advantage$home_court_advantage), 
           linetype = "dotted", color = "grey", linewidth = 0.8) +
  annotate("text", 
         x = 1, 
         y = mean(team_home_advantage$home_court_advantage),
         label = paste0("Avg: ", round(mean(team_home_advantage$home_court_advantage), 1)),
         hjust = -0, color = "grey", size = 3) +
  scale_fill_manual(values = c("FALSE" = "#4a4a6a", "TRUE" = "#f7941d")) +
  coord_flip() +
  labs(
    title = "Home-Court Advantage by Team (2002–Present)",
    subtitle = "Knicks (orange) rank 23rd out of 30 teams",
    x = NULL, y = "Avg Points Scored: Home − Away"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold"),
        axis.text.y = element_text(size = 8))
```

::: fragment
The Knicks rank **23rd** out of 32 teams (including SEA & NJ) in home-court scoring advantage, placing them in the bottom 1/3 of the league. Having MSG as a home-court may actually be more of a detriment than a benefit.

Follow-up question: do visiting players may play *better at MSG* compared to other away games?
:::

## Q2: Visiting Player Performance at MSG {background-color="#1a1a2e"}

```{r}
#| label: fig-q2-plot
#| echo: false
road_means <- pb_road_flagged |>
  group_by(at_msg) |>
  summarise(
    ts             = mean(ts, na.rm = TRUE),
    turnovers      = mean(turnovers, na.rm = TRUE),
    defensive_output = mean(defensive_output, na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(location = if_else(at_msg, "Away at MSG", "Away (Other)")) |>
  select(location, ts, turnovers, defensive_output) |>
  pivot_longer(cols = c(ts, turnovers, defensive_output),
               names_to = "metric", values_to = "value") |>
  mutate(
    metric = recode(metric,
      ts               = "True Shooting %",
      turnovers        = "Turnovers per game",
      defensive_output = "Defensive Output (STL+BLK)"
    ),
    location = factor(location, levels = c("Away (Other)", "Away at MSG"))
  )

ggplot(road_means, aes(x = location, y = value, fill = location)) +
  geom_col(width = 0.75) +
  facet_wrap(~ metric, scales = "free_y") +
  scale_fill_manual(values = c("Away (Other)" = "#4a4a6a", "Away at MSG" = "#f7941d")) +
  labs(
    title = "Visiting Player Performance: MSG vs. Other Away Arenas",
    x = NULL, y = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none",
        strip.text = element_text(face = "bold"),
        axis.text.x = element_text(angle = 20, hjust = 1))
```

::: fragment
At MSG, visiting players produce **less defensive stats** (*p* \< .001), but **shoot** **more efficiently** (*p* \< .001) and **turn the ball over** **less** (*p* = .029). Differences in raw points and offensive stat production were not significant.

Based on the second and third graphs, one may conclude NBA players across the league tend to be more "locked in" when they have the ball at MSG vs. other away arenas. But why do players produce less blocks and steals?

Let's look at individual players.
:::

## Q3: Who rises to the occasion at MSG? Who struggles? {background-color="#1a1a2e"}

```{r fig.height=5.5}
#| label: fig-q3-plot
#| echo: false
player_msg_advantage <- pb_road_flagged |>
  filter(!did_not_play, minutes >= 15) |>
  mutate(total_output = offensive_output + defensive_output) |>
  group_by(athlete_id, athlete_display_name, at_msg) |>
  summarise(
    games      = n(),
    avg_total  = mean(total_output, na.rm = TRUE),
    avg_pts    = mean(points, na.rm = TRUE),
    avg_ts     = mean(ts, na.rm = TRUE),
    .groups    = "drop"
  ) |>
  pivot_wider(names_from = at_msg,
              values_from = c(games, avg_total, avg_pts, avg_ts)) |>
  mutate(
    msg_adv_total = avg_total_TRUE - avg_total_FALSE,
    msg_adv_pts   = avg_pts_TRUE   - avg_pts_FALSE,
    msg_adv_ts    = avg_ts_TRUE    - avg_ts_FALSE
  ) |>
  filter(games_TRUE >= 8)

msg_extremes <- bind_rows(
  player_msg_advantage |> arrange(desc(msg_adv_total)) |> slice_head(n = 12) |> mutate(group = "MSG Risers"),
  player_msg_advantage |> arrange(msg_adv_total)       |> slice_head(n = 12) |> mutate(group = "MSG Chokers")
) |>
  mutate(athlete_display_name = factor(athlete_display_name,
                                       levels = athlete_display_name[order(msg_adv_total)]))

ggplot(msg_extremes,
       aes(x = msg_adv_total, y = athlete_display_name, fill = group)) +
  geom_col(width = 0.75) +
  facet_wrap(~ group, scales = "free_y") +
  scale_fill_manual(values = c("MSG Risers" = "#f7941d", "MSG Strugglers" = "#6a4a7a")) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  labs(
    title = "Total Stat Output: MSG vs. Other Away Games (All Player Data Since 2002)",
    subtitle = "Min. 8 games w/ >15mins played at MSG as a visiting player",
    x = "MSG Output − Other Away Output",
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none",
        strip.text = element_text(face = "bold", size = 13))
```

::: fragment
The influence of playing at MSG on individual players' statistical production depends on the player.

Knicks fans, do the players on the left seem overrated by other NBA fans? Do the players on the right evoke fear, anger, disdain, or general thoughts associated with villains?
:::

## Q3: MSG Risers/Strugglers (Current Players Only) {background-color="#1a1a2e"}

```{r fig.height=5.5}
#| label: fig-q3-plot2
#| echo: false
current_player_ids <- pb |>
  filter(season == most_recent_nba_season()) |>
  distinct(athlete_id)

player_msg_advantage_current <- pb_road_flagged |>
  filter(!did_not_play, minutes >= 15) |>
  mutate(total_output = offensive_output + defensive_output) |>
  group_by(athlete_id, athlete_display_name, at_msg) |>
  summarise(
    games      = n(),
    avg_total  = mean(total_output, na.rm = TRUE),
    avg_pts    = mean(points, na.rm = TRUE),
    avg_ts     = mean(ts, na.rm = TRUE),
    .groups    = "drop"
  ) |>
  pivot_wider(names_from = at_msg,
              values_from = c(games, avg_total, avg_pts, avg_ts)) |>
  mutate(
    msg_adv_total = avg_total_TRUE - avg_total_FALSE,
    msg_adv_pts   = avg_pts_TRUE   - avg_pts_FALSE,
    msg_adv_ts    = avg_ts_TRUE    - avg_ts_FALSE
  ) |>
  semi_join(current_player_ids, by = "athlete_id") |>
  filter(games_TRUE >= 8)

msg_extremes_current <- bind_rows(
  player_msg_advantage_current |> arrange(desc(msg_adv_total)) |> slice_head(n = 12) |> mutate(group = "MSG Risers"),
  player_msg_advantage_current |> arrange(msg_adv_total)       |> slice_head(n = 12) |> mutate(group = "MSG Chokers")
) |>
  mutate(athlete_display_name = factor(athlete_display_name,
                                       levels = athlete_display_name[order(msg_adv_total)]))

ggplot(msg_extremes_current,
       aes(x = msg_adv_total, y = athlete_display_name, fill = group)) +
  geom_col(width = 0.75) +
  facet_wrap(~ group, scales = "free_y") +
  scale_fill_manual(values = c("MSG Risers" = "#f7941d", "MSG Strugglers" = "#6a4a7a")) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  labs(
    title = "Total Stat Output: MSG vs. Other Away Games (Only Current Player Data)",
    subtitle = "Min. 8 games w/ >15mins played at MSG as a visiting player",
    x = "MSG Output − Other Away Output",
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none",
        strip.text = element_text(face = "bold", size = 13))
```

::: fragment
The influence of playing at MSG on individual players' statistical production depends on the player.

Knicks fans, do the players on the left seem overrated by other NBA fans? Do the players on the right evoke fear, anger, disdain, or general thoughts associated with villains?
:::

## Conclusions {background-color="#1a1a2e"}

::: incremental
-   **Q1:** The Knicks' home-court advantage at MSG is actually *worse* than most NBA teams.
-   **Q2:** Visiting players show small but statistically significant differences at MSG compared to other away arenas. On average, players shoot more efficiently and turn the ball over less, but produce less blocks and steals.
-   **Q3:** There is meaningful individual variation in how players perform at MSG relative to their road averages.
-   **Takeaway:** While players across the NBA perform better offensively at MSG, the "MSG effect" is not a homogeneous influence on players; some perform better and others worse when they play at MSG compared to other away arenas.
:::

------------------------------------------------------------------------

## Isley Jean-Pierre

### From School To Juvenile Incarceration

------------------------------------------------------------------------

## Shannon Joyce

### Toxic Homes: Exploring Mold Exposure Complaint and Domestic Violence Report Trends in NYC

```{r}
#| echo: false

library(tidyverse)
library(readxl)
library(ggplot2)
library(mosaic)
library(AICcmodavg)
library(knitr)
library(patchwork)

mold_data <- read_parquet(
  here("data", "raw","311_Service_Requests_from_2010_to_Present_20251215.parquet"))
dv_data <- read_parquet(
  here("data", "raw","NYPD_Complaint_Data_Historic_20251218.parquet"))

mold_data_clean <- mold_data %>% filter(
           `Location Type` == "RESIDENTIAL BUILDING" | `Location Type` == "Residential Building" | `Location Type` == "Loft Residence" | `Location Type` == "Mixed Use Building" | `Location Type` == "Apartment" | `Location Type` == "3+ Family Apartment Building" | `Location Type` == "1-2 Family Dwelling" | `Location Type` == "1-2 Family Mixed Use Building" | `Location Type` == "3+ Family Mixed Use Building" | `Location Type` == "Single Room Occupancy (SRO)")

dv_data_clean<- dv_data %>% rename(
  "complaint_number" = `CMPLNT_NUM`,
  "inc_occur_date" = `CMPLNT_FR_DT`,
  "inc_occur_time" = `CMPLNT_FR_TM`,
  "inc_end_date" = `CMPLNT_TO_DT`,
  "inc_end_time" = `CMPLNT_TO_TM`,
  "precinct_occur" = `ADDR_PCT_CD`,
  "report_date" = `RPT_DT`,
  "key_code" = `KY_CD`,
  "offense_type" = `OFNS_DESC`,
  "class_code" = `PD_CD`,
  "class_code_desc" = `PD_DESC`,
  "attempt_completion" = `CRM_ATPT_CPTD_CD`,
  "offense_level" = `LAW_CAT_CD`,
  "borough" = `BORO_NM`,
  "occur_location" = `LOC_OF_OCCUR_DESC`,
  "premise_desc" = `PREM_TYP_DESC`,
  "juris_code_desc" = `JURIS_DESC`,
  "jurisdiction" = `JURISDICTION_CODE`,
  "park_occur" = `PARKS_NM`,
  "development" = `HADEVELOPT`,
  "development_code" = `HOUSING_PSA`,
  "x_coord" = `X_COORD_CD`,
  "y_coord" = `Y_COORD_CD`,
  "suspect_age" = `SUSP_AGE_GROUP`,
  "suspect_race" = `SUSP_RACE`,
  "suspect_sex" = `SUSP_SEX`,
  "transit_district" = `TRANSIT_DISTRICT`,
  "patrol_borough" = `PATROL_BORO`,
  "station_name" = `STATION_NAME`,
  "victim_age" = `VIC_AGE_GROUP`,
  "victim_race" = `VIC_RACE`,
  "victim_sex" = `VIC_SEX`
  )

mold_data_clean <- mold_data_clean %>%
  mutate(Created_Date_Original = `Created Date`) %>% 
  separate(
    col = `Created Date`,
  into = c("Year","Month","Day"),
  sep = "-", 
  remove = FALSE
)

dv_data_clean <- dv_data_clean %>% separate(
  col = inc_occur_date,
  into = c("Year","Month","Day"),
  sep = "-",
)

mold_data_clean <- mold_data_clean %>%
  filter(Descriptor != "Unsafe Mold Cleanup")

mold_data_clean<- mold_data_clean %>% mutate(
  `Complaint Type` = recode(
    `Complaint Type`, 
    "UNSANITARY CONDITION" = "Mold",
    "Unsanitary Condition" = "Mold",
    "MOLD" = "Mold",
    "GENERAL" = "Mold",
    "GENERAL CONSTRUCTION" = "Mold"
  ))

mold_data_clean<- mold_data_clean %>% mutate(
  `Month` = recode(
    `Month`, 
    "01" = "01 - January",
    "02" = "02 - February",
    "03" = "03 - March",
    "04" = "04 - April",
    "05" = "05 - May",
    "06" = "06 - June",
    "07" = "07 - July",
    "08" = "08 - August",
    "09" = "09 - September",
    "10" = "10 - October",
    "11" = "11 - November",
    "12" = "12 - December"
    ))

dv_data_clean<- dv_data_clean %>% mutate(
  `Month` = recode(
    `Month`, 
    "01" = "01 - January",
    "02" = "02 - February",
    "03" = "03 - March",
    "04" = "04 - April",
    "05" = "05 - May",
    "06" = "06 - June",
    "07" = "07 - July",
    "08" = "08 - August",
    "09" = "09 - September",
    "10" = "10 - October",
    "11" = "11 - November",
    "12" = "12 - December"
  ))

dv_data_clean$complaint <- "DV"

dv_data_clean <- dv_data_clean %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Year >= 2010)

mold_data_clean<- mold_data_clean %>% mutate(
  Borough = case_when(
    City == "NEW YORK" ~ "MANHATTAN",
    City == "BROOKLYN" ~ "BROOKLYN",
    City == "ARVERNE" ~ "QUEENS",
    City == "BRONX" ~ "BRONX",
    City == "JAMAICA" ~ "QUEENS",
    City == "SPRINGFIELD GARDENS" ~ "QUEENS",
    City == "FLUSHING" ~ "QUEENS",
    City == "STATEN ISLAND" ~ "STATEN ISLAND",
    City == "RICHMOND HILL" ~ "QUEENS",
    City == "ASTORIA" ~ "QUEENS",
    City == "HOLLIS" ~ "QUEENS",
    City == "RIDGEWOOD" ~ "QUEENS",
    City == "FOREST HILLS" ~ "QUEENS",
    City == "ELMHURST" ~ "QUEENS",
    City == "MASPETH" ~ "QUEENS",
    City == "SOUTH RICHMOND HILL" ~ "QUEENS",
    City == "JACKSON HEIGHTS" ~ "QUEENS",
    City == "BAYSIDE" ~ "QUEENS",
    City == "FAR ROCKAWAY" ~ "QUEENS",
    City == "SAINT ALBANS" ~ "QUEENS",
    City == "CORONA" ~ "QUEENS",
    City == "WOODSIDE" ~ "QUEENS",
    City == "QUEENS VILLAGE" ~ "QUEENS",
    City == "REGO PARK" ~ "QUEENS",
    City == "ROSEDALE" ~ "QUEENS",
    City == "SUNNYSIDE" ~ "QUEENS",
    City == "OZONE PARK" ~ "QUEENS",
    City == "EAST ELMHURST" ~ "QUEENS",
    City == "MIDDLE VILLAGE" ~ "QUEENS",
    City == "WOODHAVEN" ~ "QUEENS",
    City == "SOUTH OZONE PARK" ~ "QUEENS",
    City == "ROCKAWAY PARK" ~ "QUEENS",
    City == "KEW GARDENS" ~ "QUEENS",
    City == "FRESH MEADOWS" ~ "QUEENS",
    City == "COLLEGE POINT" ~ "QUEENS",
    City == "LONG ISLAND CITY" ~ "QUEENS",
    City == "OAKLAND GARDENS" ~ "QUEENS",
    City == "WHITESTONE" ~ "QUEENS",
    City == "HOWARD BEACH" ~ "QUEENS",
    City == "CAMBRIA HEIGHTS" ~ "QUEENS",
    City == "BELLEROSE" ~ "QUEENS",
    City == "LITTLE NECK" ~ "QUEENS",
    City == "BREEZY POINT" ~ "QUEENS",
    City == "GLEN OAKS" ~ "QUEENS",
    City == "FLORAL PARK" ~ "QUEENS",
    City ==  "PELHAM" ~ "BRONX",
    City == "NEW HYDE PARK" ~ "QUEENS",
    City == "QUEENS" ~ "QUEENS",
    City == "MANHATTAN" ~ "MANHATTAN",
    City == "Far Rockaway" ~ "QUEENS",  
    City == "Astoria" ~ "QUEENS",
    City == "Elmhurst" ~ "QUEENS",
    City == "Corona" ~ "QUEENS",       
    City == "Ozone Park" ~ "QUEENS",
    City == "Forest Hills" ~ "QUEENS",
    City == "Jamaica" ~ "QUEENS",  
    City == "Arverne" ~ "QUEENS",
    City == "Bayside" ~ "QUEENS",
    City == "East Elmhurst" ~ "QUEENS", 
    City == "Flushing" ~ "QUEENS",
    City == "Middle Village" ~ "QUEENS",
    City == "Ridgewood" ~ "QUEENS",
    City == "Woodside" ~ "QUEENS",
    City == "Oakland Gardens" ~ "QUEENS",
    City == "Rego Park" ~ "QUEENS",
    City == "Hollis" ~ "QUEENS",
    City == "Saint Albans" ~ "QUEENS",
    City == "Springfield Gardens" ~ "QUEENS",
    City == "Kew Gardens" ~ "QUEENS",
    City == "Fresh Meadows" ~ "QUEENS",
    City == "Howard Beach" ~ "QUEENS",
    City == "South Rich mond Hill" ~ "QUEENS",
    City == "Whitestone" ~ "QUEENS",
    City == "South Ozone Park" ~ "QUEENS",
    City == "College Point" ~ "QUEENS",
    City == "Jackson Heights" ~ "QUEENS",
    City == "Maspeth" ~ "QUEENS",
    City == "Long Island City" ~ "QUEENS",
    City == "Rockaway Park" ~ "QUEENS",
    City == "Sunnyside" ~ "QUEENS",
    City == "Woodhaven" ~ "QUEENS",
    City == "Floral Park" ~ "QUEENS",
    City == "Glen Oaks" ~ "QUEENS",
    City == "Queens Village" ~ "QUEENS",
    City == "Bellerose" ~ "QUEENS",
    City == "Little Neck" ~ "QUEENS",
    City == "Richmond Hill" ~ "QUEENS",
    City == "Rosedale" ~ "QUEENS",
    City == "Cambria Heights" ~ "QUEENS",
    City == "New Hyde Park" ~ "QUEENS",
    City == "Breezy Point" ~ "QUEENS",
  )
)

mold_data_clean <- mold_data_clean %>% filter(!is.na(Borough))
mold_data_clean<- mold_data_clean %>% filter(Year != 2025)

mold_data_clean <- mold_data_clean %>%
  mutate(
    created_date = as.Date(`Created Date`),
    closed_date  = as.Date(`Closed Date`),
    resolution_days = as.numeric(closed_date - created_date)
  )


aggregated_dv_data <- dv_data_clean %>%
  group_by(Year, Month, borough) %>%
  summarise(
    `complaint` = n(),
    .groups = "drop"
  )
aggregated_dv_data <- aggregated_dv_data %>%
  filter(borough != "(null)")

aggregated_dv_data <- aggregated_dv_data %>%
  mutate(Year = as.character(Year))

aggregated_dv_data<- aggregated_dv_data %>% rename(
  "Borough" = "borough")

aggregated_dv_data<- aggregated_dv_data %>% rename(
  "DV Reports" = "complaint"
)

aggregated_mold_data <- mold_data_clean %>%
  group_by(Year, Month, Borough) %>%
  summarise(
  `Complaint Type` = n(),
  .groups = "drop"
)

aggregated_mold_data<- aggregated_mold_data %>% rename(
  "Mold Complaints" = "Complaint Type"
)

aggregated_dv_mold_data <- left_join(
  aggregated_dv_data,
  aggregated_mold_data,
  by = c("Borough", "Year", "Month")
)

aggregated_dv_mold_data <- aggregated_dv_mold_data %>%
  mutate(
    year_month = paste(Year, Month)
  )

aggregated_dv_mold_data <- aggregated_dv_mold_data %>%
  group_by(Borough) %>%
  mutate(time_index = row_number()) %>%
  ungroup()

mold_monthly_resolution <- mold_data_clean %>%
  group_by(Year, Month) %>%
  summarise(
    avg_resolution_days = mean(resolution_days, na.rm = TRUE),
    n_complaints = n()
  ) %>%
  arrange(Year, Month)
```

## Project Overview

-   Mold Exposure —\> Psychological Stress

-   Psychological Stress —\> Domestic Violence

Do domestic violence reports and residential mold complaints in NYC follow similar, correlated patterns over time?

## Datasets

[311 Service Requests (Mold Complaints)](https://data.cityofnewyork.us/Social-Services/311-Service-Requests-from-2020-to-Present/erm2-nwe9/about_data)

```{r}
#| label: mold datasets
#| echo: false
head(aggregated_mold_data, n=3) %>% kable()
```

\|

[NYPD Complaint Data Historic (Domestic Violence Reports)](https://data.cityofnewyork.us/Public-Safety/NYPD-Complaint-Data-Historic/qgea-i56i/about_data)

```{r}
#| label: dv datasets
#| echo: false
head(aggregated_dv_data, n=3) %>% kable()
```

## Exploratory Summaries

```{r}
#| label: summaries
#| echo: false
dv_summary <- aggregated_dv_data %>%
  summarise(
    total_reports = sum(`DV Reports`),
    start_year = min(as.numeric(Year)),
    end_year = max(as.numeric(Year)),
    boroughs = n_distinct(Borough),
    avg_monthly = mean(`DV Reports`)
  )

mold_summary <- aggregated_mold_data %>%
  summarise(
    total_complaints = sum(`Mold Complaints`),
    start_year = min(as.numeric(Year)),
    end_year = max(as.numeric(Year)),
    boroughs = n_distinct(Borough),
    avg_monthly = mean(`Mold Complaints`)
  )
```

DV Report Summaries

```{r}
kable(dv_summary)
```

\|

Mold Complaint Summaries

```{r}
kable(mold_summary)
```

## Exploratory Analysis: Heat Maps

```{r}
#| label: fig-heatmaps
#| echo: false
dv_plot_data <- aggregated_dv_data %>%
  group_by(Year, Borough) %>%
  summarise(total_reports = sum(`DV Reports`))

p1<- ggplot(dv_plot_data, aes(x = Year, y = Borough, fill = total_reports)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkred") +
  labs(
    title = "DV Reports by Borough and Year",
    x = "Year",
    y = "Borough",
    fill = "DV Reports"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45))

mold_plot_data <- aggregated_mold_data %>%
  group_by(Year, Borough) %>%
  summarise(total_complaints = sum(`Mold Complaints`))

p2<- ggplot(mold_plot_data, aes(x = Year, y = Borough, fill = total_complaints)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "wheat", high = "darkgreen") +
  labs(
    title = "Mold Complaints by Borough and Year",
    x = "Year",
    y = "Borough",
    fill = "Mold Complaints"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45))

p1 + p2
```

## Exploratory Analysis: Temporal Trends by Borough

```{r}
#| label: trends
#| echo: false
plot_data <- aggregated_dv_mold_data %>%
  pivot_longer(
    cols = c(`DV Reports`, `Mold Complaints`),
    names_to = "Type",
    values_to = "Count"
  )

ggplot(plot_data, aes(x = time_index, y = Count, color = Type)) +
  geom_line(linewidth = 0.5) +
  facet_wrap(~Borough) +
  scale_color_manual(values = c("DV Reports" = "darkred", "Mold Complaints" = "darkgreen")) +
  labs(
    title = "Monthly DV and Mold Reports by Borough",
    x = "Time",
    y = "Number of Reports",
    color = "Report Type"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45)
  )
```

## Correlation Plot: Totals by Borough

```{r}
#| label: fig-corrplot1
#| echo: false
ggplot(aggregated_dv_mold_data, aes(x = `Mold Complaints`, y = `DV Reports`, color = Borough)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "gray18") +
  labs(title = "DV Reports vs Mold Complaints by Borough",
       x = "Mold Complaints",
       y = "DV Reports") +
  theme_minimal()
```

## Correlation Test: DV Reports \~ Mold Complaints

```{r}
#| label: corr
#| echo: false
cor.test(aggregated_dv_mold_data$`DV Reports`, 
         aggregated_dv_mold_data$`Mold Complaints`)
```

## Correlation Plot: Lagged Data

```{r}
#| label: fig-corrplot2
#| echo: false
dv_mold_lagged <- aggregated_dv_mold_data %>%
  arrange(Borough, time_index) %>%
  group_by(Borough) %>%
  mutate(DV_next_month = lead(`DV Reports`, n = 1)) %>%
  ungroup()

ggplot(dv_mold_lagged, aes(x = `Mold Complaints`, y = DV_next_month)) +
  geom_point(alpha = 0.5, color = "darkgreen") +
  geom_smooth(method = "lm", color = "darkred") +
  labs(
    title = "Next Month DV Reports vs Current Month Mold Complaints",
    x = "Mold Complaints (Current Month)",
    y = "DV Reports (Next Month)"
  ) +
  theme_minimal()
```

## Correlation Test: Lagged Data

```{r}
#| label: corr2
#| echo: false
cor.test(dv_mold_lagged$DV_next_month, dv_mold_lagged$`Mold Complaints`)
```

## Regression Models

DV Reports \~ Mold Complaints + Borough

```{r}
#| label: reg
#| echo: false
lm_borough <- lm(
  `DV Reports` ~ `Mold Complaints` + Borough,
  data = aggregated_dv_mold_data
)

summary(lm_borough)
AIC(lm_borough)
```

## Regression Models

DV Reports \~ Mold Complaints + Borough + Average Mold Resolution Days

```{r}
aggregated_dv_mold_data <- aggregated_dv_mold_data %>%
  left_join(mold_monthly_resolution, by = c("Year", "Month"))

lm_resolution_borough <- lm(
  `DV Reports` ~ `Mold Complaints` + Borough + avg_resolution_days,
  data = aggregated_dv_mold_data
)

summary(lm_resolution_borough)
AIC(lm_resolution_borough)
```

## Key Findings

-   Consistent positive association
-   Regression model is still significant when accounting for borough differences (though weaker)
-   Lagged analyses were very similar to non-lagged results

------------------------------------------------------------------------

## Emma Valentina Tupone

### Environmental Stressors and Social Complaints in NYC

## Research Question

-   Does environmental risk relate to social stress?

-   Flooding → environmental risk

-   Noise → social stress indicator

## Data Sources

-   311 Noise & Flooding Complaints

-   E-Designations

-   NYC Hazard Mitigation Plan

## Flooding Complaints by Borough

-   Flooding varies across boroughs

-   Infrastructure differences likely

## Flooding vs. Noise Complaints

-   Small positive trend

-   Not statistically significant

## Results

-   Weak positive association

-   Not significant

-   Little variance explained

## Why it Matters

-   Open data reveals urban stress patterns

-   Flooding alone isn't predictive

-   Framework for future analysis

## Thank You!

Questions?

------------------------------------------------------------------------

## Xinru Wang

### Beating Around the Bush

## Urban Wildlife in NYC

-   Wildlife incidents are reported across NYC every day.

-   But they are **not evenly distributed** across boroughs.

-   **What explains these patterns?**

## Could Street Trees Influence Wildlife Incidents?

At first glance, this might seem unlikely. Street trees line sidewalks, while many wildlife incidents occur in parks. But urban ecosystems are connected.

**Street trees can support urban wildlife by providing:**

• Food\
• Shelter\
• Travel pathways

```{r libraries, message=FALSE, warning=FALSE}
#| include: false
library(tidyverse)
library(janitor)
library(skimr)
library(ggplot2)
library(knitr)
library(rcompanion)
```

## 2015 NYC Street Tree Census

• Over 680,000 street trees recorded across NYC\
• Includes species, location, and health condition\
• Used to estimate urban canopy coverage

```{r}
#| label: data-import-csv
#| message: false
#| include: false

# Import NYC Open Data CSV files
tree_data <- read_parquet(
  here("data", "raw","2015_Street_Tree_Census.parquet"))
animal_data <- read_parquet(
  here("data", "raw","Urban_Park_Ranger_Animal_Condition_Response.parquet"))

#Standardize column names
tree_data <- tree_data %>% clean_names()
animal_data <- animal_data %>% clean_names()

# Select variables needed for tree-level analysis
tree_clean <- tree_data %>%
  select(borough, health, tree_dbh, latitude, longitude)

# Select variables needed for wildlife incident analysis
animal_clean <- animal_data %>%
  select(borough, species_description, animal_class, animal_condition, property)

# Check for missing borough values
sum(is.na(tree_data$borough))
sum(is.na(animal_data$borough))

# Convert key categorical variables to factors and clean missing values
tree_clean <- tree_clean %>%
  mutate(
    health = factor(health, levels = c("Poor", "Fair", "Good"))
  )

animal_clean <- animal_clean %>%
  mutate(
    animal_condition = na_if(animal_condition, "N/A"),
    animal_condition = factor(animal_condition),
    animal_class = factor(animal_class)
  )
```

```{r}
#| label: fig-tree-summary
#| echo: false
#| message: false
#| warning: false

tree_summary <- tree_clean %>%
  group_by(borough) %>%
  summarise(
    total_trees = n(),
    pct_good_health = mean(health == "Good", na.rm = TRUE),
    avg_dbh = mean(tree_dbh, na.rm = TRUE),
    .groups = "drop"
  )

ggplot(tree_summary,
       aes(x = reorder(borough, -total_trees),
           y = total_trees)) +
  geom_col(fill = "chartreuse4") +
  labs(
    title = "Total Street Trees by Borough",
    x = "Borough",
    y = "Total Street Trees"
  ) +
  theme_minimal(base_size = 12) +
    theme(plot.title = element_text(size = 17, family = "serif", face = "bold"),
        axis.title.x = element_text(size = 12, family = "serif"),
        axis.title.y = element_text(size = 12, family = "serif"))
```

## Urban Park Ranger Wildlife Incident Reports

-   Reports of wildlife incidents across NYC parks
-   Includes injured animals, distressed wildlife, and conflicts with humans
-   Allows us to track wildlife activity patterns

```{r}
#| label: fig-animal-summary
#| echo: false
#| message: false
#| warning: false
#| fig-height: 2
#| fig-width: 6

animal_summary <- animal_clean %>%
  group_by(borough) %>%
  summarise(
    total_incidents = n(),
    pct_injured = mean(animal_condition == "Injured", na.rm = TRUE),
    .groups = "drop"
  )

ggplot(animal_summary,
       aes(x = reorder(borough, -total_incidents),
           y = total_incidents)) +
  geom_col(fill = "salmon4") +
  labs(
    title = "Wildlife Incidents by Borough",
    x = "Borough",
    y = "Total Incidents"
  ) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(size = 17, family = "serif", face = "bold"),
        axis.title.x = element_text(size = 12, family = "serif"),
        axis.title.y = element_text(size = 12, family = "serif"))
```

## Street Tree Density Across New York City

```{r}
#| label: fig-density-heatmap
#| fig-cap: "Brighter colors indicate higher concentrations of street trees."
#| message: false
#| echo: false
#| fig-width: 10
#| fig-height: 6

ggplot(tree_clean, aes(x = longitude, y = latitude)) +
  geom_bin2d(bins = 50) +
  scale_fill_viridis_c(
    option = "plasma",
    name = "Street Tree Density"
  ) +
  coord_fixed() +
  labs(
    title = "Street Tree Density in NYC",
    subtitle = "Higher values indicate greater concentration of street trees",
    x = "Longitude",
    y = "Latitude"
  ) +
    theme_minimal(base_size = 12) +
  theme(plot.title = element_text(size = 17, family = "serif", face = "bold"),
        axis.title.x = element_text(size = 12, family = "serif"),
        axis.title.y = element_text(size = 12, family = "serif"))
```

## Wildlife Incidents per 10,000 Street Trees

```{r}
#| label: fig-incident-per-tree
#| echo: false
#| message: false
#| fig-cap: How many wildlife incidents occur for every 10,000 street trees.

borough_summary <- left_join(tree_summary, animal_summary, by = "borough")

borough_summary <- borough_summary %>%
  mutate(incidents_per_10k_trees = total_incidents / total_trees * 10000)

ggplot(borough_summary,
       aes(x = borough, y = incidents_per_10k_trees)) +
  geom_col(fill = "dodgerblue4") +
  labs(
    title = "Wildlife Incidents per 10,000 Street Trees by Borough",
    x = "Borough",
    y = "Incidents per 10,000 Street Trees"
  ) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(size = 17, family = "serif", face = "bold"),
        axis.title.x = element_text(size = 12, family = "serif"),
        axis.title.y = element_text(size = 12, family = "serif"))
```

## Weak Relationship Between Street Trees and Wildlife Incidents

```{r}
#| label: simple-regression
#| include: false
simple_regression <- lm(total_incidents ~ total_trees, data = borough_summary)
summary(simple_regression)
r2 <- summary(simple_regression)$r.squared
```

```{r}
#| label: fig-scatterplot-tree-incident
#| fig-cap: "Each point represents a NYC borough."
#| message: false
#| echo: false
#| fig-width: 7
#| fig-height: 4


ggplot(borough_summary,
       aes(x = total_trees, y = total_incidents, label = borough)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(vjust = -0.8) +
  annotate(
  "text",
  x = 225000,
  y = 1250,
  label = paste0("R² = ", round(r2, 2)),
  size = 3.5,
  family = "serif") +
  labs(
    title = "Street Tree Abundance and Wildlife Incidents by Borough",
    x = "Total Street Trees",
    y = "Total Wildlife Incidents"
  ) +
    theme_minimal(base_size = 9) +
  theme(plot.title = element_text(size = 17, family = "serif", face = "bold"),
        axis.title.x = element_text(size = 12, family = "serif"),
        axis.title.y = element_text(size = 12, family = "serif"))
```

## Raccoons Dominate Wildlife Incidents Across NYC

```{r}
#| label: fig-bar-common-species
#| fig-cap: "Raccoons appear most frequently in wildlife incident reports across boroughs."
#| message: false
#| echo: false

top_species <- animal_clean %>%
  count(borough, species_description) %>%
  group_by(borough) %>%
  slice_max(n, n = 5) %>%
  ungroup()

ggplot(top_species,
       aes(x = reorder(species_description, n), y = n)) +
  geom_col(fill = "mistyrose4") +
  coord_flip() +
  facet_wrap(~ borough, scales = "free_y") +
  labs(
    title = "Most Common Wildlife Species Involved in Incidents by Borough",
    x = "Species",
    y = "Number of Incidents"
  ) +
    theme_minimal(base_size = 10) +
  theme(plot.title = element_text(size = 17, family = "serif", face = "bold"),
        axis.title.x = element_text(size = 12, family = "serif"),
        axis.title.y = element_text(size = 12, family = "serif"))
```

## Key Takeaways

-   Street tree abundance alone does not strongly predict wildlife incidents

-   Wildlife incidents vary across boroughs

-   Raccoon are the most commonly reported species

-   Other urban factors likely drive wildlife encounters

------------------------------------------------------------------------

## Connect with the Students

Explore their work and connect:

🔗 [NYC Open Data Student Gallery](https://martinezc1-nyc-open-data-student-gallery.share.connect.posit.cloud/)

🔗 [NYC Open Data Student Gallery Github](https://github.com/martinezc1/NYC-Open-Data-Student-Gallery)
